### 2015-06-15 Paper/jcgt-template/paper.tex
Paper prep!

\documentclass{jcgt}

\setciteauthor{TODO insert your name(s) here as they should appear in the citation}
\setcitetitle{TODO insert your paper's title here without linebreaks}

% Mark submissions with the date of submission using the following line:
%\submitted{\today}

% Once an article is accepted accepted, switch to the following line and comment the preceding one. The editor will supply the argument values.
\accepted{2014-02-07}{2014-02-07}{2014-02-07}{Editor Name}{3}{1}{1}{1}{2014}
\seturl{http://jcgt.org/published/0003/01/01/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\title{JCGT Style Guidelines and\\Formatting Template}

\author
       {Roy G. Biv\\Colortech, Inc.
        \and Raymond Trace\\Graphica University
       }

\teaser{
  \includegraphics[width=2in]{teapot.png}
  \label{fig:teaser}
  \caption{A teapot teaser figure. A teaser figure is \textbf{mandatory} for JCGT.}
}

\maketitle
\thispagestyle{firstpagestyle}

\begin{abstract}
\small
This document is the \textit{JCGT} formatting template \textit{and} a description of the guidelines
for  \textit{JCGT} articles.  The author names on this document are fictional and chosen to show
how to format affiliations.
\end{abstract}

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}
Documents may be typeset using any system so long as they follow the formatting
of this example, however we recommend
the use of \LaTeX\ because it simplifies typesetting.

\subsection{Related Work}
\label{sec:relatedwork}

Unless the point of the article is to provide a survey, do not survey all related work in a \textit{JCGT} article. Instead, discuss only directly relevant work against which the technique will be compared or alternatives that the reader might prefer.  There need not be an explicit related work section, however the introduction should provide enough information for the reader to know why he or she might prefer this technique to a previous one that is known to the community.

\section{Sections}
Divide the article into logical sections...

\subsection{Sub-section}
...and subsections.\pdfmarginpar{You can use pdfmarginpar to leave notes for your coauthors.  Please don't leave notes in the review copy.}

\subsubsection{Sub-subsections}
Use sub-subsections sparingly.

\paragraph{Paragraph.} Consider ``paragraph'' formatting as an alternative to sub-subsections.

\section{Abstract}
Briefly describe the topic, value of the technique, and major limitations in the abstract. For example,

``The CIE Lab color  space is useful for image editing operations and device-independent representation of
color.  However, most modern display  input  and  cameras  output is in the sRGB color space, as are stored images on disk.  We describe a method for
efficiently converting colors between the Lab and sRGB color spaces that requires no branches,  lookup tables, or floating-point operations.

Our 32-bit fixed-point
implementation is 30\% faster than the traditional (and floating point) method on
iPad 3 and Core i7 processors and produces provably
minimal error for 24-bit input color.  However,  unlike traditional color space
conversions, it does not generalize for conversions to and from CIE XYZ or
gamma 1.0 RGB space in the new method, and it is slower than direct floating-point
conversion on devices that do not support native integer instructions (e.g., DX9 GPUs).

The article includes C and GLSL source code adapted from the hardware accelerated path of the Colortech's commercial PaintMaster application for
both desktop and mobile platforms. ''

\section{Images}

Capture raster images at high resolution in a lossless format, such as PNG.  Vector images
can be directly incorporated in formats such as PDF; avoid rasterizing vector source diagrams
and results.  Include figures with captions as shown in Figure~\ref{fig:teapot}.

Figures should be near the text that refers to them whenever possible, and should not be
reduced to grayscale.  Encode images in the sRGB space (the default for PNG).

\begin{figure}[htb]
  \centering
   \includegraphics[width=0.5\columnwidth]{teapot.png}
   \caption{\label{fig:teapot}
     This is a teapot rendered by OpenGL with environment mapping and a Blinn-Phong BSDF.}
\end{figure}

\section{Source Code}

Format source code listings with syntax highlighting as shown in Listing~\ref{lst:hello}.  Inline
code, such as \lstinline{lerp(a, b, t)}, should also be in a fixed-width font.

\begin{lstlisting}[caption={A simple C program.}, label={lst:hello}, float]
#include <stdio.h>

/* Entry point for the program */
int main(const int argc, const char* argv[]) {

    /* Print some output */
    printf("Hello world!\n");

    return 0;
}
\end{lstlisting}

\section{Hyperlinks}
Link section, figure, table, equation, etc. reference numbers and citations to their target (the JCGT \LaTeX class automatically generates these links).

Favor standard citations over URLs whenever possible, since URLs may not stand the test of time.  When providing a URL, type the full URL text so that it is still useful in print, and create a hyperlink.  For example,
the \textit{JCGT} website is at \href{http://jcgt.org}{http://jcgt.org}.

\section{Citations and Bibliography}
Do not use citations as nouns--the text should read correctly were they omitted. For example, the following are correct:

\begin{enumerate}
\item ``The Rendering Equation \cite{Immel:1986:RMN:15886.15901,Kajiya:1986:RE:15922.15902} relates the incoming and outgoing light at a surface...''
\item ``Immel et al.'s paper~\shortcite{Immel:1986:RMN:15886.15901} uses a directional parameterization...''
\end{enumerate}

\noindent The bibliography should use ACM SIGGRAPH format.

\section{Units}
Use SI units, e.g., meters, seconds, unless there is an application-specific reason to employ a non SI-unit such as `feet'.  Units should appear in normal Roman type when in an equation, e.g.,
%
\begin{equation}
\frac{150\;\mathrm{m}}{20\;\mathrm{s}} = 75\;\mathrm{m}/\mathrm{s}
\end{equation}
%
to distinguish them from variable names.

Time performance should be measured in \textbf{time} units, e.g., ``the shader took 3.6\;s to execute on GeForce GTX 680.''  However, it is appropriate to also express values in frames per second when discussing the end-to-end performance of a complete system.  For example, the performance of a shadow algorithm implementation should be measured in milliseconds but the performance of a complete virtual reality system could be measured in frames per second instead of rendering time per frame.

\section{Mathematics}
Please use the guidelines in Table~\ref{tbl:math} for typesetting mathematics, although in some cases, domain-specific notation should overrule them.

\begin{table}[htdp]
\small
\begin{center}
\begin{tabular}{l|c}
Scalar & $x$\\
Mathematical vector & $\vec{v}$ \\
Unit vector & $\hat{\omega}$ \\
Matrix & $\mathbf{M}$ \\
Transpose & $\mathbf{M}^\transpose$\\
Inverse & $\mathbf{M}^{-1}$\\
Geometric point & $X$ \\
Set & $\mathbb{S}$ \\
Subscript expression & $h_i$ \\
Subscript name & $L_\mathrm{in}$ \\
Function & $f(x)$ \\
Named function & $\max(3, 4)$, $\operatorname{lerp}(a, b, t)$
\end{tabular}
\end{center}
\caption{Math symbol formatting guidelines.}
\label{tbl:math}
\end{table}

\noindent Equation~\ref{eqn:rendering} is an example of a numbered equation following these conventions.

\begin{equation}
L_\mathrm{o}(X, \hat{\omega}_\mathrm{o}) = L_\mathrm{e}(X, \hat{\omega}_\mathrm{o}) + \int_{\mathbf{S}^2} L_\mathrm{i}(X, \hat{\omega}_\mathrm{i}) \cdot f(\hat{\omega}_\mathrm{i}, \hat{\omega}_\mathrm{o}) \cdot |\hat{n} \cdot \hat{\omega}_\mathrm{i} |~ d\hat{\omega}_\mathrm{i}
\label{eqn:rendering}
\end{equation}

Large equations, images, and tables may exceed the regular text margins but should stop within 1.5 cm of the physical page border.

\subsection*{Acknowledgements}
Authors may provide a brief acknowledgements section if desired.

All entries in the bibliography \textbf{must} have URLs unless no URL is possible (e.g., book, very old thesis).

\small
\bibliographystyle{jcgt}
\bibliography{paper}

\section*{Index of Supplemental Materials}
When supplemental materials such as video, data sets, and source code are provided with an article, briefly describe them by directory or filename here.

\section*{Author Contact Information}

\hspace{-2mm}\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
Roy G. Biv \newline
Colortech, Inc. \newline
29 Red Blvd. \newline
New York, NY 10511 \newline
\href{mailto:roy@colortech.com}{roy@colortech.com}
&

Raymond Trace \newline
Graphica University \newline
37 Rue De Lambert \newline
Paris, 75009 France \newline
\href{mailto:rtrace@graphica.edu}{rtrace@graphica.edu} \newline
\href{http://graphica.edu/~rtrace}{http://graphica.edu/\textasciitilde rtrace}

\end{tabular}

\afterdoc

\end{document}

### 2015-06-16 GLFW/Curves/ShaderDefs.h
Added tests to compare to 1d baked out curves

@@ -5,6 +5,7 @@
 //        SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
 //        SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
 //        SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
+//        SHADER_UNIFORM(NAME)
 //    SHADER_END()
 //
 //    SHADER_BEGIN(NAME)
@@ -18,6 +19,10 @@
 //    to set data for this attribute.
 //
 //    TYPE can be float or double.
+//
+//    SHADER_UNIFORM(NAME)
+//
+//    Lets you set a uniform in the shader.  NAME is the name of the uniform.  Assumed to be a float!
 //
 //    SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
 //    SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
@@ -41,6 +46,22 @@ SHADER_BEGIN(TrilinearTest)
     SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
     SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
     SHADER_UNIFORM_TEXTURE_3D(uSampler, float)
+SHADER_END()
+
+SHADER_BEGIN(BilinearBakeTest)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
+    SHADER_UNIFORM_TEXTURE_2D(uSampler, float)
+    SHADER_UNIFORM_TEXTURE_2D(uBakedSampler, float)
+    SHADER_UNIFORM(uBakeSamples)
+SHADER_END()
+
+SHADER_BEGIN(TrilinearBakeTest)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
+    SHADER_UNIFORM_TEXTURE_3D(uSampler, float)
+    SHADER_UNIFORM_TEXTURE_2D(uBakedSampler, float)
+    SHADER_UNIFORM(uBakeSamples)
 SHADER_END()
 
 SHADER_BEGIN(RationalTest)
[…]

### 2015-06-16 GLFW/Curves/Shader_BilinearBakeTest.cpp

@@ -1,0 +1,154 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            BilinearBakeTest
+//=============================================================================================================
+
+void CShaderBilinearBakeTest::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+
+    SetTextureData_uSampler(2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f
+    });
+
+    // 4x1 baked out texture for curve to show accuracy using same number of pixels as 2x2 texture
+    const int c_numBakeSamples = 4;
+    std::vector<float> curvePoints;
+    for (int i = 0; i < c_numBakeSamples; ++i) {
+        float t = float(i) / float(c_numBakeSamples - 1);
+        float t2 = t*t;
+        float s = 1.0f - t;
+        float s2 = s*s;
+        float curveValue = A*s2 + B*2.0f*s*t + C*t2;
+        curvePoints.push_back(curveValue);
+        curvePoints.push_back(0.0f);
+        curvePoints.push_back(0.0f);
+        curvePoints.push_back(0.0f);
+    }
+    SetTextureData_uBakedSampler(c_numBakeSamples, 1, curvePoints);
+    SetUniformData_uBakeSamples((float)c_numBakeSamples);
+}
+
+const char *CShaderBilinearBakeTest::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
[…]

### 2015-06-16 GLFW/Curves/Shaders.h

@@ -25,6 +25,13 @@
             m_numTriangles = data.size() / ELEMENTSIZE; \
         }
 
+#define SHADER_UNIFORM(NAME) \
+    private: \
+        GLuint m_uniform_##NAME##; \
+        float m_uniform_value_##NAME##; \
+    public: \
+        void SetUniformData_##NAME##(float value) {m_uniform_value_##NAME## = value;} 
+
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
     private: \
         GLuint m_uniform_##NAME##; \
@@ -55,6 +62,7 @@
 enum EShaderTest {
     #define SHADER_BEGIN(NAME) e_shader##NAME,
     #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+    #define SHADER_UNIFORM(NAME)
     #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
     #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
     #define SHADER_END()

### 2015-06-16 GLFW/Curves/main.cpp

@@ -66,6 +66,7 @@ int main(void)
     // init our shaders
     #define SHADER_BEGIN(NAME) CShader##NAME shader##NAME##;  shader##NAME##.Init();
     #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+    #define SHADER_UNIFORM(NAME)
     #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
     #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
     #define SHADER_END()
@@ -83,6 +84,7 @@ int main(void)
         switch (g_whichTest){
         #define SHADER_BEGIN(NAME) case e_shader##NAME: shader##NAME##.Render(); glfwSetWindowTitle(window, #NAME " - Arrow keys to cycle test"); break;
         #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+        #define SHADER_UNIFORM(NAME)
         #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
         #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
         #define SHADER_END()

### 2015-06-16 GLFW/Curves/shaders.cpp

@@ -48,6 +48,9 @@ GLenum GLType<double>()
         m_attr_##NAME## = glGetAttribLocation(m_program, #NAME); \
         m_attr_##NAME##_buffer = -1; \
         glEnableVertexAttribArray(m_attr_##NAME##);
+#define SHADER_UNIFORM(NAME) \
+        m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
+        m_uniform_value_##NAME## = 0.0f;
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_texture_##NAME## = -1;
@@ -63,6 +66,7 @@ GLenum GLType<double>()
     CShader##NAME##::~CShader##NAME##() { \
         glDeleteProgram(m_program);
 #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+#define SHADER_UNIFORM(NAME)
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
         glDeleteTextures(1, &m_texture_##NAME##);
 #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
@@ -74,18 +78,21 @@ GLenum GLType<double>()
 // ----- MAKE RENDER FUNCTIONS -----
 #define SHADER_BEGIN(NAME) \
     void CShader##NAME##::Render() { \
-        glUseProgram(m_program);
+        glUseProgram(m_program); \
+        GLuint texIndex = 0;
 #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE) \
         glBindBuffer(GL_ARRAY_BUFFER, m_attr_##NAME##_buffer); \
         glVertexAttribPointer(m_attr_##NAME##, ELEMENTSIZE, GLType<TYPE>(), false, 0, 0);
+#define SHADER_UNIFORM(NAME) \
+        glUniform1f(m_uniform_##NAME##, m_uniform_value_##NAME##);
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
-        glActiveTexture(GL_TEXTURE0); \
+        glActiveTexture(GL_TEXTURE0 + texIndex); \
         glBindTexture(GL_TEXTURE_2D, m_texture_##NAME##); \
[…]

### 2015-06-22 Paper/Figures/Figure2.tex
Figure 2 done. updated figure 1 to be same orientation as 2

\documentclass{article}
\usepackage{tikz}
\definecolor{darkgreen}{RGB}{0,192,0}
\title{Cartesian closed categories and the price of eggs}
\author{Jane Doe}
\date{September 1994}
\begin{document}

	\usetikzlibrary{arrows.meta}
	\tikzset{>={Latex[width=3mm,length=3mm]}}

	\begin{figure}
		\begin{tikzpicture}[x=12.5cm,y=4cm]
			% raw texture, bilinear sampled texture, curve results
		    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=4cm,height=4cm]{Figure2Texture.png}};
		    \node[anchor=south west,inner sep=0] at (4.125cm,0) {\includegraphics[width=4cm,height=4cm]{Figure2Bilinear.png}};
		    \node[anchor=south west,inner sep=0] at (8.25cm,0) {\includegraphics[width=4cm,height=4cm]{Figure2Curves.png}};
		    % representative line for where the quadratic bezier curve lives
		    \draw[yellow,->,line width=0.5mm]    (5.125cm,1cm) -- (7.125cm,3cm);    
		\end{tikzpicture}	
		\caption{Left: a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.  Center: The same texture as viewed when using bilinear texture sampling.  The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve. Right: The curve resulting from sampling along the yellow line.}		
	\end{figure}

\end{document}

### 2015-06-22 Paper/Figures/Figure2.tex
More WIP.  Getting ready to move to latex!

@@
 	\begin{figure}
-		\begin{tikzpicture}[x=12.5cm,y=4cm]
+		\begin{tikzpicture}[x=12.5cm,y=4.25cm]
+			% border
+			\draw (0cm,0cm) -- (12.5cm,0cm) -- (12.5cm,4.25cm) -- (0cm,4.25cm) -- (0cm, 0cm);		
 			% raw texture, bilinear sampled texture, curve results
-		    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=4cm,height=4cm]{Figure2Texture.png}};
-		    \node[anchor=south west,inner sep=0] at (4.125cm,0) {\includegraphics[width=4cm,height=4cm]{Figure2Bilinear.png}};
-		    \node[anchor=south west,inner sep=0] at (8.25cm,0) {\includegraphics[width=4cm,height=4cm]{Figure2Curves.png}};
+		    \node[anchor=south west,inner sep=0] at (0.125cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure2Texture.png}};
+		    \node[anchor=south west,inner sep=0] at (4.25cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure2Bilinear.png}};
+		    \node[anchor=south west,inner sep=0] at (8.375cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure2Curves.png}};
 		    % representative line for where the quadratic bezier curve lives
-		    \draw[yellow,->,line width=0.5mm]    (5.125cm,1cm) -- (7.125cm,3cm);    
+		    \draw[yellow,->,line width=0.5mm]    (5.25cm,1.125cm) -- (7.25cm,3.125cm);    
 		\end{tikzpicture}
@@
 The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve.
-Right: The curve resulting from sampling along the yellow line.}
+Right: The curves resulting from sampling along the yellow line (Alpha curve ommited).}
 	\end{figure}

### 2015-06-23 Paper/Figures/Figure4.tex
Paper Progress. Figures in paper

--- 2015-06-22 Paper/Figures/Figure2.tex
@@
 			% raw texture, bilinear sampled texture, curve results
-		    \node[anchor=south west,inner sep=0] at (0.125cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure2Texture.png}};
-		    \node[anchor=south west,inner sep=0] at (4.25cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure2Bilinear.png}};
-		    \node[anchor=south west,inner sep=0] at (8.375cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure2Curves.png}};
+		    \node[anchor=south west,inner sep=0] at (0.125cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Texture.png}};
+		    \node[anchor=south west,inner sep=0] at (4.25cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Bilinear.png}};
+		    \node[anchor=south west,inner sep=0] at (8.375cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Curves.png}};
 		    % representative line for where the quadratic bezier curve lives
 		    \draw[yellow,->,line width=0.5mm]    (5.25cm,1.125cm) -- (7.25cm,3.125cm);    
+		    \draw (0.08,0.25) node[] {\Huge{A}};
+		    \draw (0.25,0.25) node[] {\Huge{B}};
+		    \draw (0.08,0.75) node[] {\Huge{B}};
+		    \draw (0.25,0.75) node[] {\Huge{C}};    		    
 		\end{tikzpicture}

### 2015-06-23 Paper/paper.tex
Paper Progress. Figures in paper

\documentclass{jcgt}
\usepackage{tikz}
\definecolor{darkgreen}{RGB}{0,192,0}

\setciteauthor{Alan Wolfe}
\setcitetitle{GPU Efficient Texture Based Bezier Curve Evaluation}

% Mark submissions with the date of submission using the following line:
%\submitted{\today}

% Once an article is accepted accepted, switch to the following line and comment the preceding one. The editor will supply the argument values.
\accepted{2014-02-07}{2014-02-07}{2014-02-07}{Editor Name}{3}{1}{1}{1}{2014}
\seturl{http://jcgt.org/published/0003/01/01/}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\usetikzlibrary{arrows.meta}
\tikzset{>={Latex[width=3mm,length=3mm]}}

\title{GPU Efficient Texture Based Bezier Curve Evaluation}

\author
       {Alan Wolfe\\Blizzard Entertainment}

\teaser{
  \begin{tikzpicture}[x=5in,y=1.7in]
    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=5in,height=1.7in]{Teaser.png}};
    % representative line for where the quadratic bezier curve lives in the bilinear sampled texture
    \draw[yellow,->,line width=0.5mm]    (0.41,0.25) -- (0.58,0.75);
    \draw (0.08,0.25) node[] {\Huge{A}};
    \draw (0.25,0.25) node[] {\Huge{B}};
    \draw (0.08,0.75) node[] {\Huge{B}};
    \draw (0.25,0.75) node[] {\Huge{C}};    
  \end{tikzpicture}
  \caption{Left: 2x2 texture containing control points for a quadratic Bezier curve per color channel. Middle: The texture as viewed with bilinear sampling. Right: The resulting curves when sampling along the yellow line (Alpha curve omitted).}
  \label{fig:teaser}
}

\maketitle
\thispagestyle{firstpagestyle}

\begin{abstract}
\small
Modern graphics techniques expose internal parameters to allow re-use and to help seperate the technical implementation from the artistic usage cases.  A popular choice is to expose parameters as a customizable curve and to quantize the curve into a texture which either leads to lower quality results, or more texture memory being used to accomodate a higher sampling frequency.  The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for the same costs.  Piecewise curves, B-Splines and Nurbs are mentioned, and there are also limited applications towards vector graphics.
\end{abstract}

%-------------------------------------------------------------------------
\section{Introduction}
\label{sec:introduction}
There are two basic ways for a shader program to gain access to customized curve data.  One way is to evaluate the curve on the CPU at discrete intervals and put those points into a texture that can be used by the GPU.  The other way is to pass curve control point data from the CPU to the shader program as shader constants.

Baking curve points into a texture means that the shader program doesn't need to know what type of curve it was that made the data, but comes at the loss of quality since there are a finite number of curve points sampled, and the data between points is just a linear interpolation between the samples.  If higher quality is desired, you can achieve this by increasing the resolution of the texture to be able to trade accuracy for texture memory.

Passing control point data to a shader program as shader constants allows you to get high quality curve calculations, but comes at the cost of the shader program being written in a very specific way for the type of curve you want to use, as well as more shader program instructions to calculate specific curve points.

\begin{figure}
  \includegraphics[width=5in]{Figure2.png}
  \caption{Left: A quadratic Bezier curve written to the green channel, and it's baked out equivelant using 4 pixels written to the red channel.  Right: The technique from this paper also using 4 pixels, written to the green channel, and the baked out equivelant written to the red channel again for comparison. \label{fig:sampleconfig}}
  \label{fig:quickcomparison}
\end{figure}

This paper shows a third method where:
\begin{itemize}
  \item Curve data is encoded within a texture in such a way to allow the texture sampler to evaluate polynomial basis functions before the data reaches the shader program.
  \item It gives accuracy results closer to that of shader constant curves, while having less calculation overhead.
  \item The technique can support both integral and rational Bezier curves of any order and can also be used for piecewise curves.
  \item The curve type must be decided on in advance, like when using the shader constant method.
  \item There are limited applications towards vector graphics.
\end{itemize}

A quick comparison of the visual quality of these three techniques can be seen in \autoref{fig:quickcomparison}.

TODO: make those bullet points reference forward into sections of the paper

%-------------------------------------------------------------------------
\section{The Technique}
\label{sec:thetechnique}

The core of this technique is that the linear texture interpolation capabilities on the GPU can be mathematically equivelant to De Casteljeau's algorithm for evaluating Bezier curves.

A one dimensional texture with linear sampling results in the evaluation of a linear Bezier curve (order 1), a two dimensional texture with linear sampling can result in a quadratic bezier curve (order 2), and a three dimensional texture (volumetric texture) with linear sampling can result in a cubic Bezier curve (order 3).

The pattern continues for higher dimensionality textures, and curves of lower degrees can be combined to create curves of higher degrees by either continuing De Casteljeau's algorithm in the shader program, or by using the Bernstein form of Bezier curves to combine multiple curve points with fewer operations.

\subsection{Intuition}

The De Casteljeau algorithm shows us that we can find points on a Bezier curve by evaluating a hierarchy of linear interpolations.  For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time t for each interpolation (\autoref{lst:GLSLDeCasteljeau})

\begin{lstlisting}[caption={GLSL De Casteljeau Algorithm For a Quadratic Bezier Curve}, label={lst:GLSLDeCasteljeau}]
float QuadraticBezier (
  in float t,
  in float A,
  in float B,
  in float C
) {
    return mix(mix(A,B,t), mix(B,C,t), t);
}
\end{lstlisting}

Bilinear interpolation is used when linear sampling is enabled and a texture sample is taking from a 2d texture.  Bilinear interpolation is achieved by linearly interpolating across one axis (say, the X axis) and then interpolating the two results by the other axis (the Y axis).

From this, we have an idea of how to set up the points in our texture so that when performing bilinear sampling (\autoref{fig:decasteljeauBilinear}), that we will get, as output, points on a quadratic bezier curve.

  \begin{figure}
    % bezier curve diagram
    \begin{tikzpicture}[x=4cm,y=4cm]
      % border
      \draw (-0.2,-0.2) -- (1.2,-0.2) -- (1.2,1.2) -- (-0.2,1.2) -- (-0.2,-0.2);
      % 1d quadratic bezier curve with control points 0,1,0
      \draw[scale=1,domain=0:1,smooth,variable=\x,blue,line width=0.5mm] plot ({\x},{2*\x-2*\x*\x});    
      % control polygon / labels
      \draw[red,->]       (0.0,0.0) -- (0.5,1.0);
      \draw[darkgreen,->] (0.5,1.0) -- (1.0,0.0);
      \draw[red]          (0.25,0.5) node[anchor=east] {$\overline{AB}$};
      \draw[darkgreen]    (0.75,0.5) node[anchor=west] {$\overline{BC}$};
      % control point labels
      \draw (0.0,0.0) node[anchor=east]  {\bf{A}};
      \draw (0.5,1.0) node[anchor=south] {\bf{B}};
      \draw (1.0,0.0) node[anchor=west]  {\bf{C}};
      % draw a line from AB->AC for time = 0.75
      \draw[orange,->] (0.3,0.6) -- (0.8,0.4);
      \draw[orange] (0.40,0.55) node[anchor=south west] {$\stackrel{\frown}{ABC}$};
      % draw the point at t=0.6 and label underneath the curve
      \draw[black,fill=black] (0.6,0.48) circle (1mm);
      \draw[black] (0.5,0.45) node[anchor=north] {\bf{t}=0.6};
    \end{tikzpicture}
    % bilinear diagram
    \begin{tikzpicture}[x=4cm,y=4cm]
        % border
        \draw (-0.2,-0.2) -- (1.2,-0.2) -- (1.2,1.2) -- (-0.2,1.2) -- (-0.2,-0.2);
        % box
        \draw (0,0) -- (1,0) -- (1,1) -- (0,1) -- (0,0);
        % representative line for where the quadratic bezier curve lives
        \draw[blue,line width=0.5mm] (0,0) -- (1,1);    
        % corner labels
        \draw (0,0) node[anchor=north east] {\bf{A}};
        \draw (1,0) node[anchor=north west] {\bf{B}};     
        \draw (0,1) node[anchor=south east] {\bf{B}};
        \draw (1,1) node[anchor=south west] {\bf{C}};     
        % x axis interpolation
        \draw[red,->]       (0.0,0.1) -- (1.0,0.1);
        \draw[red]          (0.4,0.1) node[anchor=south] {$\overline{AB}$};
        \draw[darkgreen,->] (0.0,0.9) -- (1.0,0.9);
        \draw[darkgreen]    (0.4,0.9) node[anchor=north] {$\overline{BC}$};
        % y axis interpolation
        \draw[orange,->]    (0.6,0.0) -- (0.6,1.0);
        \draw[orange]     (0.6,0.5) node[anchor=west] {$\stackrel{\frown}{ABC}$};
        % draw the point at t=0.6 and label for it
        \draw[black,fill=black] (0.6,0.6) circle (1mm);
        \draw[black] (0.55,0.6) node[anchor=east] {\bf{t}=0.6};
    \end{tikzpicture} 
    \caption{Left: A quadratic Bezier curve evaluated at {\bf{t}}=0.6 for control points A,B,C using the De Casteljeau algorithm.  Right: The De Casteljeau algorithm using bilinear interpolation.  Note that in this case, the X axis is evaluated before the Y, but the Y axis could be evaluated before the X for the same results.}
    \label{fig:decasteljeauBilinear}
  \end{figure}

Since we need to linearly interpolate between {$\overline{AB}$} and {$\overline{BC}$}, and between those results, all by the same time t, we need to ensure that our u coordinate equals our v coordinate.

It can be seen that the actual pixel value in a bilinear sampled texture is in the middle of a pixel.  That means that when calculating our texture coordinates we must sample between pixel location (0.5,0.5) and pixel location (1.5,1.5) to get the correct results.

The common pixel formats contain four color channels – Red, Green, Blue and Alpha – which allows us to be able to evaluate four curves with a single texture read.

\autoref {fig:texbilcurve} shows this in action.

  \begin{figure}
    \begin{tikzpicture}[x=12.5cm,y=4.25cm]
      % border
      \draw (0cm,0cm) -- (12.5cm,0cm) -- (12.5cm,4.25cm) -- (0cm,4.25cm) -- (0cm, 0cm);   
      % raw texture, bilinear sampled texture, curve results
        \node[anchor=south west,inner sep=0] at (0.125cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Texture.png}};
        \node[anchor=south west,inner sep=0] at (4.25cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Bilinear.png}};
        \node[anchor=south west,inner sep=0] at (8.375cm,0.125cm) {\includegraphics[width=4cm,height=4cm]{Figure4Curves.png}};
        % representative line for where the quadratic bezier curve lives
        \draw[yellow,->,line width=0.5mm]    (5.25cm,1.125cm) -- (7.25cm,3.125cm);    
        \draw (0.08,0.25) node[] {\Huge{A}};
        \draw (0.25,0.25) node[] {\Huge{B}};
        \draw (0.08,0.75) node[] {\Huge{B}};
        \draw (0.25,0.75) node[] {\Huge{C}};            
    \end{tikzpicture}
    \caption{Left: a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.  Center: The same texture as viewed when using bilinear texture sampling.  The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve. Right: The curves resulting from sampling along the yellow line (Alpha curve ommited).}   
    \label{fig:texbilcurve}
  \end{figure}

\subsection{Mathematical Basis}

TODO: this section.
TODO: show linear, bilinear, trilinear interpolation to be equivelant!  How to prove for N dimensions?

TODO: find where this text belongs.
While the Bernstein form of Bezier curves is equivelant to evaluating a Bezier curve with the De Casteljeau algorithm, in practice there are differences that come up between the two.  For instance, it is well known that the De Casteljeau algorithm is slower but more numerically robust than evaluating the Bernstein form.

The technique presented in this paper is no different.  While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures.

TODO: give the details of the architecture and cite the two papers cited from the other place!

TODO: show accuracy in practice vs calculated in shader program.  Mention that it's "ok" in practice, better than standard texture baking, and reference the section that gives more information on this accuracy issue and how to improve it?

%-------------------------------------------------------------------------
\section{The Technique}
\label{sec:thetechnique}

While this technique is able to be used with any texture dimensionality, there are different characteristics when using textures of different dimensionalities.  Those characteristics will be explored here.

\subsection{One Dimensional Textures}

One dimensional textures are textures which have N pixels in a single row or column, such as 8x1, 16x1 or more generally Nx1.

Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st order (linear) Bezier basis functions.

That means that if you want a Bezier curve higher than order 1, you are going to have to take more texture samples and combine the results in the shader program.  While this is more expensive computationally, it does have the benefit of doing more of the work in the shader program, which has higher precision, so the end result will be a higher quality curve.

TODO: Flesh out details, show diagram of texture layout.
TODO: Maybe just GLSL for linear and quartic, but images for linear, quadratic, cubic, quartic with comparison vs "ground truth".

\subsection{Two Dimensional Textures}

Two dimensional textures are textures which are MxN pixels in size, such as 8x8 or 16x16 or 32x4.

Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd order (quadratic) Bezier basis functions.

If you want a Bezier curve higher than order 2, once again you are going to have to take more texture samples and combine the results in the shader program.  While more computationally expensive, it again results in higher precision results.

TODO: flesh out details, show diagram of texture layout.
TODO: GLSL for quadratric and quartic, but images for quadratic, cubic, quartic with comparison vs "ground truth".
TODO: explain how linear can still be achieved even if it isn't that useful (yet? Hw/sw)

\subsection{Three Dimensional Textures}

Three dimensional textures (often refered to as volumetric textures) are textures which are MxNxO pixels in size such as 8x8x2 or 16x8x4.

Using three dimensional textures allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier basis functions.

Again, you can take more texture samples and combine the results in the shader program to get higher than order 3 curves if desired.

TODO: flesh out details, show diagram of texture layout.
TODO: GLSL for cubic and quartic, but images for cubic, quartic with comparison vs ground truth.
TODO: explain how linear and quadratic could still be achieved even if it isn't that useful (ye? Hw/sw)
TODO: beyond 3d textures? Could do 4d with mipmapped volumetric textures!

\subsection{Summary of Implications of Texture Dimensionality}

TODO: dimensionality / curve order comparisons. A table? Maybe side by side images?
TODO: texture size changes, number of textures used, number of texture samples taken
TODO: include quadrilinear and above?
TODO: we might want to do this in the performance results section instead and provide perf metrics as well.

%-------------------------------------------------------------------------
\section{Extensions}
\label{sec:extensions}

There are a few ways to extend this technique for more options.

\subsection{Combining Color Channels}

TODO: this.  Higher order curves without more texture reads

\subsection{Piecewise Curves}

TODO: this.  Pros and cons. B-splines can be converted to piecewise Bezier with Boem's algorithm (what's it called again?).

\subsection{Rational Bezier Curves}

TODO: this.
TODO: Nurbs can be converted to rational bezier curves with Boem's algorithm as well

\subsection{Multidimensional Bezier Curves}

TODO: this.  Each color channel is an axis.

%-------------------------------------------------------------------------
\section{Addressing Accuracy Issues}
\label{sec:addressingaccuracyissues}

TODO: this. HW vs SW vs HWSW hybrid vs read points yourself and do math w/o using interpolator. Everythign in between.
TODO: images to show differences.

%-------------------------------------------------------------------------
\section{Limited Applications for Vector Graphics}
\label{sec:limitedapplicationsforvectorgraphics}

TODO: this
TODO: mention that it isn't ideal since this technique is only good if you already know time "t" to evaluate, which is difficult to get otherwise.
TODO: mention that you don't have access to the control points since the interpolator does that level of math for you, but that affine transformations on the resulting curve point is equivelant to doing then on the control points.
TODO: mention 1d curve usage
TODO: mention polar curve usage
TODO: mention use for color gradients
TODO: picture of flag
TODO: put real usages here: particle properties, and whatever else.

%-------------------------------------------------------------------------
\section{Comparisons With Other Techniques}
\label{sec:comparisonswithothertechniques}

TODO: real apples to apples comparisons with texture baking (can be any order!) as well as shader constants.

%-------------------------------------------------------------------------
\section{Performance Characteristics}
\label{sec:performancecharacteristics}

TODO: Show some real performance values. 
TODO: show difference between 3d texture doing cubic, vs 2d texture with 2 texture reads and shader program results.
TODO: show results from multiple GPUs?

%-------------------------------------------------------------------------
\section*{Future Work}
\label{sec:futurework}

TODO: this

%-------------------------------------------------------------------------
\section*{Acknowledgements}
\label{sec:acknowledgements}
TODO: this

%-------------------------------------------------------------------------
\section*{References}
\label{sec:references}
TODO: this

%-------------------------------------------------------------------------
\section*{Index of Supplemental Materials}
\label{sec:indexofsupplementalmaterials}
TODO: this

%-------------------------------------------------------------------------
\section*{Author Contact Information}

\hspace{-2mm}\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
Roy G. Biv \newline
Colortech, Inc. \newline
29 Red Blvd. \newline
New York, NY 10511 \newline
\href{mailto:roy@colortech.com}{roy@colortech.com}
&

Raymond Trace \newline
Graphica University \newline
37 Rue De Lambert \newline
Paris, 75009 France \newline
\href{mailto:rtrace@graphica.edu}{rtrace@graphica.edu} \newline
\href{http://graphica.edu/~rtrace}{http://graphica.edu/\textasciitilde rtrace}

\end{tabular}

\afterdoc

\end{document}

### 2015-06-24 GLFW/Curves/ShaderDefs.h
1d, 2d, 3d texture perf tests

@@ -3,6 +3,7 @@
 //
 //    SHADER_BEGIN(NAME, WIDTH, HEIGHT)
 //        SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+//        SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
 //        SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
 //        SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
 //        SHADER_UNIFORM(NAME)
@@ -24,6 +25,7 @@
 //
 //    Lets you set a uniform in the shader.  NAME is the name of the uniform.  Assumed to be a float!
 //
+//    SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
 //    SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
 //    SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
 //
@@ -100,9 +102,28 @@ SHADER_BEGIN(Quartic3d, 1000, 500)
     SHADER_UNIFORM_TEXTURE_3D(uSampler, float)
 SHADER_END()
 
+SHADER_BEGIN(Texture1d, 1000, 1000)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 1, double)
+    SHADER_UNIFORM_TEXTURE_1D(uSampler, float)
+SHADER_END()
+
+SHADER_BEGIN(Texture2d, 1000, 1000)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
+    SHADER_UNIFORM_TEXTURE_2D(uSampler, float)
+SHADER_END()
+
+SHADER_BEGIN(Texture3d, 1000, 1000)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
+    SHADER_UNIFORM_TEXTURE_3D(uSampler, float)
+SHADER_END()
+
 #undef SHADER_BEGIN
 #undef SHADER_VERTEX_ATTRIBUTE
 #undef SHADER_UNIFORM
[…]

### 2015-06-24 GLFW/Curves/Shader_Texture2d.cpp

@@ -1,0 +1,68 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Texture2d
+//=============================================================================================================
+
+void CShaderTexture2d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        1.0, 0.0,
+        1.0, 1.0,
+        0.0, 0.0,
+        1.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f };
+    const float G[] = { 0.0f , 1.0f, 0.25f };
+    const float B[] = { 0.2f , 0.0f, 1.00f };
+    const float A[] = { 0.75f, 0.0f, 0.29f };
+
+    SetTextureData_uSampler(2, 2, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2]
+    });
+}
+
+const char *CShaderTexture2d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderTexture2d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vTextureCoord).xyz, 1.0);
+    }
+    );
+}
+

### 2015-06-24 GLFW/Curves/Shaders.h

@@ -33,13 +33,22 @@
     public: \
         void SetUniformData_##NAME##(float value) {m_uniform_value_##NAME## = value;} 
 
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+    private: \
+        GLuint m_uniform_##NAME##; \
+        GLuint m_texture_##NAME##; \
+    public: \
+        void SetTextureData_##NAME##(GLsizei width, const std::vector<TYPE>& data) { \
+            m_texture_##NAME## = MakeTexture1D<TYPE>(width, data); \
+        }
+
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
     private: \
         GLuint m_uniform_##NAME##; \
         GLuint m_texture_##NAME##; \
     public: \
         void SetTextureData_##NAME##(GLsizei width, GLsizei height, const std::vector<TYPE>& data) { \
-            m_texture_##NAME## = MakeTexture<TYPE>(width, height, data); \
+            m_texture_##NAME## = MakeTexture2D<TYPE>(width, height, data); \
         }
 
 #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
@@ -64,6 +73,7 @@ enum EShaderTest {
     #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) e_shader##NAME,
     #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
     #define SHADER_UNIFORM(NAME)
+    #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
     #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
     #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
     #define SHADER_END()

### 2015-06-24 GLFW/Curves/main.cpp

@@ -67,6 +67,7 @@ int main(void)
     #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) CShader##NAME shader##NAME##;  shader##NAME##.Init();
     #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
     #define SHADER_UNIFORM(NAME)
+    #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
     #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
     #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
     #define SHADER_END()
@@ -93,6 +94,7 @@ int main(void)
             #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) case e_shader##NAME: shader##NAME##.GetWidthHeight(width,height); break;
             #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
             #define SHADER_UNIFORM(NAME)
+            #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
             #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
             #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
             #define SHADER_END()
@@ -125,6 +127,7 @@ int main(void)
             #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) case e_shader##NAME: sprintf(title,"%s %s",#NAME " - Arrow keys to cycle test", FPS);glfwSetWindowTitle(window, title); break;
             #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
             #define SHADER_UNIFORM(NAME)
+            #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
             #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
             #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
             #define SHADER_END()
@@ -138,6 +141,7 @@ int main(void)
         #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) case e_shader##NAME: shader##NAME##.Render(); break;
         #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
[…]

### 2015-06-24 GLFW/Curves/shaders.cpp

@@ -54,6 +54,9 @@ GLenum GLType<double>()
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_texture_##NAME## = -1;
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+        m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
+        m_texture_##NAME## = -1;
 #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_texture_##NAME## = -1;
@@ -67,6 +70,8 @@ GLenum GLType<double>()
         glDeleteProgram(m_program);
 #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
 #define SHADER_UNIFORM(NAME)
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+        glDeleteTextures(1, &m_texture_##NAME##);
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
         glDeleteTextures(1, &m_texture_##NAME##);
 #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
@@ -85,6 +90,10 @@ GLenum GLType<double>()
         glVertexAttribPointer(m_attr_##NAME##, ELEMENTSIZE, GLType<TYPE>(), false, 0, 0);
 #define SHADER_UNIFORM(NAME) \
         glUniform1f(m_uniform_##NAME##, m_uniform_value_##NAME##);
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+        glActiveTexture(GL_TEXTURE0 + texIndex); \
+        glBindTexture(GL_TEXTURE_1D, m_texture_##NAME##); \
+        glUniform1i(m_uniform_##NAME##, texIndex++);
 #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
         glActiveTexture(GL_TEXTURE0 + texIndex); \
         glBindTexture(GL_TEXTURE_2D, m_texture_##NAME##); \

### 2015-06-24 GLFW/Curves/utils.cpp

@@ -81,7 +81,35 @@ GLuint MakeBuffer<float>(const std::vector<float>& data)
 
 //=============================================================================================================
 template<>
-GLuint MakeTexture<unsigned char>(GLsizei width, GLsizei height, const std::vector<unsigned char>& data)
+GLuint MakeTexture1D<unsigned char>(GLsizei width, const std::vector<unsigned char>& data)
+{
+    GLuint texture = 0;
+    glCreateTextures(GL_TEXTURE_1D, 1, &texture);
+    glBindTexture(GL_TEXTURE_1D, texture);
+    glTexImage1D(GL_TEXTURE_1D, 0, GL_RGBA, width, 0, GL_RGBA, GL_UNSIGNED_BYTE, &data[0]);
+    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, GL_LINEAR);
+    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, GL_LINEAR);
+    glBindTexture(GL_TEXTURE_1D, NULL);
+    return texture;
+}
+
+//=============================================================================================================
+template<>
+GLuint MakeTexture1D<float>(GLsizei width, const std::vector<float>& data)
+{
+    GLuint texture = 0;
+    glCreateTextures(GL_TEXTURE_1D, 1, &texture);
+    glBindTexture(GL_TEXTURE_1D, texture);
+    glTexImage1D(GL_TEXTURE_1D, 0, GL_RGBA32F, width, 0, GL_RGBA, GL_FLOAT, &data[0]);
+    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, GL_LINEAR);
+    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, GL_LINEAR);
+    glBindTexture(GL_TEXTURE_1D, NULL);
+    return texture;
+}
+
+//=============================================================================================================
+template<>
+GLuint MakeTexture2D<unsigned char>(GLsizei width, GLsizei height, const std::vector<unsigned char>& data)
 {
     GLuint texture = 0;
     glCreateTextures(GL_TEXTURE_2D, 1, &texture);
@@ -95,7 +123,7 @@ GLuint MakeTexture<unsigned char>(GLsizei width, GLsizei height, const std::vect
 
 //=============================================================================================================
 template<>
[…]

### 2015-06-24 GLFW/Curves/utils.h

@@ -12,7 +12,10 @@ template<typename T>
 GLuint MakeBuffer(const std::vector<T>& data);
 
 template<typename T>
-GLuint MakeTexture(GLsizei width, GLsizei height, const std::vector<T>& data);
+GLuint MakeTexture1D(GLsizei width, const std::vector<T>& data);
+
+template<typename T>
+GLuint MakeTexture2D(GLsizei width, GLsizei height, const std::vector<T>& data);
 
 template<typename T>
 GLuint MakeTexture3D(GLsizei width, GLsizei height, GLsizei depth, const std::vector<T>& data);
@@ -27,9 +30,14 @@ template<>
 GLuint MakeBuffer<float>(const std::vector<float>& data);
 
 template<>
-GLuint MakeTexture<unsigned char>(GLsizei width, GLsizei height, const std::vector<unsigned char>& data);
+GLuint MakeTexture1D<unsigned char>(GLsizei width, const std::vector<unsigned char>& data);
 template<>
-GLuint MakeTexture<float>(GLsizei width, GLsizei height, const std::vector<float>& data);
+GLuint MakeTexture1D<float>(GLsizei width, const std::vector<float>& data);
+
+template<>
+GLuint MakeTexture2D<unsigned char>(GLsizei width, GLsizei height, const std::vector<unsigned char>& data);
+template<>
+GLuint MakeTexture2D<float>(GLsizei width, GLsizei height, const std::vector<float>& data);
 
 template<>
 GLuint MakeTexture3D<unsigned char>(GLsizei width, GLsizei height, GLsizei depth, const std::vector<unsigned char>& data);

### 2015-06-24 GLFW/Curves/ShaderDefs.h
Added some more shader perf tests

@@ -3,9 +3,9 @@
 //
 //    SHADER_BEGIN(NAME, WIDTH, HEIGHT)
 //        SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
-//        SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
-//        SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
-//        SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
+//        SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
+//        SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP)
+//        SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP)
 //        SHADER_UNIFORM(NAME)
 //    SHADER_END()
 //
@@ -25,12 +25,13 @@
 //
 //    Lets you set a uniform in the shader.  NAME is the name of the uniform.  Assumed to be a float!
 //
-//    SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
-//    SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
-//    SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
+//    SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
+//    SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP)
+//    SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP)
 //
 //    Defines a shader uniform.  Also defines a texture to assign to it.  NAME is the name of the uniform as
-//    defined in the shader.  Call SetTextureData_<NAME> to set the texture data.
+//    defined in the shader.  Call SetTextureData_<NAME> to set the texture data. If LERP is true, it uses
+//    linear sampling, else uses nearest.
 //
 //    Type can be float or unsigned char. floats should be 0..1, unsigned char should be 0..255
 //
@@ -41,83 +42,107 @@
 SHADER_BEGIN(BilinearTest, 1000, 500)
     SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
[…]

### 2015-06-24 GLFW/Curves/Shader_BilinearTest2.cpp

@@ -1,0 +1,67 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            BilinearTest2
+//=============================================================================================================
+
+void CShaderBilinearTest2::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        1.0, 0.0,
+        1.0, 1.0,
+        0.0, 0.0,
+        1.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+
+    SetTextureData_uSampler(2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderBilinearTest2::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderBilinearTest2::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vec2((vTextureCoord.x + 0.5) / 2.0)).xyz,1.0);
+    }
+    );
+}
+

### 2015-06-24 GLFW/Curves/Shader_TrilinearTest2.cpp

@@ -1,0 +1,71 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            TrilinearTest2
+//=============================================================================================================
+
+void CShaderTrilinearTest2::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0, 0.0,
+        1.0, 0.0, 0.0,
+        1.0, 1.0, 0.0,
+        0.0, 0.0, 0.0,
+        1.0, 1.0, 0.0,
+        0.0, 1.0, 0.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+    float D = 0.1f;
+
+    SetTextureData_uSampler(2, 2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+        C, 0.0f, 0.0f, 0.0f,     D, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderTrilinearTest2::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec3 aTextureCoord;
+
+    out vec3 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderTrilinearTest2::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler3D uSampler;
+    
+    in vec3 vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vec3((vTextureCoord.x + 0.5) / 2.0)).xyz, 1.0);
+    }
+    );
+}
+

### 2015-06-24 GLFW/Curves/Shaders.h

@@ -33,31 +33,31 @@
     public: \
         void SetUniformData_##NAME##(float value) {m_uniform_value_##NAME## = value;} 
 
-#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP) \
     private: \
         GLuint m_uniform_##NAME##; \
         GLuint m_texture_##NAME##; \
     public: \
         void SetTextureData_##NAME##(GLsizei width, const std::vector<TYPE>& data) { \
-            m_texture_##NAME## = MakeTexture1D<TYPE>(width, data); \
+            m_texture_##NAME## = MakeTexture1D<TYPE>(width, LERP, data); \
         }
 
-#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP) \
     private: \
         GLuint m_uniform_##NAME##; \
         GLuint m_texture_##NAME##; \
     public: \
         void SetTextureData_##NAME##(GLsizei width, GLsizei height, const std::vector<TYPE>& data) { \
-            m_texture_##NAME## = MakeTexture2D<TYPE>(width, height, data); \
+            m_texture_##NAME## = MakeTexture2D<TYPE>(width, height, LERP, data); \
         }
 
-#define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP) \
     private: \
         GLuint m_uniform_##NAME##; \
         GLuint m_texture_##NAME##; \
     public: \
         void SetTextureData_##NAME##(GLsizei width, GLsizei height, GLsizei depth, const std::vector<TYPE>& data) { \
-            m_texture_##NAME## = MakeTexture3D<TYPE>(width, height, depth, data); \
+            m_texture_##NAME## = MakeTexture3D<TYPE>(width, height, depth, LERP, data); \
         }
 
 #define SHADER_END() \
@@ -73,9 +73,9 @@ enum EShaderTest {
     #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) e_shader##NAME,
[…]

### 2015-06-24 GLFW/Curves/main.cpp

@@ -67,9 +67,9 @@ int main(void)
     #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) CShader##NAME shader##NAME##;  shader##NAME##.Init();
     #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
     #define SHADER_UNIFORM(NAME)
-    #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
-    #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
-    #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
+    #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
+    #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP)
+    #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP)
     #define SHADER_END()
     #include "ShaderDefs.h"
 
@@ -94,9 +94,9 @@ int main(void)
             #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) case e_shader##NAME: shader##NAME##.GetWidthHeight(width,height); break;
             #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
             #define SHADER_UNIFORM(NAME)
-            #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE)
-            #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE)
-            #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE)
+            #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
+            #define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP)
+            #define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP)
             #define SHADER_END()
             #include "ShaderDefs.h"
             }
@@ -115,7 +115,7 @@ int main(void)
         if (currentTime - lastFPSTime > 1.0) {
             double elapsed = currentTime - lastFPSTime;
             float fps = float(frameCount) / float(elapsed);
-            sprintf(FPS, "(FPS: %0.1f / ms: %0.2f", fps, 1000.0 / fps);
[…]

### 2015-06-24 GLFW/Curves/shaders.cpp

@@ -51,13 +51,13 @@ GLenum GLType<double>()
 #define SHADER_UNIFORM(NAME) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_uniform_value_##NAME## = 0.0f;
-#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_texture_##NAME## = -1;
-#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_texture_##NAME## = -1;
-#define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP) \
         m_uniform_##NAME## = glGetUniformLocation(m_program, #NAME); \
         m_texture_##NAME## = -1;
 #define SHADER_END() \
@@ -70,11 +70,11 @@ GLenum GLType<double>()
         glDeleteProgram(m_program);
 #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
 #define SHADER_UNIFORM(NAME)
-#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP) \
         glDeleteTextures(1, &m_texture_##NAME##);
-#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP) \
         glDeleteTextures(1, &m_texture_##NAME##);
-#define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE) \
+#define SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP) \
         glDeleteTextures(1, &m_texture_##NAME##);
 #define SHADER_END() \
     } 
@@ -90,15 +90,15 @@ GLenum GLType<double>()
[…]

### 2015-06-24 GLFW/Curves/utils.cpp

@@ -81,84 +81,90 @@ GLuint MakeBuffer<float>(const std::vector<float>& data)
 
 //=============================================================================================================
 template<>
-GLuint MakeTexture1D<unsigned char>(GLsizei width, const std::vector<unsigned char>& data)
+GLuint MakeTexture1D<unsigned char>(GLsizei width, bool lerpSample, const std::vector<unsigned char>& data)
 {
+    GLint sampling = lerpSample ? GL_LINEAR : GL_NEAREST;
     GLuint texture = 0;
     glCreateTextures(GL_TEXTURE_1D, 1, &texture);
     glBindTexture(GL_TEXTURE_1D, texture);
     glTexImage1D(GL_TEXTURE_1D, 0, GL_RGBA, width, 0, GL_RGBA, GL_UNSIGNED_BYTE, &data[0]);
-    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, GL_LINEAR);
-    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, GL_LINEAR);
+    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, sampling);
+    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, sampling);
     glBindTexture(GL_TEXTURE_1D, NULL);
     return texture;
 }
 
 //=============================================================================================================
 template<>
-GLuint MakeTexture1D<float>(GLsizei width, const std::vector<float>& data)
+GLuint MakeTexture1D<float>(GLsizei width, bool lerpSample, const std::vector<float>& data)
 {
+    GLint sampling = lerpSample ? GL_LINEAR : GL_NEAREST;
     GLuint texture = 0;
     glCreateTextures(GL_TEXTURE_1D, 1, &texture);
     glBindTexture(GL_TEXTURE_1D, texture);
     glTexImage1D(GL_TEXTURE_1D, 0, GL_RGBA32F, width, 0, GL_RGBA, GL_FLOAT, &data[0]);
-    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MAG_FILTER, GL_LINEAR);
-    glTexParameteri(GL_TEXTURE_1D, GL_TEXTURE_MIN_FILTER, GL_LINEAR);
[…]

### 2015-06-24 GLFW/Curves/utils.h

@@ -12,13 +12,13 @@ template<typename T>
 GLuint MakeBuffer(const std::vector<T>& data);
 
 template<typename T>
-GLuint MakeTexture1D(GLsizei width, const std::vector<T>& data);
+GLuint MakeTexture1D(GLsizei width, bool lerpSample, const std::vector<T>& data);
 
 template<typename T>
-GLuint MakeTexture2D(GLsizei width, GLsizei height, const std::vector<T>& data);
+GLuint MakeTexture2D(GLsizei width, GLsizei height, bool lerpSample, const std::vector<T>& data);
 
 template<typename T>
-GLuint MakeTexture3D(GLsizei width, GLsizei height, GLsizei depth, const std::vector<T>& data);
+GLuint MakeTexture3D(GLsizei width, GLsizei height, GLsizei depth, bool lerpSample, const std::vector<T>& data);
 
 //=============================================================================================================
 // Template Specializations
@@ -30,17 +30,17 @@ template<>
 GLuint MakeBuffer<float>(const std::vector<float>& data);
 
 template<>
-GLuint MakeTexture1D<unsigned char>(GLsizei width, const std::vector<unsigned char>& data);
+GLuint MakeTexture1D<unsigned char>(GLsizei width, bool lerpSample, const std::vector<unsigned char>& data);
 template<>
-GLuint MakeTexture1D<float>(GLsizei width, const std::vector<float>& data);
+GLuint MakeTexture1D<float>(GLsizei width, bool lerpSample, const std::vector<float>& data);
 
 template<>
-GLuint MakeTexture2D<unsigned char>(GLsizei width, GLsizei height, const std::vector<unsigned char>& data);
+GLuint MakeTexture2D<unsigned char>(GLsizei width, GLsizei height, bool lerpSample, const std::vector<unsigned char>& data);
 template<>
-GLuint MakeTexture2D<float>(GLsizei width, GLsizei height, const std::vector<float>& data);
+GLuint MakeTexture2D<float>(GLsizei width, GLsizei height, bool lerpSample, const std::vector<float>& data);
 
 template<>
-GLuint MakeTexture3D<unsigned char>(GLsizei width, GLsizei height, GLsizei depth, const std::vector<unsigned char>& data);
+GLuint MakeTexture3D<unsigned char>(GLsizei width, GLsizei height, GLsizei depth, bool lerpSample, const std::vector<unsigned char>& data);
 template<>
[…]

### 2015-06-24 Paper/paper.tex
mathematical basis WIP

@@
 \usepackage{tikz}
+\usepackage{amsmath}
 \definecolor{darkgreen}{RGB}{0,192,0}
@@
 
-TODO: this section.
-TODO: show linear, bilinear, trilinear interpolation to be equivelant!  How to prove for N dimensions?
+The De Casteljeau algorithm is equivelant to the Bernstein form of Bezier curves (\autoref{eqn:bernsteinform}) which means that the Bernstein form must be able to be eqvaluated by linear, bilinear, trilinear, and N-Linear interpolation.
+
+\begin{equation}
+\bf{P} = \sum\limits_{i=0}^n\binom {n} {i}s^{n-i}t^i\text{\bf{P}}_i
+\label{eqn:bernsteinform}
+\end{equation}
+
+When n is 1, to make a linear Bezier curve, the equation we get out is in fact just linear interpolation (\autoref{eqn:bernsteinformn1}).  Note that in the Berntstein form, s is equivelant to 1-t.
+
+\begin{equation}
+\bf{P} = s*P_0 + t*P_1
+\label{eqn:bernsteinformn1}
+\end{equation}
+
+When n is 2, to make a quadratic Bezier curve, things are not quite as obvious:
+
+TODO: finish this section.
+TODO: show linear, bilinear, trilinear interpolation to be equivelant!
+TODO: How to prove for N dimensions?
+
+\subsection{Accuracy}
 

### 2015-06-24 Paper/paper.tex
mathematical basis v1

--- 2015-06-23 Paper/paper.tex
@@
 The De Casteljeau algorithm shows us that we can find points on a Bezier curve by evaluating a hierarchy of linear interpolations.
-For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time t for each interpolation (\autoref{lst:GLSLDeCasteljeau})
+For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time $t$ for each interpolation (\autoref{lst:GLSLDeCasteljeau})
 
@@
 
-Since we need to linearly interpolate between {$\overline{AB}$} and {$\overline{BC}$}, and between those results, all by the same time t, we need to ensure that our u coordinate equals our v coordinate.
+Since we need to linearly interpolate between {$\overline{AB}$} and {$\overline{BC}$}, and between those results, all by the same time $t$, we need to ensure that our $u$ coordinate equals our $v$ coordinate.
 
 It can be seen that the actual pixel value in a bilinear sampled texture is in the middle of a pixel.
-That means that when calculating our texture coordinates we must sample between pixel location (0.5,0.5) and pixel location (1.5,1.5) to get the correct results.
+That means that when calculating our texture coordinates we must sample between pixel location $(0.5,0.5)$ and pixel location $(1.5,1.5)$ to get the correct results.
 
@@
 
-TODO: this section.
-TODO: show linear, bilinear, trilinear interpolation to be equivelant!  How to prove for N dimensions?
+The De Casteljeau algorithm is equivelant to the Bernstein form of Bezier curves.
 
-TODO: find where this text belongs.
+\begin{equation}
+\bf{P(t)} = \sum\limits_{i=0}^n\binom {n} {i}(1-t)^{n-i}t^i\text{\bf{P}}_i
+\label{eqn:bernsteinform}
+\end{equation}
+
+That they are equivelant means that the Bernstein form for a given $n$ must also be able to be evaluated by $n$-Linear interpolation.
+A linear curve should be able to be evaluated by linear interpolation, a quadratic curve should be able to be evaluated by bilinear interpolation, a cubic curve should be able to be evaluated by trilinear interpolation, and so on.
+
+When $n$ is $1$, to make a linear Bezier curve, the equation we get out is in fact just linear interpolation, so we can see that it's true in that case.
+
+\begin{equation}
+\bf{P(t)} = P_0(1-t) + P_1t
+\label{eqn:bernsteinformn1}
+\end{equation}
+
+When $n$ is $2$, to make a quadratic Bezier curve with bilinear interpolation, the relationship is not as obvious.
+
+\begin{equation}
+\bf{P(t)} = P_0(1-t)^2 + P_12(1-t)t + P_2t^2
+\label{eqn:bernsteinformn2}
+\end{equation}
+
+To see how that equation can be the same as bilinear interpolation, let's start with the equation for bilinear interpolation, which is just a linear interpolation between two other linear interpolations.
+We'll use $t$ and $u$ as the interpolation weights of each interpolation.
+
+\begin{equation}
+\begin{split}
+\bf{E(u)} = P_0*(1-u) + P_1*u \\
+\bf{F(u)} = P_2*(1-u) + P_3*u \\
+\bf{P(t,u)} = E(u)*(1-t) + F(u)*t \\
+\bf{P(t,u)} = (P_0*(1-u) + P_1*u)*(1-t) + (P_2*(1-u) + P_3*u)*t
+\end{split}
+\label{eqn:bilinearinterpolation}
+\end{equation}
+
+In our usage case of bilinear interpolation to evaluate Bernstein polynomials, $P_0$ will be $A$, $P_1$ and $P_2$ will both be $B$, and $P_3$ will be $C$.
+Also, $t$ and $u$ are the same in our usage case so we'll just replace $u$ with $t$.
+We will also replace $(1-t)$ with $s$ for readability.
+
+\begin{equation}
+\begin{split}
+\bf{P(t)} = (A*s+B*t)*s + (B*s+C*t)*t \\
+\bf{P(t)} = A*s^2+B*st + B*st+C*t^2 \\
+\bf{P(t)} = A*s^2+B*2st+C*t^2
+\end{split}
+\label{eqn:bilinearinterpolation2}
+\end{equation}
+
+If we replace $A$,$B$,$C$ with $P_0$, $P_1$, $P_2$, and $s$ with $(1-t)$ we then get the familiar equation back out.
+
+\begin{equation}
+\bf{P(t)} = P_0(1-t)^2+P_12(1-t)t+P_2t^2
+\label{eqn:bilinearinterpolation3}
+\end{equation}
+
+This pattern continues for trilinear interpolation and beyond
+
+TODO: How to prove for N dimensions?  This section needs help
+
+\subsection{Accuracy}
+
 While the Bernstein form of Bezier curves is equivelant to evaluating a Bezier curve with the De Casteljeau algorithm, in practice there are differences that come up between the two.
@@
 
-The technique presented in this paper is no different.
+The technique presented in this paper also has numeric differences in practice.
 While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures.
+
+As shown in \autoref{fig:texbilcurve}, the quality can be significantly higher than a baked out curve for the same number of pixels however.
+There is more information on addressing accuracy in \autoref{sec:addressingaccuracyissues}.
 
@@
 
-TODO: show accuracy in practice vs calculated in shader program.
-Mention that it's "ok" in practice, better than standard texture baking, and reference the section that gives more information on this accuracy issue and how to improve it?
+TODO: Show a zoomed in version of curves with this technique, vs the real curve
 

### 2015-06-25 Paper/paper.tex
some paper clean up

@@
   \end{tikzpicture}
-  \caption{Left: 2x2 texture containing control points for a quadratic Bezier curve per color channel.
-Middle: The texture as viewed with bilinear sampling.
-Right: The resulting curves when sampling along the yellow line (Alpha curve omitted).}
+  \caption{\textit{Left:} 2x2 texture containing control points for a quadratic Bezier curve in each color channel.
+\textit{Middle:} The texture as viewed with bilinear sampling.
+\textit{Right:} The resulting curves when sampling along the yellow line (Alpha curve omitted).}
   \label{fig:teaser}
@@
 \small
-Modern graphics techniques expose internal parameters to allow re-use and to help seperate the technical implementation from the artistic usage cases.
-A popular choice is to expose parameters as a customizable curve and to quantize the curve into a texture which either leads to lower quality results, or more texture memory being used to accomodate a higher sampling frequency.
+Modern graphics techniques expose internal parameters to allow re-use and to help seperate the technical implementation from artistic usage cases.
+A popular choice is to expose parameters as customizable curves and to quantize the curves into textures.
+This leads to either lower quality results, or more texture memory being used to accomodate higher sampling frequencies.
 The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for the same costs.
@@
 
-Baking curve points into a texture means that the shader program doesn't need to know what type of curve it was that made the data, but comes at the loss of quality since there are a finite number of curve points sampled, and the data between points is just a linear interpolation between the samples.
+Baking curve points into a texture means that the shader program doesn't need to know what type of curve it was that made the data, nor how many control points it has, but comes at the loss of quality since there are a finite number of curve points sampled, and the data between points is just a linear interpolation between the samples.
 If higher quality is desired, you can achieve this by increasing the resolution of the texture to be able to trade accuracy for texture memory.
@@
   \includegraphics[width=5in]{Figure2.png}
-  \caption{Left: A quadratic Bezier curve written to the green channel, and it's baked out equivelant using 4 pixels written to the red channel.
-Right: The technique from this paper also using 4 pixels, written to the green channel, and the baked out equivelant written to the red channel again for comparison.
+  \caption{\textit{Left:} A quadratic Bezier curve written to the green channel, and the baked out equivelant using 4 pixels written to the red channel.
+\textit{Right:} The technique from this paper, also using 4 pixels, written to the green channel, and the baked out equivelant written to the red channel again for comparison.
 \label{fig:sampleconfig}}
@@
 \begin{itemize}
-  \item Curve data is encoded within a texture in such a way to allow the texture sampler to evaluate polynomial basis functions before the data reaches the shader program.
+  \item Curve data is encoded within a texture in such a way to allow the texture sampler to calculate points on the curve before the data reaches the shader program.
   \item It gives accuracy results closer to that of shader constant curves, while having less calculation overhead.
@@
 A quick comparison of the visual quality of these three techniques can be seen in \autoref{fig:quickcomparison}.
-
-TODO: make those bullet points reference forward into sections of the paper
 
@@
 
-The pattern continues for higher dimensionality textures, and curves of lower degrees can be combined to create curves of higher degrees by either continuing De Casteljeau's algorithm in the shader program, or by using the Bernstein form of Bezier curves to combine multiple curve points with fewer operations.
+The pattern continues for higher dimensionality textures, and curves of lower degrees can be combined in the shader program to create curves of higher degrees by either continuing De Casteljeau's algorithm or by using the Bernstein form of Bezier curves.
 
@@
 The De Casteljeau algorithm shows us that we can find points on a Bezier curve by evaluating a hierarchy of linear interpolations.
-For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time $t$ for each interpolation (\autoref{lst:GLSLDeCasteljeau})
+For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time $t$ for each interpolation (\autoref{lst:GLSLDeCasteljeau}).
 
@@
 Bilinear interpolation is achieved by linearly interpolating across one axis (say, the X axis) and then interpolating the two results by the other axis (the Y axis).
+In bilinear interpolation, you have a $t$ and a $u$ interpolation value, and you have four values to interpolate between $A$,$B$,$C$,$D$ (\autoref{lst:GLSLBilinear}).
 
-From this, we have an idea of how to set up the points in our texture so that when performing bilinear sampling (\autoref{fig:decasteljeauBilinear}), that we will get, as output, points on a quadratic bezier curve.
+\begin{lstlisting}[caption={GLSL implementation of bilinear interpolation between four floats}, label={lst:GLSLBilinear}]
+float BilinearInterpolate (
+  in float u,
+  in float v,
+  in float A,
+  in float B,
+  in float C,
+  in float D
+) {
+    return mix(mix(A,B,u), mix(C,D,u), v);
+}
+\end{lstlisting}
+
+Comparing the source code for these two operations, we begin to get an idea of how to set up the points in our texture and the u and v coordinates to use such that when performing bilinear sampling, that we will get, as output, points on a quadratic bezier curve (\autoref{fig:decasteljeauBilinear}).
 
@@
 
-The common pixel formats contain four color channels – Red, Green, Blue and Alpha – which allows us to be able to evaluate four curves with a single texture read.
-
-\autoref {fig:texbilcurve} shows this in action.
+The common pixel formats contain four color channels – Red, Green, Blue and Alpha – which allows us to be able to evaluate four curves with a single texture read (\autoref{fig:texbilcurve}).
 
@@
 While the Bernstein form of Bezier curves is equivelant to evaluating a Bezier curve with the De Casteljeau algorithm, in practice there are differences that come up between the two.
-For instance, it is well known that the De Casteljeau algorithm is slower but more numerically robust than evaluating the Bernstein form.
+It is well known that the De Casteljeau algorithm is slower but more numerically robust than evaluating the Bernstein form.
 
-The technique presented in this paper also has numeric differences in practice.
+The technique presented in this paper also has numerical differences in practice.
 While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures.
@@
 %-------------------------------------------------------------------------
-\section{The Technique}
-\label{sec:thetechnique}
+\section{Implications of Texture Dimensionality}
+\label{sec:implicationsoftexturedimensionality}
 

### 2015-06-25 Paper/Figures/FigTexture1D.tex
Paper: added accuracy diagrams, combined glsl listings

--- 2015-06-22 Paper/Figures/Figure2.tex
@@
 \usepackage{tikz}
+\usepackage{tkz-euclide}
 \definecolor{darkgreen}{RGB}{0,192,0}
@@
 
-	\usetikzlibrary{arrows.meta}
-	\tikzset{>={Latex[width=3mm,length=3mm]}}
+	\begin{figure}
+		\begin{tikzpicture}[x=8cm,y=4cm]
+			\tkzInit[xmax=2,ymax=1,xmin=0,ymin=0]
+			% border
+			\draw (-0.1,-0.2) rectangle (2,1.2);
 
-	\begin{figure}
-		\begin{tikzpicture}[x=12.5cm,y=4cm]
-			% raw texture, bilinear sampled texture, curve results
-		    \node[anchor=south west,inner sep=0] at (0,0) {\includegraphics[width=4cm,height=4cm]{Figure2Texture.png}};
-		    \node[anchor=south west,inner sep=0] at (4.125cm,0) {\includegraphics[width=4cm,height=4cm]{Figure2Bilinear.png}};
-		    \node[anchor=south west,inner sep=0] at (8.25cm,0) {\includegraphics[width=4cm,height=4cm]{Figure2Curves.png}};
-		    % representative line for where the quadratic bezier curve lives
-		    \draw[yellow,->,line width=0.5mm]    (5.125cm,1cm) -- (7.125cm,3cm);    
+			\foreach \x in {0,...,4}
+				\draw (\x * 0.1 - 0.05,0.45) rectangle (\x * 0.1 + 0.05, 0.55);
+
 		\end{tikzpicture}
-		\caption{Left: a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.
-Center: The same texture as viewed when using bilinear texture sampling.
-The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve.
-Right: The curve resulting from sampling along the yellow line.}
+		\caption{TODO: this}		
 	\end{figure}

### 2015-06-25 Paper/paper.tex
Paper: added accuracy diagrams, combined glsl listings

@@
 The De Casteljeau algorithm shows us that we can find points on a Bezier curve by evaluating a hierarchy of linear interpolations.
-For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time $t$ for each interpolation (\autoref{lst:GLSLDeCasteljeau}).
+For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time $t$ for each interpolation.
 
-\begin{lstlisting}[caption={GLSL De Casteljeau Algorithm For a Quadratic Bezier Curve}, label={lst:GLSLDeCasteljeau}]
+Bilinear interpolation is used when linear sampling is enabled and a texture sample is taking from a 2d texture.
+Bilinear interpolation is achieved by linearly interpolating across one axis (say, the X axis) and then interpolating the two results by the other axis (the Y axis).
+In bilinear interpolation, you have a $t$ and a $u$ interpolation value, and you have four values to interpolate between $A$,$B$,$C$,$D$.
+
+\begin{lstlisting}[caption={GLSL implementation of bilinear interpolation and the De Casteljeau algorithm for a quadratic Bezier curve.}, label={lst:GLSLCurves}]
+float BilinearInterpolate (
+  in float u, in float v,
+  in float A, in float B, in float C, in float D
+) {
+    return mix(mix(A,B,u), mix(C,D,u), v);
+}
+
 float QuadraticBezier (
   in float t,
-  in float A,
-  in float B,
-  in float C
+  in float A, in float B, in float C
 ) {
@@
 
-Bilinear interpolation is used when linear sampling is enabled and a texture sample is taking from a 2d texture.
-Bilinear interpolation is achieved by linearly interpolating across one axis (say, the X axis) and then interpolating the two results by the other axis (the Y axis).
-In bilinear interpolation, you have a $t$ and a $u$ interpolation value, and you have four values to interpolate between $A$,$B$,$C$,$D$ (\autoref{lst:GLSLBilinear}).
-
-\begin{lstlisting}[caption={GLSL implementation of bilinear interpolation between four floats}, label={lst:GLSLBilinear}]
-float BilinearInterpolate (
-  in float u,
-  in float v,
-  in float A,
-  in float B,
-  in float C,
-  in float D
-) {
-    return mix(mix(A,B,u), mix(C,D,u), v);
-}
-\end{lstlisting}
-
-Comparing the source code for these two operations, we begin to get an idea of how to set up the points in our texture and the u and v coordinates to use such that when performing bilinear sampling, that we will get, as output, points on a quadratic bezier curve (\autoref{fig:decasteljeauBilinear}).
+Comparing the source code for these two operations  (\autoref{lst:GLSLCurves}), we begin to get an idea of how to set up the points in our texture and the u and v coordinates to use such that when performing bilinear sampling, that we will get, as output, points on a quadratic bezier curve (\autoref{fig:decasteljeauBilinear}).
 
@@
     \end{tikzpicture} 
-    \caption{Left: A quadratic Bezier curve evaluated at {\bf{t}}=0.6 for control points A,B,C using the De Casteljeau algorithm.
-Right: The De Casteljeau algorithm using bilinear interpolation.
+    \caption{\textit{Left:} A quadratic Bezier curve evaluated at {\bf{t}}=0.6 for control points A,B,C using the De Casteljeau algorithm.
+\textit{Right:} The De Casteljeau algorithm using bilinear interpolation.
 Note that in this case, the X axis is evaluated before the Y, but the Y axis could be evaluated before the X for the same results.}
@@
     \end{tikzpicture}
-    \caption{Left: a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.
-Center: The same texture as viewed when using bilinear texture sampling.
+    \caption{\textit{Left:} a 2x2 texture storing control points for a quadratic Bezier curve in each color channel.
+\textit{Middle:} The same texture as viewed when using bilinear texture sampling.
 The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve.
-Right: The curves resulting from sampling along the yellow line (Alpha curve ommited).}
+\textit{Right:} The curves resulting from sampling along the yellow line (Alpha curve ommited).}
     \label{fig:texbilcurve}
@@
 The technique presented in this paper also has numerical differences in practice.
-While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures.
+While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures (\autoref{fig:quickaccuracy}).
 
@@
 
-TODO: give the details of the architecture and cite the two papers cited from the other place!
+  \begin{figure}
+    \begin{tikzpicture}[x=12cm,y=4cm]
+      % border
+      \draw (0cm,0cm) rectangle (12cm,4cm);
+      % raw texture, bilinear sampled texture, curve results
+        \node[anchor=south west,inner sep=0] at (0cm,0cm) {\includegraphics[width=4cm,height=4cm]{HighQuality.png}};
+        \node[anchor=south west,inner sep=0] at (4cm,0cm) {\includegraphics[width=4cm,height=4cm]{HighQualityZoom.png}};
+        \node[anchor=south west,inner sep=0] at (8cm,0cm) {\includegraphics[width=4cm,height=4cm]{LowQualityZoom.png}};
+        % representative line for where the quadratic bezier curve lives
+        \draw[yellow] (0.11,0.35) rectangle (0.21,0.65);
 
-TODO: Show a zoomed in version of curves with this technique, vs the real curve
+    \end{tikzpicture}
+    \caption{\textit{Left:} Sampled curves.
+\textit{Middle:} Zooming in on a curve calculated with shader program constants.
+\textit{Right:} Zooming in on a curve calculated using the method in this paper}
+    \label{fig:quickaccuracy}
+  \end{figure}
+
+TODO: give the details of the architecture imprecision sources and cite the two papers cited from the other place!
 
 %-------------------------------------------------------------------------
-\section{Implications of Texture Dimensionality}
-\label{sec:implicationsoftexturedimensionality}
+\section{Texture Dimensionality}
+\label{sec:texturedimensionality}
 
-While this technique is able to be used with any texture dimensionality, there are different characteristics when using textures of different dimensionalities.
-Those characteristics will be explored here.
+While this technique is able to be used with any texture dimensionality, there are different characteristics for each choice.  Those characteristics will be explored here.
 
@@
 
-That means that if you want a Bezier curve higher than order 1, you are going to have to take more texture samples and combine the results in the shader program.
-While this is more expensive computationally, it does have the benefit of doing more of the work in the shader program, which has higher precision, so the end result will be a higher quality curve.
+If you want a Bezier curve higher than order 1, you are going to have to take more texture samples and combine the results in the shader program.
+While this is more expensive computationally, it does have the benefit of doing more of the work in the shader program, which has higher precision through use of full float math, so the end result will be a higher quality curve.
 

### 2015-06-27 GLFW/Curves/ShaderDefs.h
Adding 1d quadratic, cubic, quartic. shader errors focused too.

@@ -97,10 +97,22 @@ SHADER_BEGIN(RationalTest, 1000, 500)
     SHADER_UNIFORM_TEXTURE_2D(uSampler, float, true)
 SHADER_END()
 
+SHADER_BEGIN(Quadratic1d, 1000, 500)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
+    SHADER_UNIFORM_TEXTURE_1D(uSampler, float, true)
+SHADER_END()
+
 SHADER_BEGIN(Quadratic2d, 1000, 500)
     SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
     SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
     SHADER_UNIFORM_TEXTURE_2D(uSampler, float, true)
+SHADER_END()
+
+SHADER_BEGIN(Cubic1d, 1000, 500)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
+    SHADER_UNIFORM_TEXTURE_1D(uSampler, float, true)
 SHADER_END()
 
 SHADER_BEGIN(Cubic2d, 1000, 500)
@@ -111,8 +123,14 @@ SHADER_END()
 
 SHADER_BEGIN(Cubic3d, 1000, 500)
     SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
-    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
     SHADER_UNIFORM_TEXTURE_3D(uSampler, float, true)
+SHADER_END()
+
+SHADER_BEGIN(Quartic1d, 1000, 500)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
+    SHADER_UNIFORM_TEXTURE_1D(uSampler, float, true)
 SHADER_END()
 
 SHADER_BEGIN(Quartic2d, 1000, 500)
@@ -123,7 +141,7 @@ SHADER_END()
 
[…]

### 2015-06-27 GLFW/Curves/Shader_Cubic1d.cpp

@@ -1,10 +1,10 @@
 #include "Shaders.h"
 
 //=============================================================================================================
-//                                            Cubic3d
+//                                            Cubic1d
 //=============================================================================================================
 
-void CShaderCubic3d::Init()
+void CShaderCubic1d::Init()
 {
     SetAttributeData_aTextureCoord({
         0.0, 0.0,
@@ -28,16 +28,12 @@ void CShaderCubic3d::Init()
     const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f };
     const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f };
 
-    SetTextureData_uSampler(2, 2, 2, {
-        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
-        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
-
-        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
-        R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+    SetTextureData_uSampler(4, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
     });
 }
 
-const char *CShaderCubic3d::GetVertexShader()
+const char *CShaderCubic1d::GetVertexShader()
 {
     return
     SHADER_SOURCE(
@@ -53,43 +49,33 @@ const char *CShaderCubic3d::GetVertexShader()
     );
 }
 
-const char *CShaderCubic3d::GetFragmentShader()
+const char *CShaderCubic1d::GetFragmentShader()
 {
     return
     SHADER_SOURCE(
-    uniform sampler3D uSampler;
+    uniform sampler1D uSampler;
     
     in vec2 vTextureCoord;
 
     out vec4 outColor;
 
-    vec4 SampleTime(vec3 time, bool linearSampling) {
-        // Trilinear sampling:
-        // Hardware based trilinear sampling
+    vec4 SampleTime(float time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
         if (linearSampling)
-            return texture(uSampler, (time + 0.5) / 2.0);
+            return texture(uSampler, (time + 0.5) / 4.0);
 
         // Nearest sampling:
[…]

### 2015-06-27 GLFW/Curves/Shader_Quadratic1d.cpp

@@ -1,0 +1,108 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Quadratic1d
+//=============================================================================================================
+
+void CShaderQuadratic1d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f };
+    const float G[] = { 0.0f , 1.0f, 0.25f };
+    const float B[] = { 0.2f , 0.0f, 1.00f };
+    const float A[] = { 0.75f, 0.0f, 0.29f };
+
+    SetTextureData_uSampler(4, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],     0.0f, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderQuadratic1d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderQuadratic1d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler1D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(float time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / 4.0);
+
+        // Nearest sampling:
+        // Software bilinear sampling (higher quality)
+        float frac = fract(time);
+
+        float floorTime = floor(time) + 0.5;
+
+        vec4 A = texture(uSampler, (floorTime + 0.0) / 4.0);
[…]

### 2015-06-27 GLFW/Curves/Shader_Quartic3d.cpp

@@ -7,12 +7,12 @@
 void CShaderQuartic3d::Init()
 {
     SetAttributeData_aTextureCoord({
-        0.0, 0.0, 0.0,
-        2.0, 0.0, 0.0,
-        2.0, 1.0, 0.0,
-        0.0, 0.0, 0.0,
-        2.0, 1.0, 0.0,
-        0.0, 1.0, 0.0,
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
     });
     SetAttributeData_aVertexPosition({
         -1.0, -1.0,
@@ -46,9 +46,9 @@ const char *CShaderQuartic3d::GetVertexShader()
     return
     SHADER_SOURCE(
     in vec2 aVertexPosition;
-    in vec3 aTextureCoord;
+    in vec2 aTextureCoord;
 
-    out vec3 vTextureCoord;
+    out vec2 vTextureCoord;
 
     void main(void) {
         gl_Position = vec4(aVertexPosition, 1.0, 1.0);
@@ -63,7 +63,7 @@ const char *CShaderQuartic3d::GetFragmentShader()
     SHADER_SOURCE(
     uniform sampler3D uSampler;
     
-    in vec3 vTextureCoord;
+    in vec2 vTextureCoord;
 
     out vec4 outColor;
 

### 2015-06-27 GLFW/Curves/Shaders.h

@@ -12,6 +12,7 @@
         ~CShader##NAME##(); \
         void Render(); \
         void Init(); \
+        static const char *GetName() { return #NAME; } \
         static const char *GetVertexShader(); \
         static const char *GetFragmentShader(); \
         static void GetWidthHeight(int &width, int &height) {width=WIDTH; height=HEIGHT;}

### 2015-06-27 GLFW/Curves/main.cpp

@@ -61,7 +61,7 @@ int main(void)
     }
     printf("Using GLEW %s\n", glewGetString(GLEW_VERSION));
 
-    printf("Using OpenGL %s\n", glGetString(GL_VERSION));
+    printf("Using OpenGL %s\n\n", glGetString(GL_VERSION));
 
     // init our shaders
     #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) CShader##NAME shader##NAME##;  shader##NAME##.Init();

### 2015-06-27 GLFW/Curves/shaders.cpp

@@ -14,7 +14,7 @@
 template <typename T>
 GLuint LoadShader(const T& shader)
 {
-    return LoadShader(shader.GetVertexShader(), shader.GetFragmentShader());
+    return LoadShader(shader.GetName(), shader.GetVertexShader(), shader.GetFragmentShader());
 }
 
 //=============================================================================================================

### 2015-06-27 GLFW/Curves/utils.cpp

@@ -8,7 +8,7 @@
 #include <algorithm>
 
 //=============================================================================================================
-GLuint LoadShader(const char *vertexShader, const char *fragmentShader) {
+GLuint LoadShader(const char *name, const char *vertexShader, const char *fragmentShader) {
     GLuint vertShader = glCreateShader(GL_VERTEX_SHADER);
     GLuint fragShader = glCreateShader(GL_FRAGMENT_SHADER);
 
@@ -16,7 +16,6 @@ GLuint LoadShader(const char *vertexShader, const char *fragmentShader) {
     int logLength;
 
     // Compile vertex shader
-    printf("Compiling vertex shader.\n");
     glShaderSource(vertShader, 1, &vertexShader, NULL);
     glCompileShader(vertShader);
 
@@ -25,10 +24,8 @@ GLuint LoadShader(const char *vertexShader, const char *fragmentShader) {
     glGetShaderiv(vertShader, GL_INFO_LOG_LENGTH, &logLength);
     std::vector<GLchar> vertShaderError((logLength > 1) ? logLength : 1);
     glGetShaderInfoLog(vertShader, logLength, NULL, &vertShaderError[0]);
-    printf("%s\n", &vertShaderError[0]);
 
     // Compile fragment shader
-    printf("Compiling fragment shader.\n");
     glShaderSource(fragShader, 1, &fragmentShader, NULL);
     glCompileShader(fragShader);
 
@@ -37,9 +34,7 @@ GLuint LoadShader(const char *vertexShader, const char *fragmentShader) {
     glGetShaderiv(fragShader, GL_INFO_LOG_LENGTH, &logLength);
     std::vector<GLchar> fragShaderError((logLength > 1) ? logLength : 1);
     glGetShaderInfoLog(fragShader, logLength, NULL, &fragShaderError[0]);
-    printf("%s\n", &fragShaderError[0]);
 
-    printf("Linking program\n");
     GLuint program = glCreateProgram();
     glAttachShader(program, vertShader);
     glAttachShader(program, fragShader);
@@ -49,10 +44,16 @@ GLuint LoadShader(const char *vertexShader, const char *fragmentShader) {
     glGetProgramiv(program, GL_INFO_LOG_LENGTH, &logLength);
     std::vector<char> programError((logLength > 1) ? logLength : 1);
     glGetProgramInfoLog(program, logLength, NULL, &programError[0]);
-    printf("%s\n", &programError[0]);
 
[…]

### 2015-06-27 GLFW/Curves/utils.h

@@ -6,7 +6,7 @@
 #include <GLFW/glfw3.h>
 #include <vector>
 
-GLuint LoadShader(const char *vertexShader, const char *fragmentShader);
+GLuint LoadShader(const char *name, const char *vertexShader, const char *fragmentShader);
 
 template<typename T>
 GLuint MakeBuffer(const std::vector<T>& data);

### 2015-06-28 Paper/Figures/FigCubicTree.tex
1d / 2d texture explanation

\documentclass{article}
\usepackage{tikz}
\usepackage{tkz-euclide}
\definecolor{darkgreen}{RGB}{0,192,0}
\title{Cartesian closed categories and the price of eggs}
\author{Jane Doe}
\date{September 1994}
\begin{document}

\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw] (char) {#1};}}

\begin{figure}
	\begin{tikzpicture}[level/.style={sibling distance = 5cm/#1, level distance = 1.5cm}] 
		\begin{scope}[shift={(-6cm,0)}]
			\node (Root) {\circled{ABCD}}
			    child{ node{\circled{ABC}}
			            child{ node {\circled{AB}}
			            	child{ node {\circled{A}}}
			            	child{ node {\circled{B}}}            
			            }
			            child{ node {\circled{BC}}
			            	child{ node {\circled{B}}}
			            	child{ node {\circled{C}}}            
			            }                            
			    }
			    child{ node {\circled{BCD}}
			            child{ node {\circled{BC}}
			            	child{ node {\circled{B}}}
			            	child{ node {\circled{C}}}
			            }  
			            child{ node {\circled{CD}}
			            	child{ node {\circled{C}}}
			            	child{ node {\circled{D}}}
			            }  
					}
			;

			% Comments for each level
			\begin{scope}[every node/.style={right}]
				\path (Root      -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Cubic curve / Trilinear sampling};
				\path (Root-1    -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Quadratic curve / Bilinear sampling};
				\path (Root-1-1  -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Linear curve / Linear sampling};
				\path (Root-1-1-1-| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Point / Point sampling};
			\end{scope}
		\end{scope}   
	\end{tikzpicture}
	\caption{A tree showing the De Casteljeau algorithm for a cubic curve.  The labels on the right show what type of curves are evaluated at that level, as well as the $N$ dimensional sampling that is required to evaluate nodes at that level with a single texture read.}
\end{figure}

\end{document}

### 2015-06-28 Paper/Figures/FigTexture1D.tex
1d / 2d texture explanation

@@
 	\begin{figure}
-		\begin{tikzpicture}[x=8cm,y=4cm]
-			\tkzInit[xmax=2,ymax=1,xmin=0,ymin=0]
-			% border
-			\draw (-0.1,-0.2) rectangle (2,1.2);
+		\begin{tikzpicture}
+			\draw[step=1cm,gray,very thin] (0,0) grid (4,1);
+			\draw (0.5,0.5) node {$A$};
+			\draw (1.5,0.5) node {$B$};
+			\draw (2.5,0.5) node {$C$};
+			\draw (3.5,0.5) node {$D$};
+		\end{tikzpicture}
 
-			\foreach \x in {0,...,4}
-				\draw (\x * 0.1 - 0.05,0.45) rectangle (\x * 0.1 + 0.05, 0.55);
+		\vspace{5mm}
 
+		\begin{tikzpicture}
+			\draw[step=1cm,gray,very thin] (0,0) grid (8,1);
+			\draw (0.5,0.5) node {$A$};
+			\draw (1.5,0.5) node {$B$};
+			\draw (2.5,0.5) node {$C$};
+			\draw (3.5,0.5) node {$D$};
+			\draw (4.5,0.5) node {$D$};
+			\draw (5.5,0.5) node {$E$};
+			\draw (6.5,0.5) node {$F$};
+			\draw (7.5,0.5) node {$G$};			
 		\end{tikzpicture}		
-		\caption{TODO: this}		
+		\caption{\textit{Top:} A cubic curve with control points $A,B,C,D$ encoded in a 1d texture.
+\textit{Bottom:} Two piecewise curves encoded in a 1d texture.
+The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.
+If C0 continuitiy is always desired between the curves, a redundant $D$ could be removed to store these curves in 7 pixels instead of 8.}
+		\label{fig:texlayeout1d}
 	\end{figure}

### 2015-06-28 Paper/Figures/FigTexture2D.tex
1d / 2d texture explanation

\documentclass{article}
\usepackage{tikz}
\usepackage{tkz-euclide}
\definecolor{darkgreen}{RGB}{0,192,0}
\title{Cartesian closed categories and the price of eggs}
\author{Jane Doe}
\date{September 1994}
\begin{document}

	\begin{figure}
		\begin{tikzpicture}
			\draw[step=1cm,gray,very thin] (0,0) grid (2,-3);
			\draw (0.5,-0.5) node {$A$};
			\draw (1.5,-0.5) node {$B$};
			\draw (0.5,-1.5) node {$B$};
			\draw (1.5,-1.5) node {$C$};
			\draw (0.5,-2.5) node {$C$};
			\draw (1.5,-2.5) node {$D$};			
		\end{tikzpicture}
		\hspace{5mm}
		\begin{tikzpicture}
			\draw[step=1cm,gray,very thin] (0,0) grid (4,-3);
			\draw (0.5,-0.5) node {$A$};
			\draw (1.5,-0.5) node {$B$};
			\draw (0.5,-1.5) node {$B$};
			\draw (1.5,-1.5) node {$C$};
			\draw (0.5,-2.5) node {$C$};
			\draw (1.5,-2.5) node {$D$};

			\draw (2.5,-0.5) node {$D$};
			\draw (3.5,-0.5) node {$E$};
			\draw (2.5,-1.5) node {$E$};
			\draw (3.5,-1.5) node {$F$};
			\draw (2.5,-2.5) node {$F$};
			\draw (3.5,-2.5) node {$G$};					
		\end{tikzpicture}
		\caption{\textit{Left:} A cubic curve with control points $A,B,C,D$ encoded in a 2d texture that is $(2,3)$ in size.  \textit{Right:} Two piecewise curves encoded in a 2d texture that is $(4,3)$ in size.  The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.}	
		\label{fig:texlayeout1d}
	\end{figure}

\end{document}

### 2015-06-28 Paper/paper.tex
1d / 2d texture explanation

@@
 TODO: How to prove for N dimensions?  This section needs help
+TODO: could somehow show how N-linear sampling is same as De Casteljeaus for all N's? tree diagram or something else.
 
@@
 
+\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
+            \node[shape=circle,draw] (char) {#1};}}
+
+\begin{figure}
+  \begin{tikzpicture}[level/.style={sibling distance = 5cm/#1, level distance = 1.5cm}] 
+    \begin{scope}[shift={(-6cm,0)}]
+      \node (Root) {\circled{ABCD}}
+          child{ node{\circled{ABC}}
+                  child{ node {\circled{AB}}
+                    child{ node {\circled{A}}}
+                    child{ node {\circled{B}}}            
+                  }
+                  child{ node {\circled{BC}}
+                    child{ node {\circled{B}}}
+                    child{ node {\circled{C}}}            
+                  }                            
+          }
+          child{ node {\circled{BCD}}
+                  child{ node {\circled{BC}}
+                    child{ node {\circled{B}}}
+                    child{ node {\circled{C}}}
+                  }  
+                  child{ node {\circled{CD}}
+                    child{ node {\circled{C}}}
+                    child{ node {\circled{D}}}
+                  }  
+          }
+      ;
+
+      % Comments for each level
+      \begin{scope}[every node/.style={right}]
+        \path (Root      -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Cubic curve / Trilinear sampling};
+        \path (Root-1    -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Quadratic curve / Bilinear sampling};
+        \path (Root-1-1  -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Linear curve / Linear sampling};
+        \path (Root-1-1-1-| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Point / Nearest Neighbor};
+      \end{scope}
+    \end{scope}   
+  \end{tikzpicture}
+  \caption{A tree showing the De Casteljeau algorithm for a cubic curve.
+The labels on the right show what type of curves are evaluated at that level, as well as the $N$ dimensional sampling that is required to evaluate nodes at that level with a single texture read.}
+  \label{fig:decdimensionality}
+\end{figure}
+
 While this technique is able to be used with any texture dimensionality, there are different characteristics for each choice.  Those characteristics will be explored here.
@@
 
-One dimensional textures are textures which have N pixels in a single row or column, such as 8x1, 16x1 or more generally Nx1.
+One dimensional textures are textures which have $W$ pixels in a single row or column, such as $(8,1)$, $(16,1)$ or more generally $(W,1)$.
 
-Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st order (linear) Bezier basis functions.
+Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st order (linear) Bezier basis functions (\autoref{fig:decdimensionality}).
 
-If you want a Bezier curve higher than order 1, you are going to have to take more texture samples and combine the results in the shader program.
-While this is more expensive computationally, it does have the benefit of doing more of the work in the shader program, which has higher precision through use of full float math, so the end result will be a higher quality curve.
+If you want a Bezier curve higher than order $1$, you can take more texture samples and combine the results in the shader program.
+While this is more expensive computationally than moving to a texture of higher dimensionality, it does have the benefit of doing more of the work in the shader program, which has higher precision through use of full float math, so the end result will be a higher quality curve.
 
-TODO: Flesh out details, show diagram of texture layout.
-TODO: Maybe just GLSL for linear and quartic, but images for linear, quadratic, cubic, quartic with comparison vs "ground truth".
+The size of the one dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $(N+1)*M$.
+For instance, a cubic (degree 3) curve requires 4 pixels ($(3+1)*1$).
+If you want to encode two piecewise cubic curves end to end, it requires 8 pixels ($(3+1)*2$).
+
+If $C0$ continuity is desired for piecewise curves, a redundant control point can be removed from the beginning of each curve after the first curve, which makes the size of texture required become $N*M+1$, requiring only 7 pixels for two cubic curves, instead of 8, or 10 pixels for three cubic curves, instead of 12 (\autoref{fig:texlayeout1d}).
+
+  \begin{figure}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0) grid (4,1);
+      \draw (0.5,0.5) node {$A$};
+      \draw (1.5,0.5) node {$B$};
+      \draw (2.5,0.5) node {$C$};
+      \draw (3.5,0.5) node {$D$};
+    \end{tikzpicture}
+
+    \vspace{5mm}
+
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0) grid (8,1);
+      \draw (0.5,0.5) node {$A$};
+      \draw (1.5,0.5) node {$B$};
+      \draw (2.5,0.5) node {$C$};
+      \draw (3.5,0.5) node {$D$};
+      \draw (4.5,0.5) node {$D$};
+      \draw (5.5,0.5) node {$E$};
+      \draw (6.5,0.5) node {$F$};
+      \draw (7.5,0.5) node {$G$};     
+    \end{tikzpicture}   
+    \caption{\textit{Top:} A cubic curve with control points $A,B,C,D$ encoded in a 1d texture with a size of 4 pixels.
+\textit{Bottom:} Two piecewise curves encoded in a 1d texture.
+The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.
+If C0 continuitiy is always desired between the curves, a redundant $D$ could be removed to store these curves in 7 pixels instead of 8.
+}
+    \label{fig:texlayeout1d}
+  \end{figure}
+
+In the case of a cubic curve with control points $A,B,C,D$, the one dimensional texture will be 4 pixels in size, and three texture reads will need to be done to get the interpolations for $\overline{AB},\overline{BC},\overline{CD}$.
+Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve (order 2) to elevate those three points from order 1 to order 3, to get the final point $\stackrel{\frown}{ABCD}$.
+
+\begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a 4 pixel 1d texture.
+Linear texture sampling used to evaluate the first level of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
+// 4 pixel 1d texture with control points encoded: A,B,C,D
+uniform sampler1D uSampler; 
+const float c_textureSize = 4.0;
+
+vec4 CubicCurveFromTexture1D_DeCastelJeau(in float t) {
+    vec4 AB = texture(uSampler, (t + 0.5) / c_textureSize);
+    vec4 BC = texture(uSampler, (t + 1.5) / c_textureSize;
+    vec4 CD = texture(uSampler, (t + 2.5) / c_textureSize);
+    vec4 ABC = mix(AB, BC, t);
+    vec4 BCD = mix(BC, CD, t);
+    return mix(ABC, BCD, t);
+}
+
+vec4 CubicCurveFromTexture1D_Bernstein(in float t) {
+    vec4 AB = texture(uSampler, (t + 0.5) / c_textureSize);
+    vec4 BC = texture(uSampler, (t + 1.5) / c_textureSize);
+    vec4 CD = texture(uSampler, (t + 2.5) / c_textureSize);
+    float s = (1 - t);
+    float s2 = s * s;
+    float t2 = t * t;
+    // Quadratic Bezier Curve = A*s*s + B*2*s*t + C*t*t
+    return AB*s2 + BC*2.0*s*t + CD*t2;
+}
+\end{lstlisting}
 
@@
 
-Two dimensional textures are textures which are MxN pixels in size, such as 8x8 or 16x16 or 32x4.
+Two dimensional textures are textures which are $(W,H)$ pixels in size, such as $(8,8)$ or $(16,16)$ or $(32,4)$.
 
-Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd order (quadratic) Bezier basis functions.
+Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd order (quadratic) Bezier basis functions (\autoref{fig:decdimensionality}).
 
-If you want a Bezier curve higher than order 2, once again you are going to have to take more texture samples and combine the results in the shader program.
-While more computationally expensive, it again results in higher precision results.
+If you want a Bezier curve higher than order 2, once again you can take more texture samples and combine the results in the shader program.
+While more computationally expensive that moving to a higher dimensionality texture, it again results in higher precision results due to more of the computation happening in full floating point precision.
 
-TODO: flesh out details, show diagram of texture layout.
-TODO: GLSL for quadratric and quartic, but images for quadratic, cubic, quartic with comparison vs "ground truth".
-TODO: explain how linear can still be achieved even if it isn't that useful (yet? Hw/sw)
+The size of the two dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $(2*M,N)$.
+For instance, a cubic (degree 3) curve will be $(2,3)$ pixels.
+If you want to encode two piecewise cubic curves end to end, it requires $(4,3)$ pixels (\autoref{fig:texlayeout2d}).
+
+  \begin{figure}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0) grid (2,-3);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};
+      \draw (0.5,-2.5) node {$C$};
+      \draw (1.5,-2.5) node {$D$};      
+    \end{tikzpicture}
+    \hspace{5mm}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0) grid (4,-3);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};
+      \draw (0.5,-2.5) node {$C$};
+      \draw (1.5,-2.5) node {$D$};
+
+      \draw (2.5,-0.5) node {$D$};
+      \draw (3.5,-0.5) node {$E$};
+      \draw (2.5,-1.5) node {$E$};
+      \draw (3.5,-1.5) node {$F$};
+      \draw (2.5,-2.5) node {$F$};
+      \draw (3.5,-2.5) node {$G$};          
+    \end{tikzpicture}
+    \caption{\textit{Left:} A cubic curve with control points $A,B,C,D$ encoded in a 2d texture that is $(2,3)$ in size.
+\textit{Right:} Two piecewise curves encoded in a 2d texture that is $(4,3)$ in size.
+The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.}
+    \label{fig:texlayeout2d}
+  \end{figure}
+
+\begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,4)$ pixel 2d texture.
+Bilinear texture sampling used to evaluate the first two levesl of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture1D}]
+// 2x4 2d texture, rounded to the nearest powers of 2 from 2x3.
+uniform sampler2D uSampler; 
+const vec2 c_textureSize = vec2(2.0,4.0);
+
+vec4 CubicCurveFromTexture2D_DeCastelJeau(in float t) {
+    vec4 ABC = texture(uSampler, (vec2(0.5, 0.5)+t) / c_textureSize);
+    vec4 BCD = texture(uSampler, (vec2(0.5, 1.5)+t) / c_textureSize);
+    return mix(ABC, BCD, t);
+}
+
+vec4 CubicCurveFromTexture2D_Bernstein(in float t) {
+    vec4 ABC = texture(uSampler, (vec2(0.5, 0.5)+t) / c_textureSize);
+    vec4 BCD = texture(uSampler, (vec2(0.5, 1.5)+t) / c_textureSize);
+    float s = (1 - t);
+    // Linear Bezier Curve = A*s + B*t
+    return ABC*s + BCD*t;
+}
+\end{lstlisting}
 

### 2015-06-29 Paper/paper.tex
3d texture wip

@@
 
-Three dimensional textures (often refered to as volumetric textures) are textures which are MxNxO pixels in size such as 8x8x2 or 16x8x4.
+Three dimensional textures (often refered to as volumetric textures) are textures which are $(W,H,D)$ pixels in size such as $(8,8,2)$ or $(16,8,4)$.
 
-Using three dimensional textures allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier basis functions.
+Using three dimensional textures allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier basis functions (\autoref{fig:decdimensionality}).
 
@@
 
-TODO: flesh out details, show diagram of texture layout.
-TODO: GLSL for cubic and quartic, but images for cubic, quartic with comparison vs ground truth.
-TODO: explain how linear and quadratic could still be achieved even if it isn't that useful (ye? Hw/sw)
-TODO: beyond 3d textures? Could do 4d with mipmapped volumetric textures!
+You may have noticed that a 1d texture can store a linear curve, but that a 2d texture cannot.
+The lowest order curve it can store is a quadratic curve.
+In the case of a 3d texture, the minimum goes up again, and the lowest order curve you can store is a cubic curve.
+
+TODO: formula for texture size
+
+\begin{figure}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0,0) grid (2,-2,0);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};
+
+      \begin{scope}[shift={(0.75,0.75,0)}]
+        \draw[step=1cm,gray,dashed] (0,0,0) grid (2,-2,0);
+        \draw[gray] (0.5,-0.5) node {$B$};
+        \draw[gray] (1.5,-0.5) node {$C$};
+        \draw[gray] (0.5,-1.5) node {$C$};
+        \draw[gray] (1.5,-1.5) node {$D$};
+      \end{scope}
+
+      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
+      \draw[dashed] (2,0,0) -- (2.75, 0.75,0);
+      \draw[dashed] (0,-2,0) -- (0.75,-1.25,0);
+      \draw[dashed] (2,-2,0) -- (2.75,-1.25,0);
+    \end{tikzpicture}
+    \hspace{5mm}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0,0) grid (4,-2,0);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};
+
+      \draw (2.5,-0.5) node {$E$};
+      \draw (3.5,-0.5) node {$F$};
+      \draw (2.5,-1.5) node {$F$};
+      \draw (3.5,-1.5) node {$G$};
+
+      \begin{scope}[shift={(0.75,0.75,0)}]
+        \draw[step=1cm,gray,dashed] (0,0,0) grid (4,-2,0);
+        \draw[gray] (0.5,-0.5) node {$B$};
+        \draw[gray] (1.5,-0.5) node {$C$};
+        \draw[gray] (0.5,-1.5) node {$C$};
+        \draw[gray] (1.5,-1.5) node {$D$};
+
+        \draw[gray] (2.5,-0.5) node {$F$};
+        \draw[gray] (3.5,-0.5) node {$G$};
+        \draw[gray] (2.5,-1.5) node {$G$};
+        \draw[gray] (3.5,-1.5) node {$H$};
+      \end{scope}
+
+      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
+      \draw[dashed] (4,0,0) -- (4.75, 0.75,0);
+      \draw[dashed] (0,-2,0) -- (0.75,-1.25,0);
+      \draw[dashed] (4,-2,0) -- (4.75,-1.25,0);
+    \end{tikzpicture}
+
+    \vspace{5mm}
+
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0,0) grid (2,-3,0);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};
+      \draw (0.5,-2.5) node {$C$};
+      \draw (1.5,-2.5) node {$D$};
+
+      \begin{scope}[shift={(0.75,0.75,0)}]
+        \draw[step=1cm,gray,dashed] (0,0,0) grid (2,-3,0);
+        \draw[gray] (0.5,-0.5) node {$B$};
+        \draw[gray] (1.5,-0.5) node {$C$};
+        \draw[gray] (0.5,-1.5) node {$C$};
+        \draw[gray] (1.5,-1.5) node {$D$};
+        \draw[gray] (0.5,-2.5) node {$D$};
+        \draw[gray] (1.5,-2.5) node {$E$};
+      \end{scope}
+
+      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
+      \draw[dashed] (2,0,0) -- (2.75, 0.75,0);
+      \draw[dashed] (0,-3,0) -- (0.75,-2.25,0);
+      \draw[dashed] (2,-3,0) -- (2.75,-2.25,0);
+    \end{tikzpicture}
+    \hspace{5mm}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0,0) grid (4,-3,0);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};
+      \draw (0.5,-2.5) node {$C$};
+      \draw (1.5,-2.5) node {$D$};
+
+      \draw (2.5,-0.5) node {$F$};
+      \draw (3.5,-0.5) node {$G$};
+      \draw (2.5,-1.5) node {$G$};
+      \draw (3.5,-1.5) node {$H$};
+      \draw (2.5,-2.5) node {$H$};
+      \draw (3.5,-2.5) node {$I$};
+
+      \begin{scope}[shift={(0.75,0.75,0)}]
+        \draw[step=1cm,gray,dashed] (0,0,0) grid (4,-3,0);
+        \draw[gray] (0.5,-0.5) node {$B$};
+        \draw[gray] (1.5,-0.5) node {$C$};
+        \draw[gray] (0.5,-1.5) node {$C$};
+        \draw[gray] (1.5,-1.5) node {$D$};
+        \draw[gray] (0.5,-2.5) node {$D$};
+        \draw[gray] (1.5,-2.5) node {$E$};
+
+        \draw[gray] (2.5,-0.5) node {$G$};
+        \draw[gray] (3.5,-0.5) node {$H$};
+        \draw[gray] (2.5,-1.5) node {$H$};
+        \draw[gray] (3.5,-1.5) node {$I$};
+        \draw[gray] (2.5,-2.5) node {$I$};
+        \draw[gray] (3.5,-2.5) node {$J$};
+      \end{scope}
+
+      \draw[dashed] (0,0,0) -- (0.75, 0.75,0);
+      \draw[dashed] (4,0,0) -- (4.75, 0.75,0);
+      \draw[dashed] (0,-3,0) -- (0.75,-2.25,0);
+      \draw[dashed] (4,-3,0) -- (4.75,-2.25,0);
+    \end{tikzpicture}
+
+    \caption{\textit{Top Left:} A cubic curve encoded in a $(2,2,2)$ sized texture, decoded with a single trilinear texture sample.
+\textit{Top Right:}  Two piecewise cubic curves encoded in a $(4,2,2)$ sized texture, decoded with a single trilinear texture sample.
+\textit{Bottom Left:} A Quartic curve encoded in a $(2,3,2)$ sized texture, decoded with two trilinear texture samples.
+\textit{Bottom Right:} Two piecewise quartic curves encoded in a $(4,3,2)$ sized texture, decoded with two trilinear texture samples.}
+    \label{fig:texlayeout1d}
+  \end{figure}
+
+TODO: GLSL for cubic!
 
@@
 TODO: we might want to do this in the performance results section instead and provide perf metrics as well.
+TODO: beyond 3d textures?
 

### 2015-06-29 Paper/paper.tex
3d textures done, dimensionality summary next

@@
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,4)$ pixel 2d texture.
-Bilinear texture sampling used to evaluate the first two levesl of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture1D}]
+Bilinear texture sampling used to evaluate the first two levesl of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture2D}]
 // 2x4 2d texture, rounded to the nearest powers of 2 from 2x3.
@@
 
-TODO: formula for texture size
+The size of the three dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $(2*M,N-1,2)$.
+For instance, a cubic (degree 3) curve will be $(2,2,2)$ pixels.
+If you want to encode two piecewise cubic curves end to end, it requires $(4,2,2)$ pixels (\autoref{fig:texlayeout3d}).
 
@@
 \textit{Bottom Right:} Two piecewise quartic curves encoded in a $(4,3,2)$ sized texture, decoded with two trilinear texture samples.}
-    \label{fig:texlayeout1d}
+    \label{fig:texlayeout3d}
   \end{figure}
 
-TODO: GLSL for cubic!
+\begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,2,2)$ pixel 3d texture.
+Trilinear texture sampling used to evaluate all three levels of the De Casteljeau algorithm.}, label={lst:GLSLCubicTexture3D}]
+// 2x2x2 3d texture.
+uniform sampler2D uSampler; 
+const vec3 c_textureSize = vec3(2.0, 2.0, 2);
 
-\subsection{Summary of Implications of Texture Dimensionality}
+vec4 CubicCurveFromTexture3D(in float t) {
+    return texture(uSampler, vec3(0.5 + t) / c_textureSize);
+}
+\end{lstlisting}
 
-TODO: dimensionality / curve order comparisons. A table? Maybe side by side images?
-TODO: texture size changes, number of textures used, number of texture samples taken
-TODO: include quadrilinear and above?
-TODO: we might want to do this in the performance results section instead and provide perf metrics as well.
-TODO: beyond 3d textures?
+\subsection{Summary of Texture Dimensionality}
+
+TODO: TABLE to compare dimensionality
+table details...
+
+y axis =
+ * 1d, 2d, 3d, 4d?
+
+x axis =
+ * minimum curve order storage
+ * texture size formula
+ * num texture samples taken for a quintic curve? sextent curve? or maybe do quadratic, cubic, quarticorder 4, order 5?
+ * texture size for them too? dims and num pixels
+
+TODO do we want images here at all? probably not i guess...
+
+TODO: need to explain the layout of the pixels in the sections above somehow.  Maybe also get rid of describing what N-dimensional textures are
 
@@
 TODO: this.  Pros and cons. B-splines can be converted to piecewise Bezier with Boem's algorithm (what's it called again?).
+TODO: how to actually evaluate piecewise curves! (GLSL if needed? or just describe it)
 

### 2015-06-29 GLFW/Curves/Shader_Cubic3d.cpp

@@ -90,8 +90,14 @@ const char *CShaderCubic3d::GetFragmentShader()
         return mix(front, back, frac.z);
     }
 
+    const vec3 c_textureSize = vec3(2.0, 2.0, 2);
+
+    vec4 CubicCurveFromTexture3D(in float t) {
+        return texture(uSampler, vec3(0.5 + t) / c_textureSize);
+    }
 
     void main(void) {
+        /*
         vec4 colorValue = vec4(0.0);
 
         if (vTextureCoord.x < 0.995)
@@ -109,6 +115,13 @@ const char *CShaderCubic3d::GetFragmentShader()
             outColor = vec4(1.0);
             return;
         }
+        */
+
+        vec4 colorValue;
+        if (vTextureCoord.x <= 1.0)
+            colorValue = CubicCurveFromTexture3D(vTextureCoord.x);
+        else
+            colorValue = CubicCurveFromTexture3D(vTextureCoord.x - 1.0);
 
         vec4 values = step(vTextureCoord.yyyy, colorValue);
         values.xyz *= 0.5;

### 2015-07-04 Paper/paper.tex
Texture Dimensionality Cleanup

@@
 \usepackage{amsmath}
+\usepackage{pgfplots}
 \definecolor{darkgreen}{RGB}{0,192,0}
@@
 A quick comparison of the visual quality of these three techniques can be seen in \autoref{fig:quickcomparison}.
+
+\subsection{Related Work}
+
+TODO: this
 
@@
 
-While the Bernstein form of Bezier curves is equivelant to evaluating a Bezier curve with the De Casteljeau algorithm, in practice there are differences that come up between the two.
-It is well known that the De Casteljeau algorithm is slower but more numerically robust than evaluating the Bernstein form.
-
-The technique presented in this paper also has numerical differences in practice.
-While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures (\autoref{fig:quickaccuracy}).
-
-As shown in \autoref{fig:texbilcurve}, the quality can be significantly higher than a baked out curve for the same number of pixels however.
-There is more information on addressing accuracy in \autoref{sec:addressingaccuracyissues}.
-
   \begin{figure}
@@
 
+While the Bernstein form of Bezier curves is equivelant to evaluating a Bezier curve with the De Casteljeau algorithm, in practice there are differences that come up between the two.
+It is well known that the De Casteljeau algorithm is slower but more numerically robust than evaluating the Bernstein form.
+
+The technique presented in this paper also has numerical differences in practice.
+While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures (\autoref{fig:quickaccuracy}).
+
+As shown in \autoref{fig:texbilcurve}, the quality can be significantly higher than a baked out curve for the same number of pixels however.
+There is more information on addressing accuracy in \autoref{sec:addressingaccuracyissues}.
+
 TODO: give the details of the architecture imprecision sources and cite the two papers cited from the other place!
@@
 \begin{figure}
-  \begin{tikzpicture}[level/.style={sibling distance = 5cm/#1, level distance = 1.5cm}] 
+  \begin{tikzpicture}[level/.style={sibling distance = 4.5cm/#1, level distance = 1.5cm}] 
     \begin{scope}[shift={(-6cm,0)}]
@@
       \begin{scope}[every node/.style={right}]
-        \path (Root      -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Cubic curve / Trilinear sampling};
-        \path (Root-1    -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Quadratic curve / Bilinear sampling};
-        \path (Root-1-1  -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Linear curve / Linear sampling};
-        \path (Root-1-1-1-| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Point / Nearest Neighbor};
+        \path (Root      -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Cubic / Trilinear};
+        \path (Root-1    -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Quadratic / Bilinear};
+        \path (Root-1-1  -| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Linear / Linear};
+        \path (Root-1-1-1-| Root-2-2-2) ++(5mm,0) node {$\Rightarrow$} ++(5mm,0) node [blue] {Point / Nearest};
       \end{scope}
@@
 
-One dimensional textures are textures which have $W$ pixels in a single row or column, such as $(8,1)$, $(16,1)$ or more generally $(W,1)$.
+Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st order (linear) Bezier curves (\autoref{fig:decdimensionality}).
 
-Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st order (linear) Bezier basis functions (\autoref{fig:decdimensionality}).
+Since the De Casteljeau algorithm just interpolates between linear interpolations, we can take more texture samples and combine them in the shader program to get higher order curves.
+For an order $N$ Bezier curve, the De Casteljeau algorithm requires $2^{N-1}$ linear interpolations for the linear level of the tree.
+You need two pixels to perform a linear interpolation, so it seems that we would need $2^N$ pixels to store a curve of order $N$ in a 1 dimensional textures.
+For a cubic curve, that would look like this: $[P_0,P_1,P_1,P_2,P_1,P_2,P_2,P_3]$.
 
-If you want a Bezier curve higher than order $1$, you can take more texture samples and combine the results in the shader program.
-While this is more expensive computationally than moving to a texture of higher dimensionality, it does have the benefit of doing more of the work in the shader program, which has higher precision through use of full float math, so the end result will be a higher quality curve.
+We can do better than that though.
+Firstly, there are redundant lerps in the list for lerping between $P_1$ and $P_2$.
+As the order of the curve increases, the number of redundancies increase as well.
+We don't want to have to pay the cost of pixel storage and texture samples for redundancies, so because we have $N+1$ control points and we only ever sample between  $P_i$ and $P_{i+1}$, we only need to store $N$ lerps in the 1 dimensional texture, which would mean we would need $N*2$ pixels.
+A cubic curve would then look like this:  $[P_0,P_1,P_1,P_2,P_2,P_3]$.
 
-The size of the one dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $(N+1)*M$.
-For instance, a cubic (degree 3) curve requires 4 pixels ($(3+1)*1$).
-If you want to encode two piecewise cubic curves end to end, it requires 8 pixels ($(3+1)*2$).
+After eliminating redundant lerps, we can see that there are redundant data values in our texture.
+$P_1$ and $P_2$ each show up twice.
+As the order of the curve increases, we would notice the pattern that all control points show up twice except the end points.
+We can remove these redundancies and still be able to get the same information out.
+The result of removing these redundancies is that our texture only needs to contain each control point once, which means we only need $N+1$ pixels to encode a curve of order $N$.
+The cubic curve now looks like this: $[P_0,P_1,P_2,P_3]$.
 
-If $C0$ continuity is desired for piecewise curves, a redundant control point can be removed from the beginning of each curve after the first curve, which makes the size of texture required become $N*M+1$, requiring only 7 pixels for two cubic curves, instead of 8, or 10 pixels for three cubic curves, instead of 12 (\autoref{fig:texlayeout1d}).
+If $M$ piecewise curves are desired, we multiply the number of pixels used for one curve by $M$.
+The size of the one dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $M*(N+1)$.
+Two piecewise cubic curves encoded into a texture would be 8 pixels in size and look like this: $[P_0,P_1,P_2,P_3,P_4,P_5,P_6,P_7]$
+
+It's often the case that you want $C0$ continuity for piecewise curves though, which in the example would give $P_4$ the same value as $P_3$.
+If your piecewise curves always had $C0$ continuity, you could remove the redundant control point for every curve after the first, which would make it so the size of the texture required became $N*M+1$ (\autoref{fig:texlayeout1d}).
 
@@
     \end{tikzpicture}
+
+    \vspace{5mm}
+
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0) grid (7,1);
+      \draw (0.5,0.5) node {$A$};
+      \draw (1.5,0.5) node {$B$};
+      \draw (2.5,0.5) node {$C$};
+      \draw (3.5,0.5) node {$D$};
+      \draw (4.5,0.5) node {$E$};
+      \draw (5.5,0.5) node {$F$};
+      \draw (6.5,0.5) node {$G$};     
+    \end{tikzpicture}      
     \caption{\textit{Top:} A cubic curve with control points $A,B,C,D$ encoded in a 1d texture with a size of 4 pixels.
-\textit{Bottom:} Two piecewise curves encoded in a 1d texture.
+\textit{Middle:} Two piecewise curves encoded in a 1d texture.
 The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.
-If C0 continuitiy is always desired between the curves, a redundant $D$ could be removed to store these curves in 7 pixels instead of 8.
+\textit{Bottom:} With $C0$ continuitiy, a redundant $D$ can be removed to store these curves in 7 pixels instead of 8.
 }
@@
 
+Taking $N$ linearly interpolated texture samples from a one dimensional texture of size $N+1$ gives us the linear interpolated values we would need to continue to perform the De Casteljeau algorithm.
+We can compute the final curve point either by doing that, or by plugging the values into the Bernstein form equation of Bezier curves.
+
 In the case of a cubic curve with control points $A,B,C,D$, the one dimensional texture will be 4 pixels in size, and three texture reads will need to be done to get the interpolations for $\overline{AB},\overline{BC},\overline{CD}$.
-Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve (order 2) to elevate those three points from order 1 to order 3, to get the final point $\stackrel{\frown}{ABCD}$.
+Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = A*s^2 + B*st + C*t^2$) to elevate those three points from order 1 to order 3, to get the final point $\stackrel{\frown}{ABCD}$.
+Sample code of this example is provided in \autoref{lst:GLSLCubicTexture1D}.
 
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a 4 pixel 1d texture.
-Linear texture sampling used to evaluate the first level of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
+Linear texture sampling is used to evaluate the linear level of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
 // 4 pixel 1d texture with control points encoded: A,B,C,D
@@
 
-vec4 CubicCurveFromTexture1D_DeCastelJeau(in float t) {
+vec4 CubicCurveFromTexture1D_DeCasteljeau(in float t) {
     vec4 AB = texture(uSampler, (t + 0.5) / c_textureSize);
@@
 \subsection{Two Dimensional Textures}
+Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd order (quadratic) Bezier curves (\autoref{fig:decdimensionality}).
 
-Two dimensional textures are textures which are $(W,H)$ pixels in size, such as $(8,8)$ or $(16,16)$ or $(32,4)$.
+This allows us to either calculate a quadratic bezier curve with a single texture read, or allows us to get the quadratic level values needed to make a higher order curve.
 
-Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd order (quadratic) Bezier basis functions (\autoref{fig:decdimensionality}).
+Knowing that a quadratic curve is just the linear interpolation of time $t$ between the points on two linear curves at time $t$, we know that our two dimensional texture needs to set up to be able to make this happen.
+The result is that if we have a $2$x$2$ texture, the top two pixels should be $P_0$ and $P_1$ and the bottom two pixels should be $P_1$ and $P_2$.
+When we do a bilinear interpolation such that we plug $t$ into both $u$ and $v$, the end result will be that $\overline{P_0P_1}$ and $\overline{P_1P_2}$ will be calculated from the $u$ axis interpolation, and then those two will be linearly interpolated across the $v$ axis to give us the final result.
 
-If you want a Bezier curve higher than order 2, once again you can take more texture samples and combine the results in the shader program.
-While more computationally expensive that moving to a higher dimensionality texture, it again results in higher precision results due to more of the computation happening in full floating point precision.
+Knowing that we can linearly interpolate between two quadratic curves to create a cubic curve, and that we can combine three quadratic curves to create a quartic curve, the pattern seems to be that we need a texture size of $(2,2*(N-1))$ to encode a curve of order $N$ into a two dimensional texture.
 
-The size of the two dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $(2*M,N)$.
-For instance, a cubic (degree 3) curve will be $(2,3)$ pixels.
-If you want to encode two piecewise cubic curves end to end, it requires $(4,3)$ pixels (\autoref{fig:texlayeout2d}).
+When actually creating that texture, we would once again see redundancies however.
+For a cubic curve with control points $P_0,P_1,P_2,P_3$ we would see that the top row of pixels was $P_0,P_1$, then the next row was $P_1,P_2$.
+That would be our first quadratic curve.
+The third row would start our second quadratic curve which would be $P_1,P_2$ and then the fourth and final row would be $P_2,P_3$.
+In this case, $P_1,P_2$ is redundant.
+If we increased the order of the curve, the pattern that we would see is that every curve after the first curve would have a redundant row.
+
+Removing that redunant row, it means that we start with a $2$x$2$ texture for a quadratic curve, and then just add a row of pixels for each order above quadratic.
+That makes the size of our texture required be only $(2,N)$.
+
+If $M$ piecewise curves are desired, each of degree $N$, we can encode them across the $X$ axis to require a texture size of $(2*M,N)$ (\autoref{fig:texlayeout2d}).
 
   \begin{figure}
+    \begin{tikzpicture}
+      \draw[step=1cm,gray,very thin] (0,0) grid (2,-2);
+      \draw (0.5,-0.5) node {$A$};
+      \draw (1.5,-0.5) node {$B$};
+      \draw (0.5,-1.5) node {$B$};
+      \draw (1.5,-1.5) node {$C$};     
+    \end{tikzpicture}
+    \hspace{5mm}  
     \begin{tikzpicture}
@@
     \end{tikzpicture}
-    \caption{\textit{Left:} A cubic curve with control points $A,B,C,D$ encoded in a 2d texture that is $(2,3)$ in size.
+    \caption{\textit{Left:} A quadratic curve with control points $A,B,C$ encoded in a 2d texture that is $(2,2)$ in size.
+\textit{Middle:} A cubic curve with control points $A,B,C,D$ encoded in a 2d texture that is $(2,3)$ in size.
 \textit{Right:} Two piecewise curves encoded in a 2d texture that is $(4,3)$ in size.
@@
 
-vec4 CubicCurveFromTexture2D_DeCastelJeau(in float t) {
+vec4 CubicCurveFromTexture2D_DeCasteljeau(in float t) {
     vec4 ABC = texture(uSampler, (vec2(0.5, 0.5)+t) / c_textureSize);
@@
 
-Three dimensional textures (often refered to as volumetric textures) are textures which are $(W,H,D)$ pixels in size such as $(8,8,2)$ or $(16,8,4)$.
+Using three dimensional textures (often refered to as volumetric textures) allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier curves (\autoref{fig:decdimensionality}).
 
-Using three dimensional textures allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier basis functions (\autoref{fig:decdimensionality}).
+This allows us to either calculate a cubic bezier curve with a single texture read, or allows us to get the cubic level values needed to make a higher order curve.
 
-Again, you can take more texture samples and combine the results in the shader program to get higher than order 3 curves if desired.
+Knowing that a cubic curve is just the linear interpolation of time $t$ between the points on two quadratic curves at time $t$, we know that our three dimensional texture needs to be set up to be able to make this happen.
+With a $2$x$2$x$2$ texture, the front $2$x$2$ pixels would encode a quadratic curve for $P_0,P_1,P_2$ and the back $2$x$2$ pixels would encode a quadratic curve for $P_1,P_2,P_3$.
+Then, when we sample the texture, plugging $t$ into $u,v$ and $w$, the result will be that it will calculate the points on the quadratic curves $P_0,P_1,P_2$ at time $t$ and also $P_1,P_2,P_3$ at time $t$, and then will interpolate across the $w$ axis to give us the final result.
 
-You may have noticed that a 1d texture can store a linear curve, but that a 2d texture cannot.
-The lowest order curve it can store is a quadratic curve.
-In the case of a 3d texture, the minimum goes up again, and the lowest order curve you can store is a cubic curve.
+You can combine two cubic curves to make a quartic curve, or three cubic curves to make a quintic curve.
+If you were to put $2$x$2$x$2$ cubic curves back to back, you would notice a redundancy like we saw in lower dimensionality textures.
+Instead of going that route though, we can just build on the redundancy removement from two dimensional textures.
 
-The size of the three dimensional texture needed for $M$ piecewise curves, each of degree $N$ is $(2*M,N-1,2)$.
-For instance, a cubic (degree 3) curve will be $(2,2,2)$ pixels.
-If you want to encode two piecewise cubic curves end to end, it requires $(4,2,2)$ pixels (\autoref{fig:texlayeout3d}).
+The size of a three dimensional texture needed to encode a curve of degree $N$ is $(2,N-1,2)$.
+If you wanted to store $M$ piecewise curves, each of degree $N$, the formula becomes $(2*M,N-1,2)$ (\autoref{fig:texlayeout3d}).
 
@@
 uniform sampler2D uSampler; 
-const vec3 c_textureSize = vec3(2.0, 2.0, 2);
+const vec3 c_textureSize = vec3(2.0, 2.0, 2.0);
 
@@
 
-TODO: TABLE to compare dimensionality
-table details...
+Increasing texture dimensionality allows you to evaluate the same order curve with fewer texture reads but comes at the cost of using more texture memory.
+We evaluated texture dimensions one, two and three, but the pattern continues for higher dimensions as well.
 
-y axis =
- * 1d, 2d, 3d, 4d?
+The table below is a comparison of texture dimensionality options.  $M$ is the number of piecewise curves being stored and $N$ is the order of the curve.
 
-x axis =
- * minimum curve order storage
- * texture size formula
- * num texture samples taken for a quintic curve? sextent curve? or maybe do quadratic, cubic, quarticorder 4, order 5?
- * texture size for them too? dims and num pixels
+\begin{tabular}{|l|l|l|l|l|}
+\hline
+ & \bf{Min. Order} & \bf{\# Samples} & \bf{Dimensions} & \bf{\# Pixels} \\ \hline
+\bf{1D} & 1 (Linear) & $N$ & $(M*(N+1))$ & $M*(N+1)*1$ \\ \hline
+\bf{2D} & 2 (Quadratic) & $N-1$ & $(2*M,N)$ & $M*(N+0)*2$\\ \hline
+\bf{3D} & 3 (Cubic) & $N-2$ & $(2*M,N-1,2)$ & $M*(N-1)*4$\\ \hline
+\bf{4D} & 4 (Quartic) & $N-3$ & $(2*M,N-2,2,2)$ & $M*(N-2)*8$\\ \hline
+\end{tabular}
 
-TODO do we want images here at all? probably not i guess...
+TODO: do we want this graph? it does show pixel usage per dimensionality
+\begin{figure}
+    \begin{tikzpicture}
+
+      \begin{axis}[xmin=1,xmax=6,ymin=0,xtick={1,...,6},ytick={0,5,10,15,20,25,30},xlabel={Order},ylabel={Pixel Count},legend pos=north west]
+
+        % 1d textures
+        \addplot[color=orange, domain=1:6]{x+1};
+        \addlegendentry{$1D$}
+
+        % 2d textures
+        \addplot[color=red, domain=2:6]{x*2};
+        \addlegendentry{$2D$}
+
+        % 3d textures
+        \addplot[color=green, domain=3:6]{(x-1)*4};
+        \addlegendentry{$3D$}
+
+        % 4d textures
+        \addplot[color=blue, domain=4:6]{(x-2)*8};
+        \addlegendentry{$4D$}
+
+      \end{axis}
+    \end{tikzpicture}
+
+    \caption{Pixel count for curve order, with different texture dimensionalities.}
+    \label{fig:decasteljeauBilinear}
+  \end{figure}
 
@@
 TODO: images to show differences.
+TODO: doing more work in shader, because using 1d textures or soemthing.  more texture reads but higher quality
 

### 2015-07-06 Paper/paper.tex
Technique Extensions

@@
 
-TODO: need to explain the layout of the pixels in the sections above somehow.  Maybe also get rid of describing what N-dimensional textures are
-
 %-------------------------------------------------------------------------
@@
 
-TODO: this.  Higher order curves without more texture reads
+If you encode Bezier curves into a texture which has multiple color channels - such as the standard four R,G,B,A - you can set up the textures such that once you read in the R,G,B,A, you can combine the channel values together such that you get a fewer number of curves per texture read, but that they are higher order.
+
+For instance, if you had a 2x2 texture, you could encode the control points A,B,C into the red channel, and the control points B,C,D into the green channel.
+Then, after you did a texture read, you could do a lerp between the red and the green channel.
+Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points A,B,C,D.
+However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher order.
+The blue and the alpha channel could either be quadratic curves, or could also be encoded such that they could be combined together to provide another cubic curve.
+
+You could also set it up such that R,G,B,A were meant to be combined together to make a quintic (degree 5) curve.
+You'd only get a single curve value per texture read, but it would be 3 degrees higher.
+You could combine the color channels either with De Casteljeaus algorithm, or with the cubic Bernstein Bezier form.
+
+If you you are combining M color channels, each of which are values from curves of order N, the resulting curve value will be order N+M-1.
+The inutitive explanation to this, is that each channel has the ability to add one more control point to the curve, regardless of what texture dimensionality you are working with.
+
+An interesting side effect to combining color channels is that the accuracy of the resulting curve gets better.
+This is because you are doing some of the math in full precision floating point, instead of the limited precision of the fixed point math in the texture sampler.
 
@@
 
-TODO: this.  Pros and cons. B-splines can be converted to piecewise Bezier with Boem's algorithm (what's it called again?).
-TODO: how to actually evaluate piecewise curves! (GLSL if needed? or just describe it)
+As mentioned earlier, you can encode multiple Bezier curves end to end within textures of any dimensionality.
+
+When you are in need of a curve with lots of control points, piecewise curves have several benefits over increasing the order of the curve.
+
+Besides the usual benefits, when encoding Bezier curves in textures, piecewise curves allow us to use lower order curves, which allows us to use lower dimensional textures, and have less computation in the shader programs.
+
+Another benefit is that there can be discontinuities between curve segments, which is sometimes desired.
+
+B-splines can also be converted to piecewise Bezier curves using Boehm's algorithm, so even though this paper talks only about Bezier curves, you could do pre-processing of B-splines to convert them to piecewise Bezier curves, and use the techniques in this paper.
+
+For a deeper look at the benefits of piecewise curves, look at....
+TODO: find a paper that talks about the pros and cons?
+
+and for a deeper discussion about the benefits of b-spline curves, look at....
+TODO: find a paper that talks about benefits of bsplines over bezier curves
+
+Evaluating a piecewise curve with this technique is very simple.
+As an example, let's say that we have a texture that is 8x2, and encodes 4 quadratic Bezier curves end to end.
+The left most 2x2 pixels encode the quadratic curve used for time $t \epsilon [0,0.25)$.
+The next block of 2x2 pixels encode the quadratic curve used for time $t \epsilon [0.25,0.5)$.
+The third block encodes time $t \epsilon [0.5,0.75)$, and the last block encodes time $t \epsilon [0.75,1.0]$.
 
@@
 
-TODO: this.
-TODO: Nurbs can be converted to rational bezier curves with Boem's algorithm as well
+Rational Bezier curves are defined by the equation:
+
+\begin{equation}
+\text{\bf{B}}(t) = \frac
+                % Nominator
+                {\sum\limits_{i=0}^n\binom {n} {i}(1-t)^{n-i}t^iw_i\text{\bf{P}}_i}
+                % Denominator
+                {\sum\limits_{i=0}^n\binom {n} {i}(1-t)^{n-i}t^iw_i}
+\label{eqn:rationalbezier}                
+\end{equation}
+
+Looking closely, we can see that we essentially have one Bezier curve devided by another.
+The numerator has a weighting and a control point, while the denominator has only a weighting, but if we were to multiply the weighting into the control point in the numerator, we would essentially have one Bezier curve divided by another.
+
+Using this technique, we can easily encode the numerator into one color channel, and the denominator into another.
+
+If we wanted to get two rational Bezier curves per texture read, we could encode the two numerators into R and G, and the denominators into B and A.
+
+Or, if we had three curves that all used the same weights, that would mean that the denominator was the same for all three curves.
+In this case, we could encode the three numerators into R,G,B and encode the denominator in A.
+
+To compute the value of rational Bezier curves, you first take your texture samples, combining them as per normal if there were multiple taken, and then after that, you divide the numerators by the denominators to get the final values.
+
+There is a limitation to encoding rational Bezier curves in this form due to the fact that texture values range from 0 to 1, but when using rational Bezier curves, weights greater than 1 are sometimes desired.
+The good news is that you can normalize the weights by dividing all weight values by the largest weight value, such that the largest weight value becomes 1.
+The result will be the same as if you had values greater than 1 in the weights.
+
+Rational Bezier curves have many uses, as they have much more flexibility over the shapes they can take, including the ability to exactly represent all conic sections.
+You can find more information about that at...
+TODO: find paper about rational bezier curves?
+
+Just as b-splines can be converted into piecewise Bezier curves, NURBS can also be converted into piecewise rational Bezier curves, again using Boehm's algorithm, which means these techniques can also apply to NURBS, if they are first preprocessed into rational Bezier curves.
 
@@
 
-TODO: this.  Each color channel is an axis.
+So far we have only talked about one dimensional - or explicit - bezier curves.
+Multidimensional Bezier curves are evaluated seperately per axis though, which means that you can encode information per axis in different color channels.
+
+With a standard R,G,B,A 2x2 texture, you could either encode four 1 dimensional Bezier curves, or you could encode two  2 dimensional Bezier curves (one in R,G and the other in B,A), or you could encode a three dimensional curve in R,G,B and have a one dimensional curve in A, or you could encode a four dimensional curve in R,G,B,A.
 

### 2015-07-13 Paper/paper.tex
Progress

@@
 A popular choice is to expose parameters as customizable curves and to quantize the curves into textures.
-This leads to either lower quality results, or more texture memory being used to accomodate higher sampling frequencies.
+Quantization leads to either lower quality results, or more texture memory being used to accomodate higher sampling frequencies.
 The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for the same costs.
-Piecewise curves, B-Splines and Nurbs are mentioned, and there are also limited applications towards vector graphics.
+Piecewise curves, B-Splines and Nurbs are addressed, and there are also limited applications towards vector graphics.
 \end{abstract}
@@
 \label{sec:introduction}
-There are two basic ways for a shader program to gain access to customized curve data.
+There are two basic ways for a shader program to have customized curve data.
 One way is to evaluate the curve on the CPU at discrete intervals and put those points into a texture that can be used by the GPU.
-The other way is to pass curve control point data from the CPU to the shader program as shader constants.
+The other way is to pass curve control point data from the CPU to the shader program as shader constants, allowing the shader program to evaluate the curve at a given time $t$.
 
-Baking curve points into a texture means that the shader program doesn't need to know what type of curve it was that made the data, nor how many control points it has, but comes at the loss of quality since there are a finite number of curve points sampled, and the data between points is just a linear interpolation between the samples.
-If higher quality is desired, you can achieve this by increasing the resolution of the texture to be able to trade accuracy for texture memory.
+Baking curve points into a texture means that the shader program doesn't need to know what type of curve it was that made the data, nor how many control points it had, but comes at the loss of quality since there are a finite number of curve points sampled, and the data between points is just a linear interpolation between the samples.
+If higher quality is desired, you can increase the resolution of the texture to be able to trade accuracy for texture memory.
 
@@
 \begin{itemize}
-  \item Curve data is encoded within a texture in such a way to allow the texture sampler to calculate points on the curve before the data reaches the shader program.
+  \item The control points of the curves are encoded in a texture.
+  \item The texture sampler calculates points on the curve before the data reaches the shader program.
   \item It gives accuracy results closer to that of shader constant curves, while having less calculation overhead.
@@
 
-The core of this technique is that the linear texture interpolation capabilities on the GPU can be mathematically equivelant to De Casteljeau's algorithm for evaluating Bezier curves.
-
-A one dimensional texture with linear sampling results in the evaluation of a linear Bezier curve (order 1), a two dimensional texture with linear sampling can result in a quadratic bezier curve (order 2), and a three dimensional texture (volumetric texture) with linear sampling can result in a cubic Bezier curve (order 3).
-
-The pattern continues for higher dimensionality textures, and curves of lower degrees can be combined in the shader program to create curves of higher degrees by either continuing De Casteljeau's algorithm or by using the Bernstein form of Bezier curves.
+The core of this technique is that the $N$-dimensional linear texture interpolation capabilities on the GPU can be mathematically equivelant to De Casteljeau's algorithm for evaluating Bezier curves.
+We can use linear texture sampling on textures of increasing dimensionalities to have the texture sampler calculate points on curves of increasing order.
 
@@
 
-The De Casteljeau algorithm shows us that we can find points on a Bezier curve by evaluating a hierarchy of linear interpolations.
-For example, a quadratic curve is the linear interpolation between the linear interpolation of {$\overline{AB}$} and {$\overline{BC}$}, using the same time $t$ for each interpolation.
+One dimensional linear texture sampling is just the linear interpolation between two data points.
+This is equivelant to the De Casteljeau algorithm when evaluating a linear curve of order 1.
+In both cases, it is just linear interpolation between two values.
 
-Bilinear interpolation is used when linear sampling is enabled and a texture sample is taking from a 2d texture.
-Bilinear interpolation is achieved by linearly interpolating across one axis (say, the X axis) and then interpolating the two results by the other axis (the Y axis).
-In bilinear interpolation, you have a $t$ and a $u$ interpolation value, and you have four values to interpolate between $A$,$B$,$C$,$D$.
+Two dimensional linear texture sampling (bilinear texture sampling) can be thought of as just the linear interpolation across the $y$ axis, of two linear interpolations across the $x$ axis.
+In other words, it is just the linear interpolation of two linear interpolations.
+
+The De Casteljeau algorithm for evaluating a quadratic curve (order 2) is also just to linear interpolate between two linear curves (order 1).
+If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolation $\overline{P_0P_1}$ which is the interpolation between $P_0$ and $P_1$ for time $t$.
+The second linear interpolation is $\overline{P_1P_2}$ and is the interpolation between $P_1$ and $P_2$ for time $t$.
+The final point on the curve will be the interpolation at time $t$ between $\overline{P_0P_1}$ and $\overline{P_1P_2}$, which we can call $\stackrel{\frown}{P_0P_1P_2}$.
+
+We could set up a texture such that the two $x$ axis interpolations would give us the values $\overline{P_0P_1}$ and $\overline{P_1P_2}$ respectively, and then the $y$ axis interpolation between those values would give us $\stackrel{\frown}{P_0P_1P_2}$.
+When sampling, we would also use texture coordinates such that the weighting is the same for the interpolations across the $x$ and $y$ axis, so that it results in the same time $t$ value for interpolation in both linear interpolations.
+
+To further see how bilinear interpolation can be equivelant to evaluating a quadratic Bezier curve with the De Casteljeau algorithm, \autoref{fig:decasteljeauBilinear} shows it visually, and you can also compare the GLSL source code in \autoref{lst:GLSLCurves}.
 
 \begin{lstlisting}[caption={GLSL implementation of bilinear interpolation and the De Casteljeau algorithm for a quadratic Bezier curve.}, label={lst:GLSLCurves}]
+float QuadraticBezier (
+  in float t,
+  in float P0, in float P1, in float P2
+) {
+    return mix(mix(P0,P1,t), mix(P1,P2,t), t);
+}
+
+// This function can be equivelant to the function above
+// by setting the parameters:
+// u = t, v = t
+// A = P0, B = P1, C = P1, D = P2
 float BilinearInterpolate (
@@
 
-float QuadraticBezier (
-  in float t,
-  in float A, in float B, in float C
-) {
-    return mix(mix(A,B,t), mix(B,C,t), t);
-}
 \end{lstlisting}
-
-Comparing the source code for these two operations  (\autoref{lst:GLSLCurves}), we begin to get an idea of how to set up the points in our texture and the u and v coordinates to use such that when performing bilinear sampling, that we will get, as output, points on a quadratic bezier curve (\autoref{fig:decasteljeauBilinear}).
 
@@
 
-Since we need to linearly interpolate between {$\overline{AB}$} and {$\overline{BC}$}, and between those results, all by the same time $t$, we need to ensure that our $u$ coordinate equals our $v$ coordinate.
+The pattern continues for higher texture dimensions and curve orders as well.
+Linear texture sampling of textures of dimension $N$ is just the linear interpolation between two linear texture samples of dimension $N-1$.
+Using the De Casteljeau algorithm to evaluate a curve of order $N$ just means that you take a linear interpolation between curves of order $N-1$.
+
+Linear texture sampling lets you control each value (each pixel), and the weighting of each level (dimension) of the interpolations, but you can set up the pixels and texture coordinates such that it evaluates a Bezier curve.
+The De Casteljeau algorithm is a subset of the $N$-dimensional linear texture sampling available on the GPU.
 
 It can be seen that the actual pixel value in a bilinear sampled texture is in the middle of a pixel.
-That means that when calculating our texture coordinates we must sample between pixel location $(0.5,0.5)$ and pixel location $(1.5,1.5)$ to get the correct results.
+That means that when calculating our texture coordinates for eg.
+a 2x2 texture, we must sample between pixel location $(0.5,0.5)$ and pixel location $(1.5,1.5)$ to get the correct results.
 
@@
   \end{figure}
+
+It is also possible to get points on curves of higher order by taking multiple texture reads and combining them either using the De Casteljeau algorithm, or by using the Bernstein form equation of Bezier curves.
 
@@
 
-This pattern continues for trilinear interpolation and beyond
-
-TODO: How to prove for N dimensions?  This section needs help
-TODO: could somehow show how N-linear sampling is same as De Casteljeaus for all N's? tree diagram or something else.
+This pattern continues for trilinear interpolation and beyond.
+$N$ dimensional linear texture sampling is just the linear interpolation between two linear texture samples of dimension $N-1$.
+Bezier curves of order $N$ are just the linear interpolation between two bezier curves of order $N-1$.
 
@@
 
-The table below is a comparison of texture dimensionality options.  $M$ is the number of piecewise curves being stored and $N$ is the order of the curve.
+The table below is a comparison of texture dimensionality options.
+$M$ is the number of piecewise curves being stored and $N$ is the order of the curve.
+To get an idea of how dimensionality and order affects the size of the required textures, take a look at \autoref{fig:pixelcount}.
 
@@
 
-TODO: do we want this graph? it does show pixel usage per dimensionality
 \begin{figure}
@@
     \caption{Pixel count for curve order, with different texture dimensionalities.}
-    \label{fig:decasteljeauBilinear}
+    \label{fig:pixelcount}
   \end{figure}
@@
 
-Besides the usual benefits, when encoding Bezier curves in textures, piecewise curves allow us to use lower order curves, which allows us to use lower dimensional textures, and have less computation in the shader programs.
+The main benefit of piecewise curves are that they allow us to use lower order curves, which allows us to use lower dimensional textures, and have less computation in the shader programs.
 
-Another benefit is that there can be discontinuities between curve segments, which is sometimes desired.
+Another benefit is that there can be discontinuities between curve segments, which is sometimes desired by artists and graphic designers.
 
-B-splines can also be converted to piecewise Bezier curves using Boehm's algorithm, so even though this paper talks only about Bezier curves, you could do pre-processing of B-splines to convert them to piecewise Bezier curves, and use the techniques in this paper.
-
-For a deeper look at the benefits of piecewise curves, look at....
-TODO: find a paper that talks about the pros and cons?
-
-and for a deeper discussion about the benefits of b-spline curves, look at....
-TODO: find a paper that talks about benefits of bsplines over bezier curves
+B-splines can also be converted to piecewise Bezier curves using Boehm's algorithm, so even though this technique only explicitly deals with Bezier curves, B-splines could be convered to piecewise Bezier curves and could be used in that form.
 
@@
 Or, if we had three curves that all used the same weights, that would mean that the denominator was the same for all three curves.
-In this case, we could encode the three numerators into R,G,B and encode the denominator in A.
+In this case, we could encode the three numerators into R,G,B and encode the denominator in A, which would give us three rational curves with a single texture read.
 
-To compute the value of rational Bezier curves, you first take your texture samples, combining them as per normal if there were multiple taken, and then after that, you divide the numerators by the denominators to get the final values.
+To compute the value of rational Bezier curves, you first take your texture samples, combining them as per normal if there were multiple taken (if needed), and then after that, you divide the numerators by the denominators to get the final values.
 
@@
 
-Rational Bezier curves have many uses, as they have much more flexibility over the shapes they can take, including the ability to exactly represent all conic sections.
-You can find more information about that at...
-TODO: find paper about rational bezier curves?
-
 Just as b-splines can be converted into piecewise Bezier curves, NURBS can also be converted into piecewise rational Bezier curves, again using Boehm's algorithm, which means these techniques can also apply to NURBS, if they are first preprocessed into rational Bezier curves.
@@
 
-So far we have only talked about one dimensional - or explicit - bezier curves.
+So far we have only talked about one dimensional - or explicit - bezier curves which take the form of $y=f(x)$.
 Multidimensional Bezier curves are evaluated seperately per axis though, which means that you can encode information per axis in different color channels.
 
-With a standard R,G,B,A 2x2 texture, you could either encode four 1 dimensional Bezier curves, or you could encode two  2 dimensional Bezier curves (one in R,G and the other in B,A), or you could encode a three dimensional curve in R,G,B and have a one dimensional curve in A, or you could encode a four dimensional curve in R,G,B,A.
+To name a few possibilities with a standard RGBA 2x2 texture, you could encode a fourth dimensional Bezier curve, or you could encode 2 two dimensional Bezier curves, or you could even encode a three dimensional rational Bezier curve using R,G,B for the numerator of each axis, and A as the denominator for all three curves.
 
@@
 
-TODO: this. HW vs SW vs HWSW hybrid vs read points yourself and do math w/o using interpolator. Everythign in between.
-TODO: images to show differences.
-TODO: doing more work in shader, because using 1d textures or soemthing.  more texture reads but higher quality
+Even though there are accuracy limitations in modern GPU texture samplers, accuracy can be increased by doing more of the calculations in the shader program, which operate at full floating point precision.
+
+A naive way to do this would be to use nearest neighbor texture sampling instead of linear, and do the linear interpolations yourself in the shader program.
+This would mean twice as many texture reads with a 1D texture, four times as many texture reads with a 2D texture, and eight times as many texture reads with a 3D texture!
+You would also be doing a lot more blending in the shader program, so your shader programs would become heavier weight.
+This solution is essentially doing software linear texture sampling.
+
+A better approach that gives the same results would be to only do one nearest neighbor texture sample per control point in the texture, and then in the shader program, either use De Casteljeau's algorithm to combine them, or use the Bernstein form equation of Bezier curves.
+At this point, you are best off just using a 1D texture to store your control points in, since you don't need any of the built in interpolation.
+
+These two techniques do all of the curve math in the shader program at full floating point precision and so are the highest quality, but are also the most computationally expensive.
+
+Another way to address accuracy would be to do some of the work in the texture sampler, and some of the work in the shader program.  This allows you to have a sliding scale for accuracy vs cost.
+
+For instance, if you had a 2x2 image which encoded a quadratic Bezier curve, you might do two texture reads, letting the texture sampler do the $x$ axis interpolation, and then you could linearly interpolate those results in the shader program in full precision floating point math.
+This would give you a result somewhere between full hardware and full software interpolation.
+
+TODO: image to show hw vs sw vs hwsw
+
+Also, if you want a higher order curve than your texture can provide with a single read, forcing you to combine multiple curve points, combining those curve points in the shader program has the nice side benefit of increasing accuracy as well.
 
@@
 
-TODO: this
-TODO: mention that it isn't ideal since this technique is only good if you already know time "t" to evaluate, which is difficult to get otherwise.
-TODO: mention that you don't have access to the control points since the interpolator does that level of math for you, but that affine transformations on the resulting curve point is equivelant to doing then on the control points.
-TODO: mention 1d curve usage
-TODO: mention polar curve usage
-TODO: mention use for color gradients
-TODO: picture of flag
-TODO: put real usages here: particle properties, and whatever else.
+This technique does have applications to vector graphics, but they are pretty limited admitedly.
+The main reason for the limitation is that this technique is good at calculating the point on a curve at time $t$, but when using curves in vector graphics situations, you usually do not know the time $t$ that you want to know the curve point for, and it is usually difficult to find it.
+
+TODO: mention loop and blinn's paper as an example of how it avoids the problem of finding the time 4.
+
+However, there are certain special situations where you can easily get the time $t$ value of the curve that you care about.
+Two of the most common situations for these are when rendering 1D explicit Bezier curves, and when rendering 1D explicit Bezier curves in polar form.
+
+Explicit Bezier curves are curves which have scalar control points and are in the form of $y=f(x)$.
+For these curves, when you plug in a value for $x$ you get a $y$ value out.
+They are unable to make curves that have multiple $y$ values for the same $x$, and the curves can't cross over themselves to make closed shapes.
+This does make them not as useful to vector graphics as 2D Bezier curves which are of the form $(x,y) = f(t)$, but they still do have some use cases.
+Rendering explicit bezier curves using this technique is very simple.
+If rendering a quad, you just choose either the $x$ or $y$ axis, normalize it from 0 to 1 and use that to calculate the other axis value by doing a texture sample.
+At this point, you can either choose a half space to color in, or you can calculate the gradient of the function (by using the built in dFdx style functions to get partial derivatives), and use that as an estimated distance to the curve.
+
+TODO: picture of halfspace and gradient distance functions.
+
+This idea can easily be extended to 1D Bezier curves rendered in polar form.
+If rendering a quad, you can use arc tangent to find the angle of the current pixel from the center, normalize that angle to 0 to 1, and then use that value to do a texture look up to calculate the value of the curve at that point.
+Once again you can then either choose a half space to color in, or you can use the gradient information to get an estimated distance to the curve, to draw a curved line.
+
+TODO: do we need an image of polar form? maybe combine with picture above and reference the same thing
+
+Another problem with using this technique for vector graphics, is that since the texture sampler is doing at least some of the calculations for us, we don't have access to the values of the control points, which can make some operations harder.
+Luckily, one property of Bezier curves is that affine transformations done to control points is equivelant to affide transformations done to points on the curve.
+This means that we can do affine transformations on the curve points provided to us by the texture sampler, and it will be as if we had performed them on the control points themselves.
+
+Lastly, in regards to vector graphics, this technique can be used to allow people to define custom color gradients.
+The benefit is that custom, non linear color gradients can be defined, and can be scaled up without decaying to the usual artifacts seen from linear texture sampling.
+
+TODO: do we need a gradient (rect / polar?) image?
+TODO: need an image of the flag
 
@@
 
+TODO: any play here with lobes and encoding curves in polar form?
+
 %-------------------------------------------------------------------------
@@
 \hspace{-2mm}\begin{tabular}{p{0.5\textwidth}p{0.5\textwidth}}
-Roy G. Biv \newline
-Colortech, Inc. \newline
-29 Red Blvd. \newline
-New York, NY 10511 \newline
-\href{mailto:roy@colortech.com}{roy@colortech.com}
-&
-
-Raymond Trace \newline
-Graphica University \newline
-37 Rue De Lambert \newline
-Paris, 75009 France \newline
-\href{mailto:rtrace@graphica.edu}{rtrace@graphica.edu} \newline
-\href{http://graphica.edu/~rtrace}{http://graphica.edu/\textasciitilde rtrace}
-
+Alan Wolfe \newline
+Blizzard Entertainment \newline
+16215 Alton Parkway \newline
+Irvine, CA 92618 \newline
+\href{mailto:awolfe@blizzard.com}{awolfe@blizzard.com}
+\href{http://blog.demofox.org}{http://blog.demofox.org}
 \end{tabular}

### 2015-07-14 Paper/paper.tex
Progress - almost all citations in!

@@
 A quick comparison of the visual quality of these three techniques can be seen in \autoref{fig:quickcomparison}.
-
-\subsection{Related Work}
-
-TODO: this
 
@@
 
-While the Bernstein form of Bezier curves is equivelant to evaluating a Bezier curve with the De Casteljeau algorithm, in practice there are differences that come up between the two.
-It is well known that the De Casteljeau algorithm is slower but more numerically robust than evaluating the Bernstein form.
+A limitation with this technique is that control points can only take values that can be stored and recalled from the specific texture format you are using.
+This can be an issue not only for the range of values possibly - such as when a texture can only hold values from 0 to 1 or 0 to 255 - but is also an issue for accuracy.
+The value range problem is easily solved by scaling the values read from the texture, but the accuracy problem is a harder problem to address.
 
-The technique presented in this paper also has numerical differences in practice.
 While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures (\autoref{fig:quickaccuracy}).
@@
 TODO: give the details of the architecture imprecision sources and cite the two papers cited from the other place!
+TODO: make this more coherent
 
@@
 
-This technique does have applications to vector graphics, but they are pretty limited admitedly.
-The main reason for the limitation is that this technique is good at calculating the point on a curve at time $t$, but when using curves in vector graphics situations, you usually do not know the time $t$ that you want to know the curve point for, and it is usually difficult to find it.
-
-TODO: mention loop and blinn's paper as an example of how it avoids the problem of finding the time 4.
+This technique does have applications to vector graphics, but they are pretty limited and there are better solutions if using Bezier curves as vector art is the goal \cite{Loop:2005:RIC:1073204.1073303,Nehab:2008:RRG:1409060.1409088}, or if the goal is to use textures for vector art data storage \cite{Green:2007:IAM:1281500.1281665}.
+The limitation is due to the fact that this technique is good at calculating the point on a curve at time $t$, but when using curves in vector graphics situations, you usually do not know the time $t$ that you want to know the curve point for, and it is usually difficult to find it.
 
@@
 TODO: real apples to apples comparisons with texture baking (can be any order!) as well as shader constants.
+TODO: maybe we don't need this
 
@@
 
-TODO: this
+In the past, work has been done to evaluate curves on the GPU using textures, but for the purposes of texture interpolation \cite{doi:10.1080/2151237X.2008.10129269}.
+The progress made on those types of techniques could likely be used in a similar fashion to directly evaluate other curve types on the GPU for purposes other than texture sampling.
 
-TODO: any play here with lobes and encoding curves in polar form?
+Extending this technique to the third dimension would be an interesting usage case, as well as exploring ways to make the vector art usage cases more attractive.
+
+There may also be usefulness in storing curves in polar form to aproximate lobes for lighting algorithms.
+
+Lastly, throughout this paper, texture coordinates were set up such that the texture samples were taken only across the diagonal of $N$-dimensional hypercubes.
+It would be interesting to explore whether deviating from the diagonal created useful properties, more complex curves, or more complex curve types so that even more usefulness could be achieved with the same number of pixels used.
 
@@
 %-------------------------------------------------------------------------
-\section*{References}
-\label{sec:references}
-TODO: this
+\small
+\bibliographystyle{jcgt}
+\bibliography{paper}
 

### 2015-07-15 Paper/paper.tex
More progress: accuracy section.

@@
   \caption{\textit{Left:} A quadratic Bezier curve written to the green channel, and the baked out equivelant using 4 pixels written to the red channel.
-\textit{Right:} The technique from this paper, also using 4 pixels, written to the green channel, and the baked out equivelant written to the red channel again for comparison.
-\label{fig:sampleconfig}}
+\textit{Right:} The technique from this paper, also using 4 pixels, written to the green channel, and the baked out equivelant written to the red channel again for comparison.}
   \label{fig:quickcomparison}
@@
 A limitation with this technique is that control points can only take values that can be stored and recalled from the specific texture format you are using.
-This can be an issue not only for the range of values possibly - such as when a texture can only hold values from 0 to 1 or 0 to 255 - but is also an issue for accuracy.
-The value range problem is easily solved by scaling the values read from the texture, but the accuracy problem is a harder problem to address.
+This can be an issue not only for the range of values possibly - such as when a texture can only hold values from 0 to 1 or 0 to 255 - but is also an issue for accuracy due being interpolated in a 9 bit (1.8) fixed point format \cite{NVIDIA}.
+The value range problem is easily solved by scaling and offsetting.
+The accuracy problem is not as easily addressed, but there are some ways mentioned later in the paper.
 
-While it's been shown that the multidimensional linear interpolation capabilities can be mathematically equivelant to the Bernstein form as well as the De Casteljeau algorithm, there are mathematical precision issues due to current GPU architectures (\autoref{fig:quickaccuracy}).
+The accuracy issues can be seen in \autoref{fig:quickaccuracy}, although the accuracy is still significantly higher than a baked out curve using the same number of pixels as seen in \autoref{fig:quickcomparison}.
 
-As shown in \autoref{fig:texbilcurve}, the quality can be significantly higher than a baked out curve for the same number of pixels however.
-There is more information on addressing accuracy in \autoref{sec:addressingaccuracyissues}.
-
-TODO: give the details of the architecture imprecision sources and cite the two papers cited from the other place!
-TODO: make this more coherent
+TODO: the 9 bit fixed point format doesn't belong mentioned where it is.
+TODO: also need to find and mention the thing about how interpolation weights are multiplied before taking it into floating point.
 

### 2015-07-15 Paper/paper.tex
More progress, starting to run low on todos! perf next?

@@
 \textit{Middle:} The texture as viewed with bilinear sampling.
-\textit{Right:} The resulting curves when sampling along the yellow line (Alpha curve omitted).}
+\textit{Right:} The resulting quadratic Bezier curves when sampling along the yellow line (Alpha curve omitted).}
   \label{fig:teaser}
@@
 
-A limitation with this technique is that control points can only take values that can be stored and recalled from the specific texture format you are using.
-This can be an issue not only for the range of values possibly - such as when a texture can only hold values from 0 to 1 or 0 to 255 - but is also an issue for accuracy due being interpolated in a 9 bit (1.8) fixed point format \cite{NVIDIA}.
-The value range problem is easily solved by scaling and offsetting.
-The accuracy problem is not as easily addressed, but there are some ways mentioned later in the paper.
+A limitation with this technique is that control points can only take values that can be stored and recalled from the specific texture format being used, which puts a limitation on the range of values able to be used, as well as the precision of the values stored.
 
-The accuracy issues can be seen in \autoref{fig:quickaccuracy}, although the accuracy is still significantly higher than a baked out curve using the same number of pixels as seen in \autoref{fig:quickcomparison}.
+Furthermore, the fractional position of a texel used in the interpolation formulas is limited to 256 values due to it being calculated with a 9 bit (1.8) fixed point format \cite{NVIDIA}.
 
-TODO: the 9 bit fixed point format doesn't belong mentioned where it is.
-TODO: also need to find and mention the thing about how interpolation weights are multiplied before taking it into floating point.
+The accuracy issues can be seen in \autoref{fig:quickaccuracy}, although the accuracy can still be significantly higher than a baked out curve using the same number of pixels as seen in \autoref{fig:quickcomparison}.
 
@@
 
+  \begin{figure}
+    \begin{tikzpicture}[x=12cm,y=4cm]
+      % border
+      \draw (0cm,0cm) rectangle (12cm,4cm);
+      % images
+      \node[anchor=south west,inner sep=0] at (0cm,0cm) {\includegraphics[width=4cm,height=4cm]{SampleHW.png}};
+      \node[anchor=south west,inner sep=0] at (4cm,0cm) {\includegraphics[width=4cm,height=4cm]{SampleHWSW.png}};
+      \node[anchor=south west,inner sep=0] at (8cm,0cm) {\includegraphics[width=4cm,height=4cm]{SampleSW.png}};
+
+    \end{tikzpicture}
+    \caption{\textit{Left:} Curve evaluted with a single texture read and bilinear texture sampling.
+\textit{Middle:} Curve evaluated with two linear texture samples, combined in the shader program.
+\textit{Right:} Curve evaluated with three texture samples (one per control point), combined in the shader program.}
+    \label{fig:samplehwsw}
+  \end{figure}
+
 Even though there are accuracy limitations in modern GPU texture samplers, accuracy can be increased by doing more of the calculations in the shader program, which operate at full floating point precision.
@@
 A naive way to do this would be to use nearest neighbor texture sampling instead of linear, and do the linear interpolations yourself in the shader program.
-This would mean twice as many texture reads with a 1D texture, four times as many texture reads with a 2D texture, and eight times as many texture reads with a 3D texture!
+This would mean twice as many texture reads with a 1D texture, four times as many texture reads with a 2D texture, and eight times as many texture reads with a 3D texture.
 You would also be doing a lot more blending in the shader program, so your shader programs would become heavier weight.
@@
 This would give you a result somewhere between full hardware and full software interpolation.
-
-TODO: image to show hw vs sw vs hwsw
+You can compare the results in \autoref{fig:samplehwsw}.
 
@@
 \label{sec:limitedapplicationsforvectorgraphics}
+
+  \begin{figure}
+    \hspace{-1.5cm}
+    \begin{tikzpicture}[x=16cm,y=4cm]
+      % images
+      \node[anchor=south west,inner sep=0] at (0cm,0cm) {\includegraphics[width=8cm,height=4cm]{Flag.png}};
+      \node[anchor=south west,inner sep=0] at (8cm,0cm) {\includegraphics[width=8cm,height=4cm]{FlagZoom.png}};
+    \end{tikzpicture}
+    \caption{\textit{Left:}An animated flag textured with vector graphics using the techniques in this paper, using an 8x4 RGBA source texture to generate curves and color gradients.
+\textit{Right:} Zooming in on part of the image to show the quality of the vector graphics.}
+    \label{fig:vectorgfx}
+  \end{figure}
 
@@
 
-TODO: picture of halfspace and gradient distance functions.
-
 This idea can easily be extended to 1D Bezier curves rendered in polar form.
@@
 Once again you can then either choose a half space to color in, or you can use the gradient information to get an estimated distance to the curve, to draw a curved line.
-
-TODO: do we need an image of polar form? maybe combine with picture above and reference the same thing
 
@@
 Lastly, in regards to vector graphics, this technique can be used to allow people to define custom color gradients.
-The benefit is that custom, non linear color gradients can be defined, and can be scaled up without decaying to the usual artifacts seen from linear texture sampling.
+The benefit is that custom, non linear color gradients can be defined, and can be zoomed into without decaying to linear interpolation.
 
-TODO: do we need a gradient (rect / polar?) image?
-TODO: need an image of the flag
-
-%-------------------------------------------------------------------------
-\section{Comparisons With Other Techniques}
-\label{sec:comparisonswithothertechniques}
-
-TODO: real apples to apples comparisons with texture baking (can be any order!) as well as shader constants.
-TODO: maybe we don't need this
+A demonstration of these usage cases can be seen in \autoref{fig:vectorgfx}.
 
@@
 
-TODO: Show some real performance values. 
-TODO: show difference between 3d texture doing cubic, vs 2d texture with 2 texture reads and shader program results.
-TODO: show results from multiple GPUs?
+TODO: perf goals are...
+* show perf of a few curve types (linear, quadratic, cubic, quartic?), using 1d, 2d, 3d textures.  show based on \# of texture reads (like hw, hwsw, sw).
+* show results from laptop as well as work machine. maybe laptop on single GPU?
+
+TODO: perf tests... at 1000x1000
+* linear    :  1d texture (1 read vs 2 reads then lerp)
+* quadratic :  1d texture (2 reads and lerp vs 3 reads and quadratic bezier), 2d texture (1 read vs 2 reads and lerp vs 3 reads and quadratic Bezier)
+* cubic     :  1d texture (3 reads and quad vs 4 reads and quartic bezier), 2d texture (), 3d texture 
+* quartic   :  1d texture, 2d texture, 3d texture
+
+TODO: mention that it matters if you are texture lookup bound or not.  correct terms for that = ??
 
@@
 
-There may also be usefulness in storing curves in polar form to aproximate lobes for lighting algorithms.
+There may also be usefulness in curves in polar form to aproximate lobes for lighting algorithms.
 

### 2015-07-17 Paper/paper.tex
Progress: made perf tests

@@
 
+Rational Bezier curves are useful because they can be used to make shapes which cannot be formed from integral Bezier curves, including perfectly representing conic sections.
 Rational Bezier curves are defined by the equation:
@@
 
-TODO: mention that it matters if you are texture lookup bound or not.  correct terms for that = ??
+TODO: mention that it matters if you are texture lookup bound or not.  correct terms for that = ?? also matters if texture is in cache or not.
+
+TODO:
+ ? does double vs float texture / position coordinates matter for perf? it seems like it does!
+ ? does unsigned char vs float texture data matter for perf?
+
+The table below shows  (dual 980m in SLI)
+TODO: ? does opengl make use of SLI?
+TODO: time in fullscreen, apparently that's the only time you can get SLI support!
+
+\begin{tabular}{|l|l|l|}
+\hline
+& \bf{HW} & \bf{SW}\\ \hline
+\bf{1D Linear} & &\\ \hline
+\bf{2D Quadratic} & &\\ \hline
+\bf{3D Cubic} & &\\ \hline
+\end{tabular}
 

### 2015-07-17 GLFW/Curves/ShaderDefs.h

@@ -51,30 +51,6 @@ SHADER_BEGIN(TrilinearTest, 1000, 500)
     SHADER_UNIFORM_TEXTURE_3D(uSampler, float, true)
 SHADER_END()
 
-SHADER_BEGIN(BilinearTest2, 1000, 1000)
-    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
-    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
-    SHADER_UNIFORM_TEXTURE_2D(uSampler, float, true)
-SHADER_END()
-
-SHADER_BEGIN(TrilinearTest2, 1000, 1000)
-    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
-    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
-    SHADER_UNIFORM_TEXTURE_3D(uSampler, float, true)
-SHADER_END()
-
-SHADER_BEGIN(BilinearTest3, 1000, 1000)
-    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
-    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
-    SHADER_UNIFORM_TEXTURE_2D(uSampler, float, false)
-SHADER_END()
-
-SHADER_BEGIN(TrilinearTest3, 1000, 1000)
-    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
-    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
-    SHADER_UNIFORM_TEXTURE_3D(uSampler, float, false)
-SHADER_END()
-
 SHADER_BEGIN(BilinearBakeTest, 1000, 500)
     SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
     SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
@@ -162,6 +138,67 @@ SHADER_BEGIN(Texture3d, 1000, 1000)
     SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 3, double)
     SHADER_UNIFORM_TEXTURE_3D(uSampler, float, true)
 SHADER_END()
+
+SHADER_BEGIN(BilinearTest2, 1000, 1000)
[…]

### 2015-07-17 GLFW/Curves/Shader_Cubic3d.cpp

@@ -97,7 +97,6 @@ const char *CShaderCubic3d::GetFragmentShader()
     }
 
     void main(void) {
-        /*
         vec4 colorValue = vec4(0.0);
 
         if (vTextureCoord.x < 0.995)
@@ -115,13 +114,6 @@ const char *CShaderCubic3d::GetFragmentShader()
             outColor = vec4(1.0);
             return;
         }
-        */
-
-        vec4 colorValue;
-        if (vTextureCoord.x <= 1.0)
-            colorValue = CubicCurveFromTexture3D(vTextureCoord.x);
-        else
-            colorValue = CubicCurveFromTexture3D(vTextureCoord.x - 1.0);
 
         vec4 values = step(vTextureCoord.yyyy, colorValue);
         values.xyz *= 0.5;

### 2015-07-17 GLFW/Curves/main.cpp

@@ -38,12 +38,16 @@ static void key_callback(GLFWwindow* window, int key, int scancode, int action, 
 //=============================================================================================================
 int main(void)
 {
+    const bool c_fullscreen = false;
+
+
     //FreeConsole();
     GLFWwindow* window;
     glfwSetErrorCallback(error_callback);
     if (!glfwInit())
         exit(EXIT_FAILURE);
-    window = glfwCreateWindow(1000, 500, "", NULL, NULL);
+
+    window = glfwCreateWindow(1000, 500, "", c_fullscreen ? glfwGetPrimaryMonitor() : NULL, NULL);
     if (!window)
     {
         glfwTerminate();
@@ -111,14 +115,18 @@ int main(void)
         char title[256];
         ++frameCount;
 
-        double currentTime = glfwGetTime();
-        if (currentTime - lastFPSTime > 1.0) {
-            double elapsed = currentTime - lastFPSTime;
-            float fps = float(frameCount) / float(elapsed);
-            sprintf(FPS, "(FPS: %0.1f / ms: %0.4f", fps, 1000.0 / fps);
-            lastFPSTime = currentTime;
-            frameCount = 0;
-            updateTitle = true;
+        // only check time every 100 loops
+        if (frameCount % 100 == 0)
+        {
+            double currentTime = glfwGetTime();
+            if (currentTime - lastFPSTime > 2.5) {
+                double elapsed = currentTime - lastFPSTime;
+                double fps = double(frameCount) / elapsed;
+                sprintf(FPS, "(FPS: %0.1f / ms: %0.4f)", fps, 1000.0 / fps);
+                lastFPSTime = currentTime;
+                frameCount = 0;
+                updateTitle = true;
+            }
         }
 
         // update the title bar if we should

### 2015-07-18 Paper/paper.tex
Perf table filled in for machine here at home.

--- 2015-07-15 Paper/paper.tex
@@
 
-TODO: perf goals are...
-* show perf of a few curve types (linear, quadratic, cubic, quartic?), using 1d, 2d, 3d textures.  show based on \# of texture reads (like hw, hwsw, sw).
-* show results from laptop as well as work machine. maybe laptop on single GPU?
+The table below was created by running a 1000x1000 pixel shader program where each pixel evaluated a curve using either linear texture sampling (HW or hardware evaluation), or did multiple texture reads to get the control points and then calculated the curve values inside of the shader program (SW or software shader program evaluation).
+Actual performance characteristics in real world scenarios will be based on other factors, such as whether the texture is in the texture cache, or whether you are texture fetch bound or compute bound in the shader program.
 
-TODO: perf tests... at 1000x1000
-* linear    :  1d texture (1 read vs 2 reads then lerp)
-* quadratic :  1d texture (2 reads and lerp vs 3 reads and quadratic bezier), 2d texture (1 read vs 2 reads and lerp vs 3 reads and quadratic Bezier)
-* cubic     :  1d texture (3 reads and quad vs 4 reads and quartic bezier), 2d texture (), 3d texture 
-* quartic   :  1d texture, 2d texture, 3d texture
+\begin{tabular}{|l|l l|}
+\hline
+& \multicolumn{2}{|c|}{NV GF GTX 980m} \\
+& \bf{HW} & \bf{SW}\\ \hline
+\bf{1D Texture / Linear Curve} & 131.8 $\mu$s & 132.7 $\mu$s \\ \hline
+\bf{2D Texture / Quadratic Curve} & 131.1 $\mu$s & 135.1 $\mu$s \\ \hline
+\bf{3D Texture / Cubic Curve} & 135.4 $\mu$s & 146.2 $\mu$s \\ \hline
+\end{tabular}
 
-TODO: mention that it matters if you are texture lookup bound or not.  correct terms for that = ??
+TODO: do a test with the cards at work, and put those results here as well!
 

### 2015-07-18 GLFW/Curves/main.cpp

@@ -12,6 +12,13 @@
 
 EShaderTest g_whichTest = EShaderTest::e_shaderFirst;
 
+void WaitForEnter()
+{
+    printf("Press Enter to quit");
+    fflush(stdin);
+    getchar();
+}
+
 //=============================================================================================================
 static void error_callback(int error, const char* description)
 {
@@ -39,7 +46,6 @@ static void key_callback(GLFWwindow* window, int key, int scancode, int action, 
 int main(void)
 {
     const bool c_fullscreen = false;
-
 
     //FreeConsole();
     GLFWwindow* window;
@@ -95,7 +101,7 @@ int main(void)
 
             int width, height;
             switch (g_whichTest){
-            #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) case e_shader##NAME: shader##NAME##.GetWidthHeight(width,height); break;
+            #define SHADER_BEGIN(NAME, WIDTH, HEIGHT) case e_shader##NAME: shader##NAME##.GetWidthHeight(width,height);  printf("switched to" #NAME "\n"); break;
             #define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
             #define SHADER_UNIFORM(NAME)
             #define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
@@ -123,6 +129,7 @@ int main(void)
                 double elapsed = currentTime - lastFPSTime;
                 double fps = double(frameCount) / elapsed;
                 sprintf(FPS, "(FPS: %0.1f / ms: %0.4f)", fps, 1000.0 / fps);
+                printf("%s\n", FPS);
                 lastFPSTime = currentTime;
                 frameCount = 0;
                 updateTitle = true;
@@ -161,5 +168,9 @@ int main(void)
     }
     glfwDestroyWindow(window);
     glfwTerminate();
+
+    if (c_fullscreen)
+        WaitForEnter();
+
     exit(EXIT_SUCCESS);
 }

### 2015-07-18 Paper/paper.tex
Progress: Spell check and some other things.

@@
 \small
-Modern graphics techniques expose internal parameters to allow re-use and to help seperate the technical implementation from artistic usage cases.
+Modern graphics techniques expose internal parameters to allow re-use and to help separate the technical implementation from artistic usage cases.
 A popular choice is to expose parameters as customizable curves and to quantize the curves into textures.
-Quantization leads to either lower quality results, or more texture memory being used to accomodate higher sampling frequencies.
+Quantization leads to either lower quality results, or more texture memory being used to accommodate higher sampling frequencies.
 The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for the same costs.
-Piecewise curves, B-Splines and Nurbs are addressed, and there are also limited applications towards vector graphics.
+Piecewise curves, B-Splines and NURBS are addressed, and there are also limited applications towards vector graphics.
 \end{abstract}
@@
   \includegraphics[width=5in]{Figure2.png}
-  \caption{\textit{Left:} A quadratic Bezier curve written to the green channel, and the baked out equivelant using 4 pixels written to the red channel.
-\textit{Right:} The technique from this paper, also using 4 pixels, written to the green channel, and the baked out equivelant written to the red channel again for comparison.}
+  \caption{\textit{Left:} A quadratic Bezier curve written to the green channel, and the baked out equivalent using 4 pixels written to the red channel.
+\textit{Right:} The technique from this paper, also using 4 pixels, written to the green channel, and the baked out equivalent written to the red channel again for comparison.}
   \label{fig:quickcomparison}
@@
 A quick comparison of the visual quality of these three techniques can be seen in \autoref{fig:quickcomparison}.
+Besides being useful for exposing internal parameters, the technique presented in this paper is also useful as an alternative to traditional shader look up tables which use linear interpolation to get points between data points.
 
@@
 
-The core of this technique is that the $N$-dimensional linear texture interpolation capabilities on the GPU can be mathematically equivelant to De Casteljeau's algorithm for evaluating Bezier curves.
+The core of this technique is that the $N$-dimensional linear texture interpolation capabilities on the GPU can be mathematically equivalent to De Casteljeau's algorithm for evaluating Bezier curves.
 We can use linear texture sampling on textures of increasing dimensionalities to have the texture sampler calculate points on curves of increasing order.
@@
 One dimensional linear texture sampling is just the linear interpolation between two data points.
-This is equivelant to the De Casteljeau algorithm when evaluating a linear curve of order 1.
+This is equivalent to the De Casteljeau algorithm when evaluating a linear curve of order 1.
 In both cases, it is just linear interpolation between two values.
@@
 
-To further see how bilinear interpolation can be equivelant to evaluating a quadratic Bezier curve with the De Casteljeau algorithm, \autoref{fig:decasteljeauBilinear} shows it visually, and you can also compare the GLSL source code in \autoref{lst:GLSLCurves}.
+To further see how bilinear interpolation can be equivalent to evaluating a quadratic Bezier curve with the De Casteljeau algorithm, \autoref{fig:decasteljeauBilinear} shows it visually, and you can also compare the GLSL source code in \autoref{lst:GLSLCurves}.
 
@@
 The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve.
-\textit{Right:} The curves resulting from sampling along the yellow line (Alpha curve ommited).}
+\textit{Right:} The curves resulting from sampling along the yellow line (Alpha curve omitted).}
     \label{fig:texbilcurve}
@@
 
-The De Casteljeau algorithm is equivelant to the Bernstein form of Bezier curves.
+The De Casteljeau algorithm is equivalent to the Bernstein form of Bezier curves.
 
@@
 
-That they are equivelant means that the Bernstein form for a given $n$ must also be able to be evaluated by $n$-Linear interpolation.
+That they are equivalent means that the Bernstein form for a given $n$ must also be able to be evaluated by $n$-Linear interpolation.
 A linear curve should be able to be evaluated by linear interpolation, a quadratic curve should be able to be evaluated by bilinear interpolation, a cubic curve should be able to be evaluated by trilinear interpolation, and so on.
@@
 The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.
-\textit{Bottom:} With $C0$ continuitiy, a redundant $D$ can be removed to store these curves in 7 pixels instead of 8.
+\textit{Bottom:} With $C0$ continuity, a redundant $D$ can be removed to store these curves in 7 pixels instead of 8.
 }
@@
 
-This allows us to either calculate a quadratic bezier curve with a single texture read, or allows us to get the quadratic level values needed to make a higher order curve.
+This allows us to either calculate a quadratic Bezier curve with a single texture read, or allows us to get the quadratic level values needed to make a higher order curve.
 
@@
 
-Removing that redunant row, it means that we start with a $2$x$2$ texture for a quadratic curve, and then just add a row of pixels for each order above quadratic.
+Removing that redundant row, it means that we start with a $2$x$2$ texture for a quadratic curve, and then just add a row of pixels for each order above quadratic.
 That makes the size of our texture required be only $(2,N)$.
@@
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,4)$ pixel 2d texture.
-Bilinear texture sampling used to evaluate the first two levesl of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture2D}]
+Bilinear texture sampling used to evaluate the first two levels of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture2D}]
 // 2x4 2d texture, rounded to the nearest powers of 2 from 2x3.
@@
 
-Using three dimensional textures (often refered to as volumetric textures) allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier curves (\autoref{fig:decdimensionality}).
+Using three dimensional textures (often referred to as volumetric textures) allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier curves (\autoref{fig:decdimensionality}).
 
-This allows us to either calculate a cubic bezier curve with a single texture read, or allows us to get the cubic level values needed to make a higher order curve.
+This allows us to either calculate a cubic Bezier curve with a single texture read, or allows us to get the cubic level values needed to make a higher order curve.
 
@@
 If you were to put $2$x$2$x$2$ cubic curves back to back, you would notice a redundancy like we saw in lower dimensionality textures.
-Instead of going that route though, we can just build on the redundancy removement from two dimensional textures.
+Instead of going that route though, we can just build on what we did for two dimensional textures.
 
@@
 You'd only get a single curve value per texture read, but it would be 3 degrees higher.
-You could combine the color channels either with De Casteljeaus algorithm, or with the cubic Bernstein Bezier form.
+You could combine the color channels either with De Casteljeau's algorithm, or with the cubic Bernstein Bezier form.
 
 If you you are combining M color channels, each of which are values from curves of order N, the resulting curve value will be order N+M-1.
-The inutitive explanation to this, is that each channel has the ability to add one more control point to the curve, regardless of what texture dimensionality you are working with.
+The intuitive explanation to this, is that each channel has the ability to add one more control point to the curve, regardless of what texture dimensionality you are working with.
 
@@
 
-B-splines can also be converted to piecewise Bezier curves using Boehm's algorithm, so even though this technique only explicitly deals with Bezier curves, B-splines could be convered to piecewise Bezier curves and could be used in that form.
+B-splines can also be converted to piecewise Bezier curves using Boehm's algorithm, so even though this technique only explicitly deals with Bezier curves, B-splines could be converted to piecewise Bezier curves and could be used in that form.
 
@@
 
-Rational Bezier curves are useful because they can be used to make shapes which cannot be formed from integral Bezier curves, including perfectly representing conic sections.
+\begin{figure}
+    \begin{tikzpicture}[x=12cm,y=6cm]
+      \node[anchor=south west,inner sep=0] at (0cm,0cm) {\includegraphics[width=12cm,height=6cm]{Rational.png}};  
+    \end{tikzpicture}
+
+    \caption{A rational bezier spline showing cosine in green and sine in red.
+The white line is the true value of those functions.
+\textit{Left:} Evaluated with hardware sampling and then division.
+\textit{Right:} Evaluated by reading the control points into the shader program, calculating the curves, and then doing a division.}
+    \label{fig:rationalbeziersincos}
+  \end{figure}
+
+Rational Bezier curves are useful because they can be used to make shapes which cannot be formed from integral Bezier curves, including perfectly representing conic sections which mean that they can also represent sine and cosine as seen in \autoref{fig:rationalbeziersincos}.
 Rational Bezier curves are defined by the equation:
@@
 
-Looking closely, we can see that we essentially have one Bezier curve devided by another.
+Looking closely, we can see that we essentially have one Bezier curve divided by another.
 The numerator has a weighting and a control point, while the denominator has only a weighting, but if we were to multiply the weighting into the control point in the numerator, we would essentially have one Bezier curve divided by another.
@@
 
-So far we have only talked about one dimensional - or explicit - bezier curves which take the form of $y=f(x)$.
-Multidimensional Bezier curves are evaluated seperately per axis though, which means that you can encode information per axis in different color channels.
+So far we have only talked about one dimensional - or explicit - Bezier curves which take the form of $y=f(x)$.
+Multidimensional Bezier curves are evaluated separately per axis though, which means that you can encode information per axis in different color channels.
 
@@
 Another problem with using this technique for vector graphics, is that since the texture sampler is doing at least some of the calculations for us, we don't have access to the values of the control points, which can make some operations harder.
-Luckily, one property of Bezier curves is that affine transformations done to control points is equivelant to affide transformations done to points on the curve.
+Luckily, one property of Bezier curves is that affine transformations done to control points is equivalent to affine transformations done to points on the curve.
 This means that we can do affine transformations on the curve points provided to us by the texture sampler, and it will be as if we had performed them on the control points themselves.
@@
 The table below was created by running a 1000x1000 pixel shader program where each pixel evaluated a curve using either linear texture sampling (HW or hardware evaluation), or did multiple texture reads to get the control points and then calculated the curve values inside of the shader program (SW or software shader program evaluation).
+The numbers shown are the time spent rendering each frame, in microseconds and the texture format is R8G8B8A8.
 Actual performance characteristics in real world scenarios will be based on other factors, such as whether the texture is in the texture cache, or whether you are texture fetch bound or compute bound in the shader program.
@@
 
-There may also be usefulness in curves in polar form to aproximate lobes for lighting algorithms.
+There may also be usefulness in curves in polar form to approximate lobes for lighting algorithms.
 

### 2015-07-18 Paper/paper.tex
I read through the paper and made some changes

@@
 Quantization leads to either lower quality results, or more texture memory being used to accommodate higher sampling frequencies.
-The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for the same costs.
+The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for similar costs.
 Piecewise curves, B-Splines and NURBS are addressed, and there are also limited applications towards vector graphics.
@@
 Baking curve points into a texture means that the shader program doesn't need to know what type of curve it was that made the data, nor how many control points it had, but comes at the loss of quality since there are a finite number of curve points sampled, and the data between points is just a linear interpolation between the samples.
-If higher quality is desired, you can increase the resolution of the texture to be able to trade accuracy for texture memory.
-
-Passing control point data to a shader program as shader constants allows you to get high quality curve calculations, but comes at the cost of the shader program being written in a very specific way for the type of curve you want to use, as well as more shader program instructions to calculate specific curve points.
+If higher quality is desired, you can increase the resolution of the texture to trade accuracy for texture memory.
+
+Passing control point data to a shader program as shader constants allows you to get high quality curve calculations, but comes at the cost of the shader program being written specifically for the type of curve you want to use, and also takes more shader program instructions to calculate specific curve points.
 
@@
   \includegraphics[width=5in]{Figure2.png}
-  \caption{\textit{Left:} A quadratic Bezier curve written to the green channel, and the baked out equivalent using 4 pixels written to the red channel.
-\textit{Right:} The technique from this paper, also using 4 pixels, written to the green channel, and the baked out equivalent written to the red channel again for comparison.}
+  \caption{Quadratic Bezier curves (yellow) compared to a 4x1 baked out (quantized) texture for the same curve (red).
+\textit{Left:} Curve evaluated from shader program constants.
+\textit{Right:}  The technique from this paper - the curve is stored in a 2x2 texture and a bilinear texture sample is taken to get each point on the curve.}
   \label{fig:quickcomparison}
@@
 A quick comparison of the visual quality of these three techniques can be seen in \autoref{fig:quickcomparison}.
-Besides being useful for exposing internal parameters, the technique presented in this paper is also useful as an alternative to traditional shader look up tables which use linear interpolation to get points between data points.
+
+Besides being useful for exposing internal parameters, the technique presented in this paper is also useful as an alternative to traditional shader look up tables, since this technique allows non linear interpolation between data points, where traditional lookup table textures only offer linear interpolation between data points.
 
@@
 \subsection{Intuition}
+
+TODO: clean up the notation here!
 
@@
 
-Two dimensional linear texture sampling (bilinear texture sampling) can be thought of as just the linear interpolation across the $y$ axis, of two linear interpolations across the $x$ axis.
-In other words, it is just the linear interpolation of two linear interpolations.
-
-The De Casteljeau algorithm for evaluating a quadratic curve (order 2) is also just to linear interpolate between two linear curves (order 1).
+Two dimensional linear texture sampling (bilinear texture sampling) can be thought of as just the linear interpolation across the $y$ axis, of two linear interpolations across the $x$ axis (or an interpolation across the $x$ axis of two linear interpolations across the $y$ axis - order doesn't matter).
+In other words, bilinear texture sampling is just the linear interpolation of two linear interpolations.
+
+The De Casteljeau algorithm for evaluating a quadratic curve (order 2) is also just a linear interpolation between two linear interpolations.
 If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolation $\overline{P_0P_1}$ which is the interpolation between $P_0$ and $P_1$ for time $t$.
@@
 We could set up a texture such that the two $x$ axis interpolations would give us the values $\overline{P_0P_1}$ and $\overline{P_1P_2}$ respectively, and then the $y$ axis interpolation between those values would give us $\stackrel{\frown}{P_0P_1P_2}$.
-When sampling, we would also use texture coordinates such that the weighting is the same for the interpolations across the $x$ and $y$ axis, so that it results in the same time $t$ value for interpolation in both linear interpolations.
+When sampling, we would also use texture coordinates such it results in the same time $t$ value for interpolation on each axis.
 
@@
 
-// This function can be equivelant to the function above
-// by setting the parameters:
+// This function is equivelant to the function above when:
 // u = t, v = t
@@
 
-Linear texture sampling lets you control each value (each pixel), and the weighting of each level (dimension) of the interpolations, but you can set up the pixels and texture coordinates such that it evaluates a Bezier curve.
-The De Casteljeau algorithm is a subset of the $N$-dimensional linear texture sampling available on the GPU.
+Compared to a quadratic curve evaluated with De Casteljeau's algorithm, bilinear texture sampling has two blend weights instead of one, and has four values to interpolate between instead of three, but you can set a texture up such that when you sample it a specific way, you get as output a quadratic Bezier curve.
+Because of this, the De Casteljeau algorithm is a subset of the $N$-dimensional linear texture sampling available on the GPU.
 
@@
 
-The common pixel formats contain four color channels – Red, Green, Blue and Alpha – which allows us to be able to evaluate four curves with a single texture read (\autoref{fig:texbilcurve}).
+The common pixel formats contain four color channels –-- Red, Green, Blue and Alpha –-- which allows us to be able to evaluate four curves with a single texture read (\autoref{fig:texbilcurve}).
 
@@
 
+TODO: fix up notation to be consistant (Px vs A,B,C,D)
+
 The De Casteljeau algorithm is equivalent to the Bernstein form of Bezier curves.
@@
 We'll use $t$ and $u$ as the interpolation weights of each interpolation.
+We will linearly interpolate between linear interpolations $E(u)$ and $F(u)$ by $t$ to get out a result of $P(t,u)$
 
@@
 In our usage case of bilinear interpolation to evaluate Bernstein polynomials, $P_0$ will be $A$, $P_1$ and $P_2$ will both be $B$, and $P_3$ will be $C$.
-Also, $t$ and $u$ are the same in our usage case so we'll just replace $u$ with $t$.
+Also, we set $t$ and $u$ equal in our usage case so we'll replace $u$ with $t$.
 We will also replace $(1-t)$ with $s$ for readability.
@@
 
-If we replace $A$,$B$,$C$ with $P_0$, $P_1$, $P_2$, and $s$ with $(1-t)$ we then get the familiar equation back out.
+If we replace $A$,$B$,$C$ with $P_0$, $P_1$, $P_2$, and $s$ with $(1-t)$ we then get the familiar equation below, which is the Bernstein form of a quadratic Bezier curve.
 
@@
 
-This pattern continues for trilinear interpolation and beyond.
+This pattern continues for trilinear interpolation mapping to a cubic curve, and beyond.
 $N$ dimensional linear texture sampling is just the linear interpolation between two linear texture samples of dimension $N-1$.
@@
 
+While this technique is able to be used with any texture dimensionality, there are different characteristics for each choice.  Those characteristics will be explored here.
+
 \newcommand*\circled[1]{\tikz[baseline=(char.base)]{
@@
 \end{figure}
-
-While this technique is able to be used with any texture dimensionality, there are different characteristics for each choice.  Those characteristics will be explored here.
 
@@
 
-Knowing that a quadratic curve is just the linear interpolation of time $t$ between the points on two linear curves at time $t$, we know that our two dimensional texture needs to set up to be able to make this happen.
+Knowing that a quadratic curve is just the linear interpolation of time $t$ between the points on two linear curves at time $t$, we have to find a way to make a texture that will cause this to happen with bilinear interpolation.
 The result is that if we have a $2$x$2$ texture, the top two pixels should be $P_0$ and $P_1$ and the bottom two pixels should be $P_1$ and $P_2$.
@@
 
+GLSL source code is also provided below to help see how that would work for sampling a cubic curve from a two dimensional texture, with two bilinear texture samples combined to create the final cubic curve.
+
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,4)$ pixel 2d texture.
@@
 
-Knowing that a cubic curve is just the linear interpolation of time $t$ between the points on two quadratic curves at time $t$, we know that our three dimensional texture needs to be set up to be able to make this happen.
+Knowing that a cubic curve is just the linear interpolation of time $t$ between the points on two quadratic curves at time $t$, we need to find a way to set up a 3d texture to make this happen with trilinear texture sampling.
 With a $2$x$2$x$2$ texture, the front $2$x$2$ pixels would encode a quadratic curve for $P_0,P_1,P_2$ and the back $2$x$2$ pixels would encode a quadratic curve for $P_1,P_2,P_3$.
@@
 
+Below is some GLSL source code showing how you would sample a cubic curve stored in a 3d 2x2x2 texture, using trilinear texture sampling.
+
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,2,2)$ pixel 3d texture.
@@
 
-Rational Bezier curves are useful because they can be used to make shapes which cannot be formed from integral Bezier curves, including perfectly representing conic sections which mean that they can also represent sine and cosine as seen in \autoref{fig:rationalbeziersincos}.
+Rational Bezier curves are useful because they can be used to make shapes which cannot be formed from integral Bezier curves, including perfectly representing conic sections.
+This also means that they can accurately represent sine and cosine as seen in \autoref{fig:rationalbeziersincos}.
 Rational Bezier curves are defined by the equation:
@@
 
-Looking closely, we can see that we essentially have one Bezier curve divided by another.
-The numerator has a weighting and a control point, while the denominator has only a weighting, but if we were to multiply the weighting into the control point in the numerator, we would essentially have one Bezier curve divided by another.
-
-Using this technique, we can easily encode the numerator into one color channel, and the denominator into another.
+If we were to multiply the weight into the control point for the numerator, We can see that we essentially have one Bezier curve divided by another.
+Using the techniques in this paper, we could easily encode the numerator into one color channel, and the denominator into another.
 
@@
 
-So far we have only talked about one dimensional - or explicit - Bezier curves which take the form of $y=f(x)$.
+So far we have only talked about one dimensional --- or explicit --- Bezier curves which take the form of $y=f(x)$.
 Multidimensional Bezier curves are evaluated separately per axis though, which means that you can encode information per axis in different color channels.
@@
 
-For instance, if you had a 2x2 image which encoded a quadratic Bezier curve, you might do two texture reads, letting the texture sampler do the $x$ axis interpolation, and then you could linearly interpolate those results in the shader program in full precision floating point math.
+For instance, if you had a 2x2 image which encoded a quadratic Bezier curve, you might do two texture reads, letting the texture sampler do the $x$ axis interpolation, and then you could linearly interpolate those results in the shader program in full precision floating point math for the $y$ axis.
 This would give you a result somewhere between full hardware and full software interpolation.
@@
 \label{sec:limitedapplicationsforvectorgraphics}
+
+This technique does have applications to vector graphics, but they are pretty limited and there are better solutions if using Bezier curves as vector art is the goal \cite{Loop:2005:RIC:1073204.1073303,Nehab:2008:RRG:1409060.1409088}, or if the goal is to use textures for vector art data storage \cite{Green:2007:IAM:1281500.1281665}.
+The limitation is due to the fact that this technique is good at calculating the point on a curve at time $t$, but when using curves in vector graphics situations, you usually do not know the time $t$ that you want to know the curve point for, and it is usually difficult to find it.
+
+However, there are certain special situations where you can easily get the time $t$ value of the curve that you care about.
+Two of the most common situations for these are when rendering 1D explicit Bezier curves, and when rendering 1D explicit Bezier curves in polar form.
+
+Explicit Bezier curves are curves which have scalar control points and are in the form of $y=f(x)$.
+For these curves, when you plug in a value for $x$ you get a $y$ value out.
+They are unable to make curves that have multiple $y$ values for the same $x$, and the curves can't cross over themselves to make closed shapes.
+This does make them not as useful to vector graphics as 2D Bezier curves which are of the form $(x,y) = f(t)$, but they still do have some use cases.
+Rendering explicit Bezier curves using this technique is very simple.
+If rendering a quad, you just choose either the $x$ or $y$ axis, normalize it from 0 to 1 and use that to calculate the other axis value by doing a texture sample.
+At this point, you can either choose a half space to color in, or you can calculate the gradient of the function (by using the built in dFdx style functions to get partial derivatives), and use that as an estimated distance to the curve.
+
+This idea can easily be extended to 1D Bezier curves rendered in polar form.
+If rendering a quad, you can use arc tangent to find the angle of the current pixel from the center, normalize that angle to 0 to 1, and then use that value to do a texture look up to calculate the value of the curve at that point.
+Once again you can then either choose a half space to color in, or you can use the gradient information to get an estimated distance to the curve, to draw a curved line.
+
+Another problem with using this technique for vector graphics, is that since the texture sampler is doing at least some of the calculations for us, we don't have access to the values of the control points, which can make some operations harder.
+Luckily, one property of Bezier curves is that affine transformations done to control points is equivalent to affine transformations done to points on the curve.
+This means that we can do affine transformations on the curve points provided to us by the texture sampler, and it will be as if we had performed them on the control points themselves.
+
+Lastly, in regards to vector graphics, this technique can be used to allow people to define custom color gradients.
+The benefit is that custom, non linear color gradients can be defined, and can be zoomed into without decaying to linear interpolation.
 
@@
   \end{figure}
-
-This technique does have applications to vector graphics, but they are pretty limited and there are better solutions if using Bezier curves as vector art is the goal \cite{Loop:2005:RIC:1073204.1073303,Nehab:2008:RRG:1409060.1409088}, or if the goal is to use textures for vector art data storage \cite{Green:2007:IAM:1281500.1281665}.
-The limitation is due to the fact that this technique is good at calculating the point on a curve at time $t$, but when using curves in vector graphics situations, you usually do not know the time $t$ that you want to know the curve point for, and it is usually difficult to find it.
-
-However, there are certain special situations where you can easily get the time $t$ value of the curve that you care about.
-Two of the most common situations for these are when rendering 1D explicit Bezier curves, and when rendering 1D explicit Bezier curves in polar form.
-
-Explicit Bezier curves are curves which have scalar control points and are in the form of $y=f(x)$.
-For these curves, when you plug in a value for $x$ you get a $y$ value out.
-They are unable to make curves that have multiple $y$ values for the same $x$, and the curves can't cross over themselves to make closed shapes.
-This does make them not as useful to vector graphics as 2D Bezier curves which are of the form $(x,y) = f(t)$, but they still do have some use cases.
-Rendering explicit bezier curves using this technique is very simple.
-If rendering a quad, you just choose either the $x$ or $y$ axis, normalize it from 0 to 1 and use that to calculate the other axis value by doing a texture sample.
-At this point, you can either choose a half space to color in, or you can calculate the gradient of the function (by using the built in dFdx style functions to get partial derivatives), and use that as an estimated distance to the curve.
-
-This idea can easily be extended to 1D Bezier curves rendered in polar form.
-If rendering a quad, you can use arc tangent to find the angle of the current pixel from the center, normalize that angle to 0 to 1, and then use that value to do a texture look up to calculate the value of the curve at that point.
-Once again you can then either choose a half space to color in, or you can use the gradient information to get an estimated distance to the curve, to draw a curved line.
-
-Another problem with using this technique for vector graphics, is that since the texture sampler is doing at least some of the calculations for us, we don't have access to the values of the control points, which can make some operations harder.
-Luckily, one property of Bezier curves is that affine transformations done to control points is equivalent to affine transformations done to points on the curve.
-This means that we can do affine transformations on the curve points provided to us by the texture sampler, and it will be as if we had performed them on the control points themselves.
-
-Lastly, in regards to vector graphics, this technique can be used to allow people to define custom color gradients.
-The benefit is that custom, non linear color gradients can be defined, and can be zoomed into without decaying to linear interpolation.
 

### 2015-07-19 Paper/paper.tex
Replaced order with Degree

@@
 Quantization leads to either lower quality results, or more texture memory being used to accommodate higher sampling frequencies.
-The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any order, resulting in higher fidelity for similar costs.
+The technique presented in this paper leverages the capabilities of GPU texture samplers to allow more efficient storage and evaluation of both integral and rational Bezier curves of any degree, resulting in higher fidelity for similar costs.
 Piecewise curves, B-Splines and NURBS are addressed, and there are also limited applications towards vector graphics.
@@
   \item It gives accuracy results closer to that of shader constant curves, while having less calculation overhead.
-  \item The technique can support both integral and rational Bezier curves of any order and can also be used for piecewise curves.
+  \item The technique can support both integral and rational Bezier curves of any degree and can also be used for piecewise curves.
   \item The curve type must be decided on in advance, like when using the shader constant method.
@@
 The core of this technique is that the $N$-dimensional linear texture interpolation capabilities on the GPU can be mathematically equivalent to De Casteljeau's algorithm for evaluating Bezier curves.
-We can use linear texture sampling on textures of increasing dimensionalities to have the texture sampler calculate points on curves of increasing order.
+We can use linear texture sampling on textures of increasing dimensionalities to have the texture sampler calculate points on curves of increasing degree.
 
@@
 One dimensional linear texture sampling is just the linear interpolation between two data points.
-This is equivalent to the De Casteljeau algorithm when evaluating a linear curve of order 1.
+This is equivalent to the De Casteljeau algorithm when evaluating a linear curve of degree 1.
 In both cases, it is just linear interpolation between two values.
@@
 
-The De Casteljeau algorithm for evaluating a quadratic curve (order 2) is also just a linear interpolation between two linear interpolations.
+The De Casteljeau algorithm for evaluating a quadratic curve (degree 2) is also just a linear interpolation between two linear interpolations.
 If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolation $\overline{P_0P_1}$ which is the interpolation between $P_0$ and $P_1$ for time $t$.
@@
 
-The pattern continues for higher texture dimensions and curve orders as well.
+The pattern continues for higher texture dimensions and curve degrees as well.
 Linear texture sampling of textures of dimension $N$ is just the linear interpolation between two linear texture samples of dimension $N-1$.
-Using the De Casteljeau algorithm to evaluate a curve of order $N$ just means that you take a linear interpolation between curves of order $N-1$.
+Using the De Casteljeau algorithm to evaluate a curve of degree $N$ just means that you take a linear interpolation between curves of degree $N-1$.
 
@@
 
-It is also possible to get points on curves of higher order by taking multiple texture reads and combining them either using the De Casteljeau algorithm, or by using the Bernstein form equation of Bezier curves.
+It is also possible to get points on curves of higher degree by taking multiple texture reads and combining them either using the De Casteljeau algorithm, or by using the Bernstein form equation of Bezier curves.
 
@@
 $N$ dimensional linear texture sampling is just the linear interpolation between two linear texture samples of dimension $N-1$.
-Bezier curves of order $N$ are just the linear interpolation between two bezier curves of order $N-1$.
+Bezier curves of degree $N$ are just the linear interpolation between two Bezier curves of degree $N-1$.
 
@@
 
-Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st order (linear) Bezier curves (\autoref{fig:decdimensionality}).
-
-Since the De Casteljeau algorithm just interpolates between linear interpolations, we can take more texture samples and combine them in the shader program to get higher order curves.
-For an order $N$ Bezier curve, the De Casteljeau algorithm requires $2^{N-1}$ linear interpolations for the linear level of the tree.
-You need two pixels to perform a linear interpolation, so it seems that we would need $2^N$ pixels to store a curve of order $N$ in a 1 dimensional textures.
+Using one dimensional textures, the built in texture interpolation is only able to perform linear interpolation, which allows calculations of only 1st degree (linear) Bezier curves (\autoref{fig:decdimensionality}).
+
+Since the De Casteljeau algorithm just interpolates between linear interpolations, we can take more texture samples and combine them in the shader program to get higher degree curves.
+For a degree $N$ Bezier curve, the De Casteljeau algorithm requires $2^{N-1}$ linear interpolations for the linear level of the tree.
+You need two pixels to perform a linear interpolation, so it seems that we would need $2^N$ pixels to store a curve of degree $N$ in a 1 dimensional textures.
 For a cubic curve, that would look like this: $[P_0,P_1,P_1,P_2,P_1,P_2,P_2,P_3]$.
@@
 Firstly, there are redundant lerps in the list for lerping between $P_1$ and $P_2$.
-As the order of the curve increases, the number of redundancies increase as well.
+As the degree of the curve increases, the number of redundancies increase as well.
 We don't want to have to pay the cost of pixel storage and texture samples for redundancies, so because we have $N+1$ control points and we only ever sample between  $P_i$ and $P_{i+1}$, we only need to store $N$ lerps in the 1 dimensional texture, which would mean we would need $N*2$ pixels.
@@
 $P_1$ and $P_2$ each show up twice.
-As the order of the curve increases, we would notice the pattern that all control points show up twice except the end points.
+As the degree of the curve increases, we would notice the pattern that all control points show up twice except the end points.
 We can remove these redundancies and still be able to get the same information out.
-The result of removing these redundancies is that our texture only needs to contain each control point once, which means we only need $N+1$ pixels to encode a curve of order $N$.
+The result of removing these redundancies is that our texture only needs to contain each control point once, which means we only need $N+1$ pixels to encode a curve of degree $N$.
 The cubic curve now looks like this: $[P_0,P_1,P_2,P_3]$.
@@
 In the case of a cubic curve with control points $A,B,C,D$, the one dimensional texture will be 4 pixels in size, and three texture reads will need to be done to get the interpolations for $\overline{AB},\overline{BC},\overline{CD}$.
-Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = A*s^2 + B*st + C*t^2$) to elevate those three points from order 1 to order 3, to get the final point $\stackrel{\frown}{ABCD}$.
+Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = A*s^2 + B*st + C*t^2$) to elevate those three points from degree 1 to degree 3, to get the final point $\stackrel{\frown}{ABCD}$.
 Sample code of this example is provided in \autoref{lst:GLSLCubicTexture1D}.
@@
 \subsection{Two Dimensional Textures}
-Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd order (quadratic) Bezier curves (\autoref{fig:decdimensionality}).
-
-This allows us to either calculate a quadratic Bezier curve with a single texture read, or allows us to get the quadratic level values needed to make a higher order curve.
+Using two dimensional textures allows the texture interpolator to perform bilinear interpolation, which allows calculations of 2nd degree (quadratic) Bezier curves (\autoref{fig:decdimensionality}).
+
+This allows us to either calculate a quadratic Bezier curve with a single texture read, or allows us to get the quadratic level values needed to make a higher degree curve.
 
@@
 
-Knowing that we can linearly interpolate between two quadratic curves to create a cubic curve, and that we can combine three quadratic curves to create a quartic curve, the pattern seems to be that we need a texture size of $(2,2*(N-1))$ to encode a curve of order $N$ into a two dimensional texture.
+Knowing that we can linearly interpolate between two quadratic curves to create a cubic curve, and that we can combine three quadratic curves to create a quartic curve, the pattern seems to be that we need a texture size of $(2,2*(N-1))$ to encode a curve of degree $N$ into a two dimensional texture.
 
@@
 In this case, $P_1,P_2$ is redundant.
-If we increased the order of the curve, the pattern that we would see is that every curve after the first curve would have a redundant row.
-
-Removing that redundant row, it means that we start with a $2$x$2$ texture for a quadratic curve, and then just add a row of pixels for each order above quadratic.
+If we increased the degree of the curve, the pattern that we would see is that every curve after the first curve would have a redundant row.
+
+Removing that redundant row, it means that we start with a $2$x$2$ texture for a quadratic curve, and then just add a row of pixels for each degree above quadratic.
 That makes the size of our texture required be only $(2,N)$.
@@
 
-Using three dimensional textures (often referred to as volumetric textures) allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd order (cubic) Bezier curves (\autoref{fig:decdimensionality}).
-
-This allows us to either calculate a cubic Bezier curve with a single texture read, or allows us to get the cubic level values needed to make a higher order curve.
+Using three dimensional textures (often referred to as volumetric textures) allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd degree (cubic) Bezier curves (\autoref{fig:decdimensionality}).
+
+This allows us to either calculate a cubic Bezier curve with a single texture read, or allows us to get the cubic level values needed to make a higher degree curve.
 
@@
 
-Increasing texture dimensionality allows you to evaluate the same order curve with fewer texture reads but comes at the cost of using more texture memory.
+Increasing texture dimensionality allows you to evaluate the same degree curve with fewer texture reads but comes at the cost of using more texture memory.
 We evaluated texture dimensions one, two and three, but the pattern continues for higher dimensions as well.
@@
 The table below is a comparison of texture dimensionality options.
-$M$ is the number of piecewise curves being stored and $N$ is the order of the curve.
-To get an idea of how dimensionality and order affects the size of the required textures, take a look at \autoref{fig:pixelcount}.
+$M$ is the number of piecewise curves being stored and $N$ is the degree of the curve.
+To get an idea of how dimensionality and degree affects the size of the required textures, take a look at \autoref{fig:pixelcount}.
 
@@
 \hline
- & \bf{Min. Order} & \bf{\# Samples} & \bf{Dimensions} & \bf{\# Pixels} \\ \hline
+ & \bf{Min. Degree} & \bf{\# Samples} & \bf{Dimensions} & \bf{\# Pixels} \\ \hline
 \bf{1D} & 1 (Linear) & $N$ & $(M*(N+1))$ & $M*(N+1)*1$ \\ \hline
@@
 
-      \begin{axis}[xmin=1,xmax=6,ymin=0,xtick={1,...,6},ytick={0,5,10,15,20,25,30},xlabel={Order},ylabel={Pixel Count},legend pos=north west]
+      \begin{axis}[xmin=1,xmax=6,ymin=0,xtick={1,...,6},ytick={0,5,10,15,20,25,30},xlabel={Degree},ylabel={Pixel Count},legend pos=north west]
 
@@
 
-    \caption{Pixel count for curve order, with different texture dimensionalities.}
+    \caption{Pixel count for curve degree, with different texture dimensionalities.}
     \label{fig:pixelcount}
@@
 
-If you encode Bezier curves into a texture which has multiple color channels - such as the standard four R,G,B,A - you can set up the textures such that once you read in the R,G,B,A, you can combine the channel values together such that you get a fewer number of curves per texture read, but that they are higher order.
+If you encode Bezier curves into a texture which has multiple color channels - such as the standard four R,G,B,A - you can set up the textures such that once you read in the R,G,B,A, you can combine the channel values together such that you get a fewer number of curves per texture read, but that they are higher degree.
 
@@
 Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points A,B,C,D.
-However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher order.
+However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher degree.
 The blue and the alpha channel could either be quadratic curves, or could also be encoded such that they could be combined together to provide another cubic curve.
@@
 
-If you you are combining M color channels, each of which are values from curves of order N, the resulting curve value will be order N+M-1.
+If you you are combining M color channels, each of which are values from curves of degree N, the resulting curve value will be degree N+M-1.
 The intuitive explanation to this, is that each channel has the ability to add one more control point to the curve, regardless of what texture dimensionality you are working with.
@@
 
-When you are in need of a curve with lots of control points, piecewise curves have several benefits over increasing the order of the curve.
-
-The main benefit of piecewise curves are that they allow us to use lower order curves, which allows us to use lower dimensional textures, and have less computation in the shader programs.
+When you are in need of a curve with lots of control points, piecewise curves have several benefits over increasing the degree of the curve.
+
+The main benefit of piecewise curves are that they allow us to use lower degree curves, which allows us to use lower dimensional textures, and have less computation in the shader programs.
 
@@
 
-Also, if you want a higher order curve than your texture can provide with a single read, forcing you to combine multiple curve points, combining those curve points in the shader program has the nice side benefit of increasing accuracy as well.
+Also, if you want a higher degree curve than your texture can provide with a single read, forcing you to combine multiple curve points, combining those curve points in the shader program has the nice side benefit of increasing accuracy as well.
 
@@
 The benefit is that custom, non linear color gradients can be defined, and can be zoomed into without decaying to linear interpolation.
-
-  \begin{figure}
-    \hspace{-1.5cm}
-    \begin{tikzpicture}[x=16cm,y=4cm]
-      % images
-      \node[anchor=south west,inner sep=0] at (0cm,0cm) {\includegraphics[width=8cm,height=4cm]{Flag.png}};
-      \node[anchor=south west,inner sep=0] at (8cm,0cm) {\includegraphics[width=8cm,height=4cm]{FlagZoom.png}};
-    \end{tikzpicture}
-    \caption{\textit{Left:}An animated flag textured with vector graphics using the techniques in this paper, using an 8x4 RGBA source texture to generate curves and color gradients.
-\textit{Right:} Zooming in on part of the image to show the quality of the vector graphics.}
-    \label{fig:vectorgfx}
-  \end{figure}
 

### 2015-07-19 Paper/paper.tex
Notation cleanup WIP

@@
 
-TODO: clean up the notation here!
-
 One dimensional linear texture sampling is just the linear interpolation between two data points.
@@
 The De Casteljeau algorithm for evaluating a quadratic curve (degree 2) is also just a linear interpolation between two linear interpolations.
-If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolation $\overline{P_0P_1}$ which is the interpolation between $P_0$ and $P_1$ for time $t$.
-The second linear interpolation is $\overline{P_1P_2}$ and is the interpolation between $P_1$ and $P_2$ for time $t$.
-The final point on the curve will be the interpolation at time $t$ between $\overline{P_0P_1}$ and $\overline{P_1P_2}$, which we can call $\stackrel{\frown}{P_0P_1P_2}$.
-
-We could set up a texture such that the two $x$ axis interpolations would give us the values $\overline{P_0P_1}$ and $\overline{P_1P_2}$ respectively, and then the $y$ axis interpolation between those values would give us $\stackrel{\frown}{P_0P_1P_2}$.
+If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolated point $Q_{0,1}$ which is the interpolation between $P_0$ and $P_1$ for time $t$.
+The second linear interpolation is $Q_{1,2}$ and is the interpolation between $P_1$ and $P_2$ for time $t$.
+The final point on the curve will be the interpolation at time $t$ between $Q_{0,1}$ and $Q_{1,2}$, which we can call $R_{0,1,2}$.
+
+We could set up a texture such that the two $x$ axis interpolations would give us the values $Q_{0,1}$ and $Q_{1,2}$ respectively, and then the $y$ axis interpolation between those values would give us $R_{0,1,2}$.
 When sampling, we would also use texture coordinates such it results in the same time $t$ value for interpolation on each axis.
@@
       \draw[darkgreen,->] (0.5,1.0) -- (1.0,0.0);
-      \draw[red]          (0.25,0.5) node[anchor=east] {$\overline{AB}$};
-      \draw[darkgreen]    (0.75,0.5) node[anchor=west] {$\overline{BC}$};
+      \draw[red]          (0.25,0.5) node[anchor=east] {$Q_{0,1}$};
+      \draw[darkgreen]    (0.75,0.5) node[anchor=west] {$Q_{1,2}$};
       % control point labels
-      \draw (0.0,0.0) node[anchor=east]  {\bf{A}};
-      \draw (0.5,1.0) node[anchor=south] {\bf{B}};
-      \draw (1.0,0.0) node[anchor=west]  {\bf{C}};
+      \draw (0.0,0.0) node[anchor=east]  {$\bf{P_0}$};
+      \draw (0.5,1.0) node[anchor=south] {$\bf{P_1}$};
+      \draw (1.0,0.0) node[anchor=west]  {$\bf{P_2}$};
       % draw a line from AB->AC for time = 0.75
       \draw[orange,->] (0.3,0.6) -- (0.8,0.4);
-      \draw[orange] (0.40,0.55) node[anchor=south west] {$\stackrel{\frown}{ABC}$};
+      \draw[orange] (0.40,0.55) node[anchor=south west] {$R_{0,1,2}$};
       % draw the point at t=0.6 and label underneath the curve
@@
         % corner labels
-        \draw (0,0) node[anchor=north east] {\bf{A}};
-        \draw (1,0) node[anchor=north west] {\bf{B}};     
-        \draw (0,1) node[anchor=south east] {\bf{B}};
-        \draw (1,1) node[anchor=south west] {\bf{C}};     
+        \draw (0,0) node[anchor=north east] {$\bf{P_0}$};
+        \draw (1,0) node[anchor=north west] {$\bf{P_1}$};     
+        \draw (0,1) node[anchor=south east] {$\bf{P_1}$};
+        \draw (1,1) node[anchor=south west] {$\bf{P_2}$};     
         % x axis interpolation
         \draw[red,->]       (0.0,0.1) -- (1.0,0.1);
-        \draw[red]          (0.4,0.1) node[anchor=south] {$\overline{AB}$};
+        \draw[red]          (0.4,0.1) node[anchor=south] {$Q_{0,1}$};
         \draw[darkgreen,->] (0.0,0.9) -- (1.0,0.9);
-        \draw[darkgreen]    (0.4,0.9) node[anchor=north] {$\overline{BC}$};
+        \draw[darkgreen]    (0.4,0.9) node[anchor=north] {$Q_{1,2}$};
         % y axis interpolation
         \draw[orange,->]    (0.6,0.0) -- (0.6,1.0);
-        \draw[orange]     (0.6,0.5) node[anchor=west] {$\stackrel{\frown}{ABC}$};
+        \draw[orange]     (0.6,0.5) node[anchor=west] {$R_{0,1,2}$};
         % draw the point at t=0.6 and label for it
@@
     \end{tikzpicture} 
-    \caption{\textit{Left:} A quadratic Bezier curve evaluated at {\bf{t}}=0.6 for control points A,B,C using the De Casteljeau algorithm.
-\textit{Right:} The De Casteljeau algorithm using bilinear interpolation.
-Note that in this case, the X axis is evaluated before the Y, but the Y axis could be evaluated before the X for the same results.}
+    \caption{\textit{Left:} A quadratic Bezier curve evaluated at {\bf{t}}=0.6 using the De Casteljeau algorithm.  \textit{Right:} The De Casteljeau algorithm using bilinear interpolation.}
     \label{fig:decasteljeauBilinear}
@@
 
-TODO: fix up notation to be consistant (Px vs A,B,C,D)
-
-The De Casteljeau algorithm is equivalent to the Bernstein form of Bezier curves.
+The De Casteljeau algorithm is equivalent to the Bernstein form of Bezier curves (\autoref{eqn:bernsteinform}).
 
@@
 
-That they are equivalent means that the Bernstein form for a given $n$ must also be able to be evaluated by $n$-Linear interpolation.
+This means that the Bernstein form for a given $n$ must also be able to be evaluated by $n$-Linear interpolation.
 A linear curve should be able to be evaluated by linear interpolation, a quadratic curve should be able to be evaluated by bilinear interpolation, a cubic curve should be able to be evaluated by trilinear interpolation, and so on.
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (4,1);
-      \draw (0.5,0.5) node {$A$};
-      \draw (1.5,0.5) node {$B$};
-      \draw (2.5,0.5) node {$C$};
-      \draw (3.5,0.5) node {$D$};
+      \draw (0.5,0.5) node {$P_0$};
+      \draw (1.5,0.5) node {$P_1$};
+      \draw (2.5,0.5) node {$P_2$};
+      \draw (3.5,0.5) node {$P_3$};
     \end{tikzpicture}
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (8,1);
-      \draw (0.5,0.5) node {$A$};
-      \draw (1.5,0.5) node {$B$};
-      \draw (2.5,0.5) node {$C$};
-      \draw (3.5,0.5) node {$D$};
-      \draw (4.5,0.5) node {$D$};
-      \draw (5.5,0.5) node {$E$};
-      \draw (6.5,0.5) node {$F$};
-      \draw (7.5,0.5) node {$G$};     
+      \draw (0.5,0.5) node {$P_0$};
+      \draw (1.5,0.5) node {$P_1$};
+      \draw (2.5,0.5) node {$P_2$};
+      \draw (3.5,0.5) node {$P_3$};
+      \draw (4.5,0.5) node {$P_3$};
+      \draw (5.5,0.5) node {$P_4$};
+      \draw (6.5,0.5) node {$P_5$};
+      \draw (7.5,0.5) node {$P_6$};     
     \end{tikzpicture}
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (7,1);
-      \draw (0.5,0.5) node {$A$};
-      \draw (1.5,0.5) node {$B$};
-      \draw (2.5,0.5) node {$C$};
-      \draw (3.5,0.5) node {$D$};
-      \draw (4.5,0.5) node {$E$};
-      \draw (5.5,0.5) node {$F$};
-      \draw (6.5,0.5) node {$G$};     
-    \end{tikzpicture}      
-    \caption{\textit{Top:} A cubic curve with control points $A,B,C,D$ encoded in a 1d texture with a size of 4 pixels.
-\textit{Middle:} Two piecewise curves encoded in a 1d texture.
-The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.
-\textit{Bottom:} With $C0$ continuity, a redundant $D$ can be removed to store these curves in 7 pixels instead of 8.
+      \draw (0.5,0.5) node {$P_0$};
+      \draw (1.5,0.5) node {$P_1$};
+      \draw (2.5,0.5) node {$P_2$};
+      \draw (3.5,0.5) node {$P_3$};
+      \draw (4.5,0.5) node {$P_4$};
+      \draw (5.5,0.5) node {$P_5$};
+      \draw (6.5,0.5) node {$P_6$};     
+    \end{tikzpicture}      
+    \caption{\textit{Top:} A cubic curve encoded in a 1d texture with a size of 4 pixels.
+\textit{Middle:} Two piecewise cubic curves encoded in a 1d texture with $C0$ continuity.
+\textit{Bottom:} With $C0$ continuity, a redundant $P_3$ can be removed to store these curves in 7 pixels instead of 8.
 }
@@
 
-In the case of a cubic curve with control points $A,B,C,D$, the one dimensional texture will be 4 pixels in size, and three texture reads will need to be done to get the interpolations for $\overline{AB},\overline{BC},\overline{CD}$.
-Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = A*s^2 + B*st + C*t^2$) to elevate those three points from degree 1 to degree 3, to get the final point $\stackrel{\frown}{ABCD}$.
+In the case of a cubic curve with four control points, the one dimensional texture will be 4 pixels in size, and three texture reads will need to be done to get the interpolations along the line segments for $\overline{P_0P_1},\overline{P_1P_2},\overline{P_2P_3}$.
+Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = P_0*s^2 + P_1*2st + P_2*t^2$) to elevate those three points from degree 1 to degree 3, to get the final point on the curve.
 Sample code of this example is provided in \autoref{lst:GLSLCubicTexture1D}.
@@
 Linear texture sampling is used to evaluate the linear level of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
-// 4 pixel 1d texture with control points encoded: A,B,C,D
-uniform sampler1D uSampler; 
+uniform sampler1D uSampler;  // 4x1 texture: $P_0,P_1,P_2,P_3$
 const float c_textureSize = 4.0;
@@
 vec4 CubicCurveFromTexture1D_DeCasteljeau(in float t) {
-    vec4 AB = texture(uSampler, (t + 0.5) / c_textureSize);
-    vec4 BC = texture(uSampler, (t + 1.5) / c_textureSize;
-    vec4 CD = texture(uSampler, (t + 2.5) / c_textureSize);
-    vec4 ABC = mix(AB, BC, t);
-    vec4 BCD = mix(BC, CD, t);
-    return mix(ABC, BCD, t);
+    vec4 P0P1 = texture(uSampler, (t + 0.5) / c_textureSize);
+    vec4 P1P2 = texture(uSampler, (t + 1.5) / c_textureSize);
+    vec4 P2P3 = texture(uSampler, (t + 2.5) / c_textureSize);
+    vec4 P0P1P2 = mix(P0P1, P1P2, t);
+    vec4 P1P2P3 = mix(P1P2, P2P3, t);
+    return mix(P0P1P2, P1P2P3, t);
 }
@@
 vec4 CubicCurveFromTexture1D_Bernstein(in float t) {
-    vec4 AB = texture(uSampler, (t + 0.5) / c_textureSize);
-    vec4 BC = texture(uSampler, (t + 1.5) / c_textureSize);
-    vec4 CD = texture(uSampler, (t + 2.5) / c_textureSize);
+    vec4 P0P1 = texture(uSampler, (t + 0.5) / c_textureSize);
+    vec4 P1P2 = texture(uSampler, (t + 1.5) / c_textureSize);
+    vec4 P2P3 = texture(uSampler, (t + 2.5) / c_textureSize);
     float s = (1 - t);
@@
     // Quadratic Bezier Curve = A*s*s + B*2*s*t + C*t*t
-    return AB*s2 + BC*2.0*s*t + CD*t2;
+    return P0P1*s2 + P1P2*2.0*s*t + P2P3*t2;
 }
@@
 The result is that if we have a $2$x$2$ texture, the top two pixels should be $P_0$ and $P_1$ and the bottom two pixels should be $P_1$ and $P_2$.
-When we do a bilinear interpolation such that we plug $t$ into both $u$ and $v$, the end result will be that $\overline{P_0P_1}$ and $\overline{P_1P_2}$ will be calculated from the $u$ axis interpolation, and then those two will be linearly interpolated across the $v$ axis to give us the final result.
+When we do a bilinear interpolation such that we plug $t$ into both $u$ and $v$, the end result will be that the interpolations between $\overline{P_0P_1}$ and $\overline{P_1P_2}$ will be calculated from the $u$ axis interpolations, and then those two will be linearly interpolated across the $v$ axis to give us the final result.
 
@@
 Removing that redundant row, it means that we start with a $2$x$2$ texture for a quadratic curve, and then just add a row of pixels for each degree above quadratic.
-That makes the size of our texture required be only $(2,N)$.
+That makes the size of our texture required be only $(2,N)$ where $N$ is greater than 1.
 
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (2,-2);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};     
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};     
     \end{tikzpicture}
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (2,-3);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};
-      \draw (0.5,-2.5) node {$C$};
-      \draw (1.5,-2.5) node {$D$};      
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};
+      \draw (0.5,-2.5) node {$P_2$};
+      \draw (1.5,-2.5) node {$P_3$};      
     \end{tikzpicture}
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (4,-3);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};
-      \draw (0.5,-2.5) node {$C$};
-      \draw (1.5,-2.5) node {$D$};
-
-      \draw (2.5,-0.5) node {$D$};
-      \draw (3.5,-0.5) node {$E$};
-      \draw (2.5,-1.5) node {$E$};
-      \draw (3.5,-1.5) node {$F$};
-      \draw (2.5,-2.5) node {$F$};
-      \draw (3.5,-2.5) node {$G$};          
-    \end{tikzpicture}
-    \caption{\textit{Left:} A quadratic curve with control points $A,B,C$ encoded in a 2d texture that is $(2,2)$ in size.
-\textit{Middle:} A cubic curve with control points $A,B,C,D$ encoded in a 2d texture that is $(2,3)$ in size.
-\textit{Right:} Two piecewise curves encoded in a 2d texture that is $(4,3)$ in size.
-The control points for the first curve are $A,B,C,D$ and the control points for the second curve are $D,E,F,G$.}
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};
+      \draw (0.5,-2.5) node {$P_2$};
+      \draw (1.5,-2.5) node {$P_3$};
+
+      \draw (2.5,-0.5) node {$P_3$};
+      \draw (3.5,-0.5) node {$P_4$};
+      \draw (2.5,-1.5) node {$P_4$};
+      \draw (3.5,-1.5) node {$P_5$};
+      \draw (2.5,-2.5) node {$P_5$};
+      \draw (3.5,-2.5) node {$P_6$};          
+    \end{tikzpicture}
+    \caption{\textit{Left:} A quadratic curve encoded in a 2d texture that is $(2,2)$ in size.
+\textit{Middle:} A cubic curve encoded in a 2d texture that is $(2,3)$ in size.
+\textit{Right:} Two piecewise cubic curves encoded in a 2d texture with $C0$ continuity that is $(4,3)$ in size.}
     \label{fig:texlayeout2d}
@@
 vec4 CubicCurveFromTexture2D_DeCasteljeau(in float t) {
-    vec4 ABC = texture(uSampler, (vec2(0.5, 0.5)+t) / c_textureSize);
-    vec4 BCD = texture(uSampler, (vec2(0.5, 1.5)+t) / c_textureSize);
-    return mix(ABC, BCD, t);
+    vec4 P0P1P2 = texture(uSampler,(vec2(0.5, 0.5)+t)/c_textureSize);
+    vec4 P1P2P3 = texture(uSampler,(vec2(0.5, 1.5)+t)/c_textureSize);
+    return mix(P0P1P2, P1P2P3, t);
 }
@@
 vec4 CubicCurveFromTexture2D_Bernstein(in float t) {
-    vec4 ABC = texture(uSampler, (vec2(0.5, 0.5)+t) / c_textureSize);
-    vec4 BCD = texture(uSampler, (vec2(0.5, 1.5)+t) / c_textureSize);
+    vec4 P0P1P2 = texture(uSampler,(vec2(0.5, 0.5)+t)/c_textureSize);
+    vec4 P1P2P3 = texture(uSampler,(vec2(0.5, 1.5)+t)/c_textureSize);
     float s = (1 - t);
     // Linear Bezier Curve = A*s + B*t
-    return ABC*s + BCD*t;
+    return P0P1P2*s + P1P2P3*t;
 }
@@
 \subsection{Three Dimensional Textures}
+
+TODO: continue from this point cleaning up notation (overline BS as well as A,B,C control points)
 

### 2015-07-19 Paper/paper.tex
v 0.99 -> basically ready to review and me re-read a few times!

@@
 Linear texture sampling is used to evaluate the linear level of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
-uniform sampler1D uSampler;  // 4x1 texture: $P_0,P_1,P_2,P_3$
-const float c_textureSize = 4.0;
+uniform sampler1D uSampler;  
+const float c_textureSize = 4.0; // $P_0,P_1,P_2,P_3$
 
@@
 Bilinear texture sampling used to evaluate the first two levels of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture2D}]
-// 2x4 2d texture, rounded to the nearest powers of 2 from 2x3.
 uniform sampler2D uSampler; 
-const vec2 c_textureSize = vec2(2.0,4.0);
+const vec2 c_textureSize = vec2(2.0,4.0); // rounded up from 2x3
 
@@
 
-TODO: continue from this point cleaning up notation (overline BS as well as A,B,C control points)
-
 Using three dimensional textures (often referred to as volumetric textures) allows the texture interpolator to evaluate trilinear interpolation, which allows calculations of 3rd degree (cubic) Bezier curves (\autoref{fig:decdimensionality}).
@@
 If you were to put $2$x$2$x$2$ cubic curves back to back, you would notice a redundancy like we saw in lower dimensionality textures.
-Instead of going that route though, we can just build on what we did for two dimensional textures.
+Instead of going that route, we can build on what we did for two dimensional textures.
 
@@
       \draw[step=1cm,gray,very thin] (0,0,0) grid (2,-2,0);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};
 
@@
         \draw[step=1cm,gray,dashed] (0,0,0) grid (2,-2,0);
-        \draw[gray] (0.5,-0.5) node {$B$};
-        \draw[gray] (1.5,-0.5) node {$C$};
-        \draw[gray] (0.5,-1.5) node {$C$};
-        \draw[gray] (1.5,-1.5) node {$D$};
+        \draw[gray] (0.5,-0.5) node {$P_1$};
+        \draw[gray] (1.5,-0.5) node {$P_2$};
+        \draw[gray] (0.5,-1.5) node {$P_2$};
+        \draw[gray] (1.5,-1.5) node {$P_3$};
       \end{scope}
@@
       \draw[step=1cm,gray,very thin] (0,0,0) grid (4,-2,0);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};
-
-      \draw (2.5,-0.5) node {$E$};
-      \draw (3.5,-0.5) node {$F$};
-      \draw (2.5,-1.5) node {$F$};
-      \draw (3.5,-1.5) node {$G$};
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};
+
+      \draw (2.5,-0.5) node {$P_4$};
+      \draw (3.5,-0.5) node {$P_5$};
+      \draw (2.5,-1.5) node {$P_5$};
+      \draw (3.5,-1.5) node {$P_6$};
 
@@
         \draw[step=1cm,gray,dashed] (0,0,0) grid (4,-2,0);
-        \draw[gray] (0.5,-0.5) node {$B$};
-        \draw[gray] (1.5,-0.5) node {$C$};
-        \draw[gray] (0.5,-1.5) node {$C$};
-        \draw[gray] (1.5,-1.5) node {$D$};
-
-        \draw[gray] (2.5,-0.5) node {$F$};
-        \draw[gray] (3.5,-0.5) node {$G$};
-        \draw[gray] (2.5,-1.5) node {$G$};
-        \draw[gray] (3.5,-1.5) node {$H$};
+        \draw[gray] (0.5,-0.5) node {$P_1$};
+        \draw[gray] (1.5,-0.5) node {$P_2$};
+        \draw[gray] (0.5,-1.5) node {$P_2$};
+        \draw[gray] (1.5,-1.5) node {$P_3$};
+
+        \draw[gray] (2.5,-0.5) node {$P_5$};
+        \draw[gray] (3.5,-0.5) node {$P_6$};
+        \draw[gray] (2.5,-1.5) node {$P_6$};
+        \draw[gray] (3.5,-1.5) node {$P_7$};
       \end{scope}
@@
       \draw[step=1cm,gray,very thin] (0,0,0) grid (2,-3,0);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};
-      \draw (0.5,-2.5) node {$C$};
-      \draw (1.5,-2.5) node {$D$};
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};
+      \draw (0.5,-2.5) node {$P_2$};
+      \draw (1.5,-2.5) node {$P_3$};
 
@@
         \draw[step=1cm,gray,dashed] (0,0,0) grid (2,-3,0);
-        \draw[gray] (0.5,-0.5) node {$B$};
-        \draw[gray] (1.5,-0.5) node {$C$};
-        \draw[gray] (0.5,-1.5) node {$C$};
-        \draw[gray] (1.5,-1.5) node {$D$};
-        \draw[gray] (0.5,-2.5) node {$D$};
-        \draw[gray] (1.5,-2.5) node {$E$};
+        \draw[gray] (0.5,-0.5) node {$P_1$};
+        \draw[gray] (1.5,-0.5) node {$P_2$};
+        \draw[gray] (0.5,-1.5) node {$P_2$};
+        \draw[gray] (1.5,-1.5) node {$P_3$};
+        \draw[gray] (0.5,-2.5) node {$P_3$};
+        \draw[gray] (1.5,-2.5) node {$P_4$};
       \end{scope}
@@
       \draw[step=1cm,gray,very thin] (0,0,0) grid (4,-3,0);
-      \draw (0.5,-0.5) node {$A$};
-      \draw (1.5,-0.5) node {$B$};
-      \draw (0.5,-1.5) node {$B$};
-      \draw (1.5,-1.5) node {$C$};
-      \draw (0.5,-2.5) node {$C$};
-      \draw (1.5,-2.5) node {$D$};
-
-      \draw (2.5,-0.5) node {$F$};
-      \draw (3.5,-0.5) node {$G$};
-      \draw (2.5,-1.5) node {$G$};
-      \draw (3.5,-1.5) node {$H$};
-      \draw (2.5,-2.5) node {$H$};
-      \draw (3.5,-2.5) node {$I$};
+      \draw (0.5,-0.5) node {$P_0$};
+      \draw (1.5,-0.5) node {$P_1$};
+      \draw (0.5,-1.5) node {$P_1$};
+      \draw (1.5,-1.5) node {$P_2$};
+      \draw (0.5,-2.5) node {$P_2$};
+      \draw (1.5,-2.5) node {$P_3$};
+
+      \draw (2.5,-0.5) node {$P_5$};
+      \draw (3.5,-0.5) node {$P_6$};
+      \draw (2.5,-1.5) node {$P_6$};
+      \draw (3.5,-1.5) node {$P_7$};
+      \draw (2.5,-2.5) node {$P_7$};
+      \draw (3.5,-2.5) node {$P_8$};
 
@@
         \draw[step=1cm,gray,dashed] (0,0,0) grid (4,-3,0);
-        \draw[gray] (0.5,-0.5) node {$B$};
-        \draw[gray] (1.5,-0.5) node {$C$};
-        \draw[gray] (0.5,-1.5) node {$C$};
-        \draw[gray] (1.5,-1.5) node {$D$};
-        \draw[gray] (0.5,-2.5) node {$D$};
-        \draw[gray] (1.5,-2.5) node {$E$};
-
-        \draw[gray] (2.5,-0.5) node {$G$};
-        \draw[gray] (3.5,-0.5) node {$H$};
-        \draw[gray] (2.5,-1.5) node {$H$};
-        \draw[gray] (3.5,-1.5) node {$I$};
-        \draw[gray] (2.5,-2.5) node {$I$};
-        \draw[gray] (3.5,-2.5) node {$J$};
+        \draw[gray] (0.5,-0.5) node {$P_1$};
+        \draw[gray] (1.5,-0.5) node {$P_2$};
+        \draw[gray] (0.5,-1.5) node {$P_2$};
+        \draw[gray] (1.5,-1.5) node {$P_3$};
+        \draw[gray] (0.5,-2.5) node {$P_3$};
+        \draw[gray] (1.5,-2.5) node {$P_4$};
+
+        \draw[gray] (2.5,-0.5) node {$P_6$};
+        \draw[gray] (3.5,-0.5) node {$P_7$};
+        \draw[gray] (2.5,-1.5) node {$P_7$};
+        \draw[gray] (3.5,-1.5) node {$P_8$};
+        \draw[gray] (2.5,-2.5) node {$P_8$};
+        \draw[gray] (3.5,-2.5) node {$P_9$};
       \end{scope}
@@
 
+%-------------------------------------------------------------------------
+\section{Extensions}
+\label{sec:extensions}
+
+There are a few ways to extend this technique for more options.
+
+\subsection{Combining Color Channels}
+
 \begin{figure}
@@
 
-%-------------------------------------------------------------------------
-\section{Extensions}
-\label{sec:extensions}
-
-There are a few ways to extend this technique for more options.
-
-\subsection{Combining Color Channels}
-
 If you encode Bezier curves into a texture which has multiple color channels - such as the standard four R,G,B,A - you can set up the textures such that once you read in the R,G,B,A, you can combine the channel values together such that you get a fewer number of curves per texture read, but that they are higher degree.
 
-For instance, if you had a 2x2 texture, you could encode the control points A,B,C into the red channel, and the control points B,C,D into the green channel.
-Then, after you did a texture read, you could do a lerp between the red and the green channel.
-Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points A,B,C,D.
-However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher degree.
+For instance, if you had a 2x2 texture, you could encode the control points $P_0,P_1,P_2$ into the red channel, and the control points $P_1,P_2,P_3$ into the green channel.
+Then, after you did a texture read, you could do a lerp between the red and the green channel values.
+Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points $P_0,P_1,P_2,P_3$  However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher degree.
 The blue and the alpha channel could either be quadratic curves, or could also be encoded such that they could be combined together to provide another cubic curve.
@@
 
-If you you are combining M color channels, each of which are values from curves of degree N, the resulting curve value will be degree N+M-1.
-The intuitive explanation to this, is that each channel has the ability to add one more control point to the curve, regardless of what texture dimensionality you are working with.
-
-An interesting side effect to combining color channels is that the accuracy of the resulting curve gets better.
+If you you are combining $M$ color channels, each of which are values from curves of degree $N$, the resulting curve value will be degree $N+M-1$.
+The intuitive explanation to this, is that each channel has the ability to add one more control point to the curve, regardless of what texture dimensionality you are working with, and each control point added raises the curve one degree.
+
+An interesting side effect to combining color channels is that the accuracy of the resulting curve improves.
 This is because you are doing some of the math in full precision floating point, instead of the limited precision of the fixed point math in the texture sampler.
@@
 \label{sec:indexofsupplementalmaterials}
-TODO: this
+TODO: put information about where the zip can be downloaded.
+
+The zip file contains a folder named WebGL which contains the WebGL demos, and a folder named GLFW which contains the GLFW (windows) C++ OpenGL demos.
+
+\paragraph{\textbf{WebGL Folder}}
+\begin{itemize}
+  \item \textit{index.html} --- An index of the demos.
+  \item \textit{demo.html} --- A sandbox for exploring the various options of the technique.
+  \item \textit{flag.html} --- A vector art demo showing a waving flag and allowing you to modify some of the options used when rendering.
+  \item \textit{rational.html} --- Rational curve demo, showing sine and cosine compared to their actual values as computed by a shader program.
+\end{itemize}
+
+\paragraph{\textbf{GLFW Folder}}
+\begin{itemize}
+  \item \textit{Curves} --- The folder that contains the source code and the project and solution file for the demos.
+  \item \textit{glew-1.12.0} --- The glew library used for the demos.
+  \item \textit{glfw-3.1.1} --- The glfw library used for the demos.  
+\end{itemize}
 

### 2015-08-12 Paper/paper.tex
Started working on feedback from paper

@@
 One way is to evaluate the curve on the CPU at discrete intervals and put those points into a texture that can be used by the GPU.
-The other way is to pass curve control point data from the CPU to the shader program as shader constants, allowing the shader program to evaluate the curve at a given time $t$.
+The other way is to pass curve control point data from the CPU to the shader program as shader constants, allowing the shader program to evaluate the curve at a given $t$.
 
@@
   \includegraphics[width=5in]{Figure2.png}
-  \caption{Quadratic Bezier curves (yellow) compared to a 4x1 baked out (quantized) texture for the same curve (red).
-\textit{Left:} Curve evaluated from shader program constants.
-\textit{Right:}  The technique from this paper - the curve is stored in a 2x2 texture and a bilinear texture sample is taken to get each point on the curve.}
+  \caption{Quadratic Curve  \textit{Left:} Yellow is the curve calculated from shader program constants.
+Red is the same curve baked out in a 4x1 texture.
+\textit{Right:}  Yellow uses the technique from this paper to encode the curve in a 2x2 texture.
+Red is the same curve baked out in a 4x1 texture again for comparison.}
   \label{fig:quickcomparison}
@@
 The De Casteljeau algorithm for evaluating a quadratic curve (degree 2) is also just a linear interpolation between two linear interpolations.
-If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolated point $Q_{0,1}$ which is the interpolation between $P_0$ and $P_1$ for time $t$.
-The second linear interpolation is $Q_{1,2}$ and is the interpolation between $P_1$ and $P_2$ for time $t$.
-The final point on the curve will be the interpolation at time $t$ between $Q_{0,1}$ and $Q_{1,2}$, which we can call $R_{0,1,2}$.
+If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolated point $Q_{0,1}$ which is the interpolation between $P_0$ and $P_1$ at $t$.
+The second linear interpolation is $Q_{1,2}$ and is the interpolation between $P_1$ and $P_2$ at $t$.
+The final point on the curve will be the interpolation at $t$ between $Q_{0,1}$ and $Q_{1,2}$, which we can call $R_{0,1,2}$.
 
 We could set up a texture such that the two $x$ axis interpolations would give us the values $Q_{0,1}$ and $Q_{1,2}$ respectively, and then the $y$ axis interpolation between those values would give us $R_{0,1,2}$.
-When sampling, we would also use texture coordinates such it results in the same time $t$ value for interpolation on each axis.
+When sampling, we would also use texture coordinates such it results in the same $t$ value for interpolation on each axis.
 
@@
 
-Knowing that a quadratic curve is just the linear interpolation of time $t$ between the points on two linear curves at time $t$, we have to find a way to make a texture that will cause this to happen with bilinear interpolation.
+Knowing that a quadratic curve is just the linear interpolation at $t$ between the points on two linear curves at $t$, we have to find a way to make a texture that will cause this to happen with bilinear interpolation.
 The result is that if we have a $2$x$2$ texture, the top two pixels should be $P_0$ and $P_1$ and the bottom two pixels should be $P_1$ and $P_2$.
@@
 
-Knowing that a cubic curve is just the linear interpolation of time $t$ between the points on two quadratic curves at time $t$, we need to find a way to set up a 3d texture to make this happen with trilinear texture sampling.
+Knowing that a cubic curve is just the linear interpolation of $t$ between the points on two quadratic curves at $t$, we need to find a way to set up a 3d texture to make this happen with trilinear texture sampling.
 With a $2$x$2$x$2$ texture, the front $2$x$2$ pixels would encode a quadratic curve for $P_0,P_1,P_2$ and the back $2$x$2$ pixels would encode a quadratic curve for $P_1,P_2,P_3$.
-Then, when we sample the texture, plugging $t$ into $u,v$ and $w$, the result will be that it will calculate the points on the quadratic curves $P_0,P_1,P_2$ at time $t$ and also $P_1,P_2,P_3$ at time $t$, and then will interpolate across the $w$ axis to give us the final result.
+Then, when we sample the texture, plugging $t$ into $u,v$ and $w$, the result will be that it will calculate the points on the quadratic curves $P_0,P_1,P_2$ at $t$ and also $P_1,P_2,P_3$ at $t$, and then will interpolate across the $w$ axis to give us the final result.
 
@@
 As an example, let's say that we have a texture that is 8x2, and encodes 4 quadratic Bezier curves end to end.
-The left most 2x2 pixels encode the quadratic curve used for time $t \epsilon [0,0.25)$.
-The next block of 2x2 pixels encode the quadratic curve used for time $t \epsilon [0.25,0.5)$.
-The third block encodes time $t \epsilon [0.5,0.75)$, and the last block encodes time $t \epsilon [0.75,1.0]$.
+The left most 2x2 pixels encode the quadratic curve used at $t \epsilon [0,0.25)$.
+The next block of 2x2 pixels encode the quadratic curve used at $t \epsilon [0.25,0.5)$.
+The third block encodes $t \epsilon [0.5,0.75)$, and the last block encodes $t \epsilon [0.75,1.0]$.
 
@@
 This technique does have applications to vector graphics, but they are pretty limited and there are better solutions if using Bezier curves as vector art is the goal \cite{Loop:2005:RIC:1073204.1073303,Nehab:2008:RRG:1409060.1409088}, or if the goal is to use textures for vector art data storage \cite{Green:2007:IAM:1281500.1281665}.
-The limitation is due to the fact that this technique is good at calculating the point on a curve at time $t$, but when using curves in vector graphics situations, you usually do not know the time $t$ that you want to know the curve point for, and it is usually difficult to find it.
-
-However, there are certain special situations where you can easily get the time $t$ value of the curve that you care about.
+The limitation is due to the fact that this technique is good at calculating the point on a curve at $t$, but when using curves in vector graphics situations, you usually do not know the $t$ that you want to know the curve point for, and it is usually difficult to find it.
+
+However, there are certain special situations where you can easily get the $t$ value of the curve that you care about.
 Two of the most common situations for these are when rendering 1D explicit Bezier curves, and when rendering 1D explicit Bezier curves in polar form.
@@
 
-Extending this technique to the third dimension would be an interesting usage case, as well as exploring ways to make the vector art usage cases more attractive.
+Extending this technique to the third dimension to make surfaces would be an interesting usage case, as well as exploring ways to make the vector art usage cases more attractive.
 

### 2015-08-12 Paper/paper.tex
Nearly done with feedback adjustments

@@
 
-    \caption{A rational bezier spline showing cosine in green and sine in red.
-The white line is the true value of those functions.
-\textit{Left:} Evaluated with hardware sampling and then division.
-\textit{Right:} Evaluated by reading the control points into the shader program, calculating the curves, and then doing a division.}
+    \caption{Rational Bezier spline vs glsl sin() function.  Sin() values in grey on top of the Bezier spline in red.  Red pixels show where the values do not match. }
     \label{fig:rationalbeziersincos}
@@
     \end{tikzpicture}
-    \caption{\textit{Left:} Curve evaluted with a single texture read and bilinear texture sampling.
-\textit{Middle:} Curve evaluated with two linear texture samples, combined in the shader program.
-\textit{Right:} Curve evaluated with three texture samples (one per control point), combined in the shader program.}
+    \caption{ Quality versus texture read count.
+\textit{Left:} One Texture Read (one bilinear sample).
+\textit{Middle:} Two Texture Reads (two linear samples).
+\textit{Right:} Three Texture Reads (three nearest neighbor samples).}
     \label{fig:samplehwsw}
@@
 
-TODO: do a test with the cards at work, and put those results here as well!
+TODO: Test with at least one other card
+
+The performance characteristics don't change very much based on texture dimensionality.
+This shows that you can up the degree of the curve by upping the dimension of the texture you store the curve in, without incurring any significant performance costs.
 

### 2015-08-12 GLFW/Curves/ShaderDefs.h

@@ -73,6 +73,12 @@ SHADER_BEGIN(RationalTest, 1000, 500)
     SHADER_UNIFORM_TEXTURE_2D(uSampler, float, true)
 SHADER_END()
 
+SHADER_BEGIN(RationalTest2, 1000, 500)
+    SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
+    SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)
+    SHADER_UNIFORM_TEXTURE_2D(uSampler, float, true)
+SHADER_END()
+
 SHADER_BEGIN(Quadratic1d, 1000, 500)
     SHADER_VERTEX_ATTRIBUTE(aVertexPosition, 2, double)
     SHADER_VERTEX_ATTRIBUTE(aTextureCoord, 2, double)

### 2015-08-13 Paper/paper.tex
Re-read the paper, looking decent

@@
 \textit{Middle:} The texture as viewed with bilinear sampling.
-\textit{Right:} The resulting quadratic Bezier curves when sampling along the yellow line (Alpha curve omitted).}
+\textit{Right:} The resulting quadratic Bezier curves when sampling along the yellow line.}
   \label{fig:teaser}
@@
 \label{sec:introduction}
-There are two basic ways for a shader program to have customized curve data.
+There are two basic ways for a shader program to access customized curve data.
 One way is to evaluate the curve on the CPU at discrete intervals and put those points into a texture that can be used by the GPU.
@@
   \includegraphics[width=5in]{Figure2.png}
-  \caption{Quadratic Curve  \textit{Left:} Yellow is the curve calculated from shader program constants.
+  \caption{Quadratic Curve.
+\textit{Left:} Yellow is the curve calculated from shader program constants.
 Red is the same curve baked out in a 4x1 texture.
@@
 The yellow line indicates where texture samples are taken from to evaluate the quadratic Bezier curve.
-\textit{Right:} The curves resulting from sampling along the yellow line (Alpha curve omitted).}
+\textit{Right:} The curves resulting from sampling along the yellow line.}
     \label{fig:texbilcurve}
@@
 Bezier curves of degree $N$ are just the linear interpolation between two Bezier curves of degree $N-1$.
+These operations are equivalent.
 
@@
 For instance, if you had a 2x2 texture, you could encode the control points $P_0,P_1,P_2$ into the red channel, and the control points $P_1,P_2,P_3$ into the green channel.
-Then, after you did a texture read, you could do a lerp between the red and the green channel values.
+Then, after you did a texture read, you could do a lerp between the red and the green channel values by $t$.
 Since the red and green channel each contain a quadratic curve, the result would be a cubic curve, defined by the control points $P_0,P_1,P_2,P_3$  However, you've used up two of the channels for a single curve, so are getting fewer curves per texture read, but they are higher degree.
@@
 
-    \caption{Rational Bezier spline vs glsl sin() function.  Sin() values in grey on top of the Bezier spline in red.  Red pixels show where the values do not match. }
+    \caption{Rational Bezier spline vs glsl sin() function.  Sin() values in grey on top of the Bezier spline in red.  Red pixels show where the values don't match. }
     \label{fig:rationalbeziersincos}
@@
 
-Just as b-splines can be converted into piecewise Bezier curves, NURBS can also be converted into piecewise rational Bezier curves, again using Boehm's algorithm, which means these techniques can also apply to NURBS, if they are first preprocessed into rational Bezier curves.
+Just as b-splines can be converted into piecewise Bezier curves, NURBS can also be converted into piecewise rational Bezier curves, again using Boehm's algorithm, which means these techniques can also apply to NURBS, if they are first preprocessed into piecewise rational Bezier curves.
 

### 2015-08-13 Paper/paper.tex
2nd Performance Data Point.  Ready for Blizzard Review

--- 2015-08-12 Paper/paper.tex
@@
 
-\begin{tabular}{|l|l l|}
+\begin{tabular}{|l|l l|l l|}
 \hline
-& \multicolumn{2}{|c|}{NV GF GTX 980m} \\
-& \bf{HW} & \bf{SW}\\ \hline
-\bf{1D Texture / Linear Curve} & 131.8 $\mu$s & 132.7 $\mu$s \\ \hline
-\bf{2D Texture / Quadratic Curve} & 131.1 $\mu$s & 135.1 $\mu$s \\ \hline
-\bf{3D Texture / Cubic Curve} & 135.4 $\mu$s & 146.2 $\mu$s \\ \hline
+& \multicolumn{2}{|c|}{NV GF GTX 980m} & \multicolumn{2}{|c|}{NV GF GTX 770}\\
+& \bf{HW} & \bf{SW} & \bf{HW} & \bf{SW} \\ \hline
+\bf{1D Texture / Linear Curve} & 131.8 $\mu$s & 132.7 $\mu$s & 103.0 $\mu$s & 104.1 $\mu$s \\ \hline
+\bf{2D Texture / Quadratic Curve} & 131.1 $\mu$s & 135.1 $\mu$s & 104.1 $\mu$s & 118.2 $\mu$s \\ \hline
+\bf{3D Texture / Cubic Curve} & 135.4 $\mu$s & 146.2 $\mu$s & 104.1 $\mu$s & 130.1 $\mu$s \\ \hline
 \end{tabular}
-
-TODO: Test with at least one other card
 
@@
 This shows that you can up the degree of the curve by upping the dimension of the texture you store the curve in, without incurring any significant performance costs.
+While software implementations are a bit slower, they are not significantly slower.
+Again, the usage case for deciding whether to offload curve work to the sampler (and if so, how much of it), or to do it in the shader program depends on your specific circumstances, and the resource usage of your application.
 

### 2015-08-27 Paper/paper.tex
Removed blizzard contact information
per request from sylvia
Josh Grass Feedback Implemented
time to clean up for submission!

@@
   \caption{Quadratic Curve.
-\textit{Left:} Yellow is the curve calculated from shader program constants.
-Red is the same curve baked out in a 4x1 texture.
-\textit{Right:}  Yellow uses the technique from this paper to encode the curve in a 2x2 texture.
-Red is the same curve baked out in a 4x1 texture again for comparison.}
+\textit{Left:} Calculated from shader program constants.
+\textit{Middle:} The technique in this paper, using a 2x2 texture and a single texture sample per pixel.
+\textit{Right:} Baked out curve, using a 4x1 texture and a single texture sample per pixel.}
   \label{fig:quickcomparison}
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (2,-2);
+      \draw[yellow,->,line width=0.5mm]    (0.5,-0.5) -- (1.5,-1.5);
       \draw (0.5,-0.5) node {$P_0$};
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (2,-3);
+      \draw[yellow,->,line width=0.5mm]    (0.5,-0.5) -- (1.5,-1.5);
+      \draw[yellow,->,line width=0.5mm]    (0.5,-1.5) -- (1.5,-2.5);
       \draw (0.5,-0.5) node {$P_0$};
@@
       \draw[step=1cm,gray,very thin] (0,0) grid (4,-3);
+      \draw[yellow,->,line width=0.5mm]    (0.5,-0.5) -- (1.5,-1.5);
+      \draw[yellow,->,line width=0.5mm]    (0.5,-1.5) -- (1.5,-2.5);      
       \draw (0.5,-0.5) node {$P_0$};
@@
 
+      \draw[yellow,->,line width=0.5mm]    (2.5,-0.5) -- (3.5,-1.5);
+      \draw[yellow,->,line width=0.5mm]    (2.5,-1.5) -- (3.5,-2.5);   
       \draw (2.5,-0.5) node {$P_3$};
@@
 \textit{Middle:} A cubic curve encoded in a 2d texture that is $(2,3)$ in size.
-\textit{Right:} Two piecewise cubic curves encoded in a 2d texture with $C0$ continuity that is $(4,3)$ in size.}
+\textit{Right:} Two piecewise cubic curves encoded in a 2d texture with $C0$ continuity that is $(4,3)$ in size.
+The yellow lines show how the curves are sampled from the texture over t.}
     \label{fig:texlayeout2d}
@@
 \label{sec:acknowledgements}
-TODO: this
+I would like to give my deepest thanks to Ian McCown, James Anhalt III and Dr.
+Josh Grass for reading this over and giving feedback before submission.
+You all had significant responsibilities at the time, ranging from having a young newborn to moving to another continent, and as people I have a lot of respect for, I really appreciate that all three of you made time to have a look and give me meaningful feedback.
+Thank you also to my wife Chanel for your support and patience during this process!
 

### 2015-08-27 Submission/PaperSource/paper.tex
Submitted!

--- 2015-08-27 Paper/paper.tex
@@
 \label{sec:indexofsupplementalmaterials}
-TODO: put information about where the zip can be downloaded.
-
-The zip file contains a folder named WebGL which contains the WebGL demos, and a folder named GLFW which contains the GLFW (windows) C++ OpenGL demos.
+The zip file contains a folder named WebGL which contains the WebGL demos, and a folder named OpenGL which contains the C++ OpenGL demos.
 
@@
 
-\paragraph{\textbf{GLFW Folder}}
-\begin{itemize}
-  \item \textit{Curves} --- The folder that contains the source code and the project and solution file for the demos.
-  \item \textit{glew-1.12.0} --- The glew library used for the demos.
-  \item \textit{glfw-3.1.1} --- The glfw library used for the demos.  
-\end{itemize}
+\paragraph{
+\textbf{OpenGL Folder}
+\newline
+This folder contains the source code, project and solution file for the C++ OpenGL demos.  The demos were created using the libraries glew-1.12.0 and glfw-3.1.1.
+}
 

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/ShaderDefs.h

@@ -1,0 +1,215 @@
+//=============================================================================================================
+//    Macros to declare shaders
+//
+//    SHADER_BEGIN(NAME, WIDTH, HEIGHT)
+//        SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+//        SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
+//        SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP)
+//        SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP)
+//        SHADER_UNIFORM(NAME)
+//    SHADER_END()
+//
+//    SHADER_BEGIN(NAME, WIDTH, HEIGHT)
+//
+//    Defines a new shader class CShader<NAME>, and specifies the dimensions that it wants to run at
+//
+//    SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE)
+//
+//    Defines a vertex attribute.  NAME is the name of the attribute as defined in the shader.  ELEMENTSIZE is
+//    how many floats per element there are (a vec2 would be 2, for instance!).  Use SetAttributeData_<NAME>
+//    to set data for this attribute.
+//
+//    TYPE can be float or double.
+//
+//    SHADER_UNIFORM(NAME)
+//
+//    Lets you set a uniform in the shader.  NAME is the name of the uniform.  Assumed to be a float!
+//
+//    SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP)
+//    SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP)
+//    SHADER_UNIFORM_TEXTURE_3D(NAME, TYPE, LERP)
+//
+//    Defines a shader uniform.  Also defines a texture to assign to it.  NAME is the name of the uniform as
+//    defined in the shader.  Call SetTextureData_<NAME> to set the texture data. If LERP is true, it uses
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_BilinearTest.cpp

@@ -1,0 +1,128 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            BilinearTest
+//=============================================================================================================
+
+void CShaderBilinearTest::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+
+    SetTextureData_uSampler(2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderBilinearTest::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderBilinearTest::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    bool PixelInControlPoint(vec2 pixel) {
+
+        vec4 A = texture(uSampler, vec2(0.5, 0.5) / 2.0);
+        vec4 B = texture(uSampler, vec2(1.5, 0.5) / 2.0);
+        vec4 C = texture(uSampler, vec2(1.5, 1.5) / 2.0);
+
+        return
+            length(pixel - vec2(0.0, A.x)) < 0.02 ||
+            length(pixel - vec2(0.5, B.x)) < 0.02 ||
+            length(pixel - vec2(1.0, C.x)) < 0.02;
+    }
+
+    vec4 SampleTime(vec2 time, bool linearSampling) {
+        // Bilinear sampling:
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_BilinearTest3.cpp

@@ -1,0 +1,67 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            BilinearTest3
+//=============================================================================================================
+
+void CShaderBilinearTest3::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        1.0, 0.0,
+        1.0, 1.0,
+        0.0, 0.0,
+        1.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+
+    SetTextureData_uSampler(2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderBilinearTest3::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderBilinearTest3::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vec2((vTextureCoord.x + 0.5) / 2.0)).xyz,1.0);
+    }
+    );
+}
+

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Cubic1d.cpp

@@ -1,0 +1,120 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Cubic1d
+//=============================================================================================================
+
+void CShaderCubic1d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f, 0.2f };
+    const float G[] = { 0.0f , 1.0f, 0.25f, 0.8f };
+    const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f };
+    const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f };
+
+    SetTextureData_uSampler(4, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+    });
+}
+
+const char *CShaderCubic1d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderCubic1d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler1D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(float time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / 4.0);
+
+        // Nearest sampling:
+        // Software bilinear sampling (higher quality)
+        float frac = fract(time);
+
+        float floorTime = floor(time) + 0.5;
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Cubic2d.cpp

@@ -1,0 +1,113 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Cubic2d
+//=============================================================================================================
+
+void CShaderCubic2d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f, 0.2f };
+    const float G[] = { 0.0f , 1.0f, 0.25f, 0.8f };
+    const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f };
+    const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f };
+
+    SetTextureData_uSampler(2, 4, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+        R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+        0.0f, 0.0f, 0.0f, 0.0f,     0.0f, 0.0f, 0.0f, 0.0f,
+    });
+}
+
+const char *CShaderCubic2d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderCubic2d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(vec2 time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / vec2(2.0, 4.0));
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Cubic3d.cpp

@@ -1,0 +1,125 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Cubic3d
+//=============================================================================================================
+
+void CShaderCubic3d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f, 0.2f };
+    const float G[] = { 0.0f , 1.0f, 0.25f, 0.8f };
+    const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f };
+    const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f };
+
+    SetTextureData_uSampler(2, 2, 2, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+        R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+    });
+}
+
+const char *CShaderCubic3d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderCubic3d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler3D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(vec3 time, bool linearSampling) {
+        // Trilinear sampling:
+        // Hardware based trilinear sampling
+        if (linearSampling)
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Perf.cpp

@@ -1,0 +1,338 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                              Utils
+//=============================================================================================================
+
+template <typename T>
+void SetTextureAndVertexCoords(T& o)
+{
+    o.SetAttributeData_aTextureCoord({
+        0.0f, 0.0f,
+        1.0f, 0.0f,
+        1.0f, 1.0f,
+        0.0f, 0.0f,
+        1.0f, 1.0f,
+        0.0f, 1.0f,
+    });
+    o.SetAttributeData_aVertexPosition({
+        -1.0f, -1.0f,
+         1.0f, -1.0f,
+         1.0f,  1.0f,
+        -1.0f, -1.0f,
+         1.0f,  1.0f,
+        -1.0f,  1.0f,
+    });
+}
+
+template <typename T>
+void Init_Linear1D(T& o)
+{
+    SetTextureAndVertexCoords(o);
+    const unsigned char R[] = { 255,   0 };
+    const unsigned char G[] = {   0, 255 };
+    const unsigned char B[] = {  50,   0 };
+    const unsigned char A[] = { 192,   0 };
+
+    o.SetTextureData_uSampler(2, {
+        R[0], G[0], B[0], A[0], R[1], G[1], B[1], A[1]
+    });
+}
+
+template <typename T>
+void Init_Quadratic2D(T& o)
+{
+    SetTextureAndVertexCoords(o);
+    const unsigned char R[] = { 255,   0, 255 };
+    const unsigned char G[] = {   0, 255,   0 };
+    const unsigned char B[] = {  50,   0, 192 };
+    const unsigned char A[] = { 192,  64, 128 };
+
+    o.SetTextureData_uSampler(2, 2, {
+        R[0], G[0], B[0], A[0], R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1], R[2], G[2], B[2], A[2]
+    });
+}
+
+template <typename T>
+void Init_Cubic3D(T& o)
+{
+    SetTextureAndVertexCoords(o);
+    const unsigned char R[] = { 255,   0, 255,   0 };
+    const unsigned char G[] = {   0, 255,   0, 255 };
+    const unsigned char B[] = {  50,   0, 192,  64 };
+    const unsigned char A[] = { 192,  64, 128,   0 };
+
+    o.SetTextureData_uSampler(2, 2, 2, {
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Quadratic2d.cpp

@@ -1,0 +1,109 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Quadratic2d
+//=============================================================================================================
+
+void CShaderQuadratic2d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f };
+    const float G[] = { 0.0f , 1.0f, 0.25f };
+    const float B[] = { 0.2f , 0.0f, 1.00f };
+    const float A[] = { 0.75f, 0.0f, 0.29f };
+
+    SetTextureData_uSampler(2, 2, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2]
+    });
+}
+
+const char *CShaderQuadratic2d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderQuadratic2d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(vec2 time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / 2.0);
+
+        // Nearest sampling:
+        // Software bilinear sampling (higher quality)
+        vec2 frac = fract(time);
+
+        vec2 floorTime = floor(time) + 0.5;
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Quartic1d.cpp

@@ -1,0 +1,133 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Quartic1d
+//=============================================================================================================
+
+void CShaderQuartic1d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f, 0.2f, 0.7f };
+    const float G[] = { 0.0f , 1.0f, 0.25f, 0.8f, 0.6f };
+    const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f, 0.3f };
+    const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f, 1.0f };
+
+    SetTextureData_uSampler(8, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+        R[4], G[4], B[4], A[4],     0.0f, 0.0f, 0.0f, 0.0f,     0.0f, 0.0f, 0.0f, 0.0f,     0.0f, 0.0f, 0.0f, 0.0f,
+    });
+}
+
+const char *CShaderQuartic1d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderQuartic1d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler1D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(float time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Quartic2d.cpp

@@ -1,0 +1,132 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Quartic2d
+//=============================================================================================================
+
+void CShaderQuartic2d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f, 0.2f, 0.7f };
+    const float G[] = { 0.0f , 1.0f, 0.25f, 0.8f, 0.6f };
+    const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f, 0.3f };
+    const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f, 1.0f };
+
+    SetTextureData_uSampler(2, 4, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+        R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+        R[3], G[3], B[3], A[3],     R[4], G[4], B[4], A[4],
+    });
+}
+
+const char *CShaderQuartic2d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderQuartic2d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(vec2 time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / vec2(2.0, 4.0));
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Quartic3d.cpp

@@ -1,0 +1,126 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Quartic3d
+//=============================================================================================================
+
+void CShaderQuartic3d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f, 0.2f, 0.7f };
+    const float G[] = { 0.0f , 1.0f, 0.25f, 0.8f, 0.6f };
+    const float B[] = { 0.2f , 0.0f, 1.00f, 0.6f, 0.3f };
+    const float A[] = { 0.75f, 0.0f, 0.29f, 0.4f, 1.0f };
+
+    SetTextureData_uSampler(2, 4, 2, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+        R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+        0.0f, 0.0f, 0.0f, 0.0f,     0.0f, 0.0f, 0.0f, 0.0f,
+
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+        R[2], G[2], B[2], A[2],     R[3], G[3], B[3], A[3],
+        R[3], G[3], B[3], A[3],     R[4], G[4], B[4], A[4],
+        0.0f, 0.0f, 0.0f, 0.0f,     0.0f, 0.0f, 0.0f, 0.0f,
+    });
+}
+
+const char *CShaderQuartic3d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_RationalTest.cpp

@@ -1,0 +1,183 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            RationalTest
+//=============================================================================================================
+
+void CShaderRationalTest::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A1 = 0.0f;
+    float B1 = 1.0f;
+    float C1 = 1.0f;
+
+    float A2 = 1.0f;
+    float B2 = 1.0f;
+    float C2 = 0.0f;
+
+    float W1 = 1.0f;
+    float W2 = 1.0f / sqrtf(2.0);
+    float W3 = 1.0f;
+
+    A1 *= W1;
+    B1 *= W2;
+    C1 *= W3;
+
+    A2 *= W1;
+    B2 *= W2;
+    C2 *= W3;
+
+    // Note - the B channel is empty, we could encode a 3rd rational curve in there, so long
+    // as it used the same W weights! (:
+    SetTextureData_uSampler(2, 2, {
+        A1, A2, 0.0f, W1,     B1, B2, 0.0f, W2,
+        B1, B2, 0.0f, W2,     C1, C2, 0.0f, W3
+    });
+}
+
+const char *CShaderRationalTest::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderRationalTest::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(vec2 time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / 2.0);
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_RationalTest2.cpp

@@ -1,0 +1,167 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            RationalTest2
+//=============================================================================================================
+
+void CShaderRationalTest2::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0,
+        2.0, 0.0,
+        2.0, 1.0,
+        0.0, 0.0,
+        2.0, 1.0,
+        0.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A1 = 0.0f;
+    float B1 = 1.0f;
+    float C1 = 1.0f;
+
+    float A2 = 1.0f;
+    float B2 = 1.0f;
+    float C2 = 0.0f;
+
+    float W1 = 1.0f;
+    float W2 = 1.0f / sqrtf(2.0);
+    float W3 = 1.0f;
+
+    A1 *= W1;
+    B1 *= W2;
+    C1 *= W3;
+
+    A2 *= W1;
+    B2 *= W2;
+    C2 *= W3;
+
+    // Note - the B channel is empty, we could encode a 3rd rational curve in there, so long
+    // as it used the same W weights! (:
+    SetTextureData_uSampler(2, 2, {
+        A1, A2, 0.0f, W1,     B1, B2, 0.0f, W2,
+        B1, B2, 0.0f, W2,     C1, C2, 0.0f, W3
+    });
+}
+
+const char *CShaderRationalTest2::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec2 aTextureCoord;
+
+    out vec2 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderRationalTest2::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler2D uSampler;
+    
+    in vec2 vTextureCoord;
+
+    out vec4 outColor;
+
+    vec4 SampleTime(vec2 time, bool linearSampling) {
+        // Bilinear sampling:
+        // Hardware based bilinear sampling
+        if (linearSampling)
+            return texture(uSampler, (time + 0.5) / 2.0);
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Texture1d.cpp

@@ -1,0 +1,67 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Texture1d
+//=============================================================================================================
+
+void CShaderTexture1d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0,
+        1.0,
+        1.0,
+        0.0,
+        1.0,
+        0.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f};
+    const float G[] = { 0.0f , 1.0f};
+    const float B[] = { 0.2f , 0.0f};
+    const float A[] = { 0.75f, 0.0f};
+
+    SetTextureData_uSampler(2, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+    });
+}
+
+const char *CShaderTexture1d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in float aTextureCoord;
+
+    out float vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderTexture1d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler1D uSampler;
+    
+    in float vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vTextureCoord).xyz, 1.0);
+    }
+    );
+}
+

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_Texture3d.cpp

@@ -1,0 +1,71 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            Texture3d
+//=============================================================================================================
+
+void CShaderTexture3d::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0, 0.0,
+        1.0, 0.0, 0.2,
+        1.0, 1.0, 0.4,
+        0.0, 0.0, 0.6,
+        1.0, 1.0, 0.8,
+        0.0, 1.0, 1.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    const float R[] = { 0.5f , 0.0f, 0.75f };
+    const float G[] = { 0.0f , 1.0f, 0.25f };
+    const float B[] = { 0.2f , 0.0f, 1.00f };
+    const float A[] = { 0.75f, 0.0f, 0.29f };
+
+    SetTextureData_uSampler(2, 2, 2, {
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+
+        R[1], G[1], B[1], A[1],     R[2], G[2], B[2], A[2],
+        R[0], G[0], B[0], A[0],     R[1], G[1], B[1], A[1],
+    });
+}
+
+const char *CShaderTexture3d::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec3 aTextureCoord;
+
+    out vec3 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderTexture3d::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler3D uSampler;
+    
+    in vec3 vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vTextureCoord).xyz, 1.0);
+    }
+    );
+}
+

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_TrilinearBakeTest.cpp

@@ -1,0 +1,169 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            TrilinearBakeTest
+//=============================================================================================================
+
+void CShaderTrilinearBakeTest::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0, 0.0,
+        2.0, 0.0, 0.0,
+        2.0, 1.0, 0.0,
+        0.0, 0.0, 0.0,
+        2.0, 1.0, 0.0,
+        0.0, 1.0, 0.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+    float D = 0.1f;
+
+    SetTextureData_uSampler(2, 2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+        C, 0.0f, 0.0f, 0.0f,     D, 0.0f, 0.0f, 0.0f
+    });
+
+    // 8x1 baked out texture for curve to show accuracy using same number of pixels as 2x2x2 texture
+    const int c_numBakeSamples = 8;
+    std::vector<float> curvePoints;
+    for (int i = 0; i < c_numBakeSamples; ++i) {
+        float t = float(i) / float(c_numBakeSamples - 1);
+        float t2 = t*t;
+        float t3 = t*t*t;
+        float s = 1.0f - t;
+        float s2 = s*s;
+        float s3 = s*s*s;
+        float curveValue = A*s3 + B*3.0f*s2*t + C*3.0f*s*t2 + D*t3;
+        curvePoints.push_back(curveValue);
+        curvePoints.push_back(0.0f);
+        curvePoints.push_back(0.0f);
+        curvePoints.push_back(0.0f);
+    }
+    SetTextureData_uBakedSampler(c_numBakeSamples, 1, curvePoints);
+    SetUniformData_uBakeSamples((float)c_numBakeSamples);
+}
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_TrilinearTest.cpp

@@ -1,0 +1,141 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            TrilinearTest
+//=============================================================================================================
+
+void CShaderTrilinearTest::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0, 0.0,
+        2.0, 0.0, 0.0,
+        2.0, 1.0, 0.0,
+        0.0, 0.0, 0.0,
+        2.0, 1.0, 0.0,
+        0.0, 1.0, 0.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+    float D = 0.1f;
+
+    SetTextureData_uSampler(2, 2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+        C, 0.0f, 0.0f, 0.0f,     D, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderTrilinearTest::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec3 aTextureCoord;
+
+    out vec3 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderTrilinearTest::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler3D uSampler;
+    
+    in vec3 vTextureCoord;
+
+    out vec4 outColor;
+
+    bool PixelInControlPoint(vec2 pixel) {
+
+        vec4 A = texture(uSampler, vec3(0.25, 0.25, 0.25));
+        vec4 B = texture(uSampler, vec3(0.75, 0.25, 0.25));
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shader_TrilinearTest3.cpp

@@ -1,0 +1,71 @@
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                            TrilinearTest3
+//=============================================================================================================
+
+void CShaderTrilinearTest3::Init()
+{
+    SetAttributeData_aTextureCoord({
+        0.0, 0.0, 0.0,
+        1.0, 0.0, 0.0,
+        1.0, 1.0, 0.0,
+        0.0, 0.0, 0.0,
+        1.0, 1.0, 0.0,
+        0.0, 1.0, 0.0,
+    });
+    SetAttributeData_aVertexPosition({
+        -1.0, -1.0,
+         1.0, -1.0,
+         1.0,  1.0,
+        -1.0, -1.0,
+         1.0,  1.0,
+        -1.0,  1.0,
+    });
+
+    float A = 0.5f;
+    float B = 0.2f;
+    float C = 0.8f;
+    float D = 0.1f;
+
+    SetTextureData_uSampler(2, 2, 2, {
+        A, 0.0f, 0.0f, 0.0f,     B, 0.0f, 0.0f, 0.0f,
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+
+        B, 0.0f, 0.0f, 0.0f,     C, 0.0f, 0.0f, 0.0f,
+        C, 0.0f, 0.0f, 0.0f,     D, 0.0f, 0.0f, 0.0f
+    });
+}
+
+const char *CShaderTrilinearTest3::GetVertexShader()
+{
+    return
+    SHADER_SOURCE(
+    in vec2 aVertexPosition;
+    in vec3 aTextureCoord;
+
+    out vec3 vTextureCoord;
+
+    void main(void) {
+        gl_Position = vec4(aVertexPosition, 1.0, 1.0);
+        vTextureCoord = aTextureCoord;
+    }
+    );
+}
+
+const char *CShaderTrilinearTest3::GetFragmentShader()
+{
+    return
+    SHADER_SOURCE(
+    uniform sampler3D uSampler;
+    
+    in vec3 vTextureCoord;
+
+    out vec4 outColor;
+
+    void main(void) {
+        outColor = vec4(texture(uSampler, vec3((vTextureCoord.x + 0.5) / 2.0)).xyz, 1.0);
+    }
+    );
+}
+

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/Shaders.h

@@ -1,0 +1,89 @@
+//=============================================================================================================
+// Expands ShaderDefs.h into CShader... classes
+//=============================================================================================================
+
+#include <vector>
+#include "utils.h"
+
+#define SHADER_BEGIN(NAME, WIDTH, HEIGHT) \
+    class CShader##NAME## { \
+    public: \
+        CShader##NAME##(); \
+        ~CShader##NAME##(); \
+        void Render(); \
+        void Init(); \
+        static const char *GetName() { return #NAME; } \
+        static const char *GetVertexShader(); \
+        static const char *GetFragmentShader(); \
+        static void GetWidthHeight(int &width, int &height) {width=WIDTH; height=HEIGHT;}
+
+#define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE) \
+    private: \
+        GLuint m_attr_##NAME##; \
+        GLuint m_attr_##NAME##_buffer; \
+    public: \
+        void SetAttributeData_##NAME##(const std::vector<TYPE>& data) { \
+            m_attr_##NAME##_buffer = MakeBuffer<TYPE>(data); \
+            m_numTriangles = data.size() / ELEMENTSIZE; \
+        }
+
+#define SHADER_UNIFORM(NAME) \
+    private: \
+        GLuint m_uniform_##NAME##; \
+        float m_uniform_value_##NAME##; \
+    public: \
+        void SetUniformData_##NAME##(float value) {m_uniform_value_##NAME## = value;} 
+
+#define SHADER_UNIFORM_TEXTURE_1D(NAME, TYPE, LERP) \
+    private: \
+        GLuint m_uniform_##NAME##; \
+        GLuint m_texture_##NAME##; \
+    public: \
+        void SetTextureData_##NAME##(GLsizei width, const std::vector<TYPE>& data) { \
+            m_texture_##NAME## = MakeTexture1D<TYPE>(width, LERP, data); \
+        }
+
+#define SHADER_UNIFORM_TEXTURE_2D(NAME, TYPE, LERP) \
+    private: \
+        GLuint m_uniform_##NAME##; \
+        GLuint m_texture_##NAME##; \
+    public: \
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/main.cpp

@@ -1,0 +1,176 @@
+//=============================================================================================================
+// Main
+//=============================================================================================================
+
+#include "utils.h"
+#include <stdlib.h>
+#include <stdio.h>
+#include <string>
+#include <vector>
+
+#include "Shaders.h"
+
+EShaderTest g_whichTest = EShaderTest::e_shaderFirst;
+
+void WaitForEnter()
+{
+    printf("Press Enter to quit");
+    fflush(stdin);
+    getchar();
+}
+
+//=============================================================================================================
+static void error_callback(int error, const char* description)
+{
+    fputs(description, stderr);
+}
+
+//=============================================================================================================
+static void key_callback(GLFWwindow* window, int key, int scancode, int action, int mods)
+{
+    if (key == GLFW_KEY_ESCAPE && action == GLFW_PRESS)
+        glfwSetWindowShouldClose(window, GL_TRUE);
+
+    if (key == GLFW_KEY_LEFT && action == GLFW_PRESS) {
+        if (g_whichTest > EShaderTest::e_shaderFirst)
+            g_whichTest = EShaderTest(g_whichTest - 1);
+    }
+
+    if (key == GLFW_KEY_RIGHT && action == GLFW_PRESS) {
+        if (g_whichTest < EShaderTest::e_shaderLast)
+            g_whichTest = EShaderTest(g_whichTest + 1);
+    }
+}
+
+//=============================================================================================================
+int main(void)
+{
+    const bool c_fullscreen = false;
+
+    //FreeConsole();
+    GLFWwindow* window;
+    glfwSetErrorCallback(error_callback);
+    if (!glfwInit())
+        exit(EXIT_FAILURE);
+
+    window = glfwCreateWindow(1000, 500, "", c_fullscreen ? glfwGetPrimaryMonitor() : NULL, NULL);
+    if (!window)
+    {
+        glfwTerminate();
+        exit(EXIT_FAILURE);
+    }
+    glfwMakeContextCurrent(window);
+    glfwSwapInterval(0);
+    glfwSetKeyCallback(window, key_callback);
+
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/shaders.cpp

@@ -1,0 +1,108 @@
+//=============================================================================================================
+// Expands ShaderDefs.h into CShader... classes
+//=============================================================================================================
+
+#include "GL/glew.h"
+#include <windows.h>
+#include <GLFW/glfw3.h>
+#include "Shaders.h"
+
+//=============================================================================================================
+//                                        Shader Program Loading
+//=============================================================================================================
+
+template <typename T>
+GLuint LoadShader(const T& shader)
+{
+    return LoadShader(shader.GetName(), shader.GetVertexShader(), shader.GetFragmentShader());
+}
+
+//=============================================================================================================
+//                                            Helper Funcs
+//=============================================================================================================
+
+template <typename T>
+GLenum GLType();
+
+template <>
+GLenum GLType<float>()
+{
+    return GL_FLOAT;
+}
+
+template <>
+GLenum GLType<double>()
+{
+    return GL_DOUBLE;
+}
+
+//=============================================================================================================
+//                                            Boiler Plate
+//=============================================================================================================
+
+// ----- MAKE CONSTRUCTORS ----- 
+#define SHADER_BEGIN(NAME, WIDTH, HEIGHT) \
+    CShader##NAME##::CShader##NAME##() { \
+        m_program = LoadShader(*this);
+#define SHADER_VERTEX_ATTRIBUTE(NAME, ELEMENTSIZE, TYPE) \
+        m_attr_##NAME## = glGetAttribLocation(m_program, #NAME); \
+        m_attr_##NAME##_buffer = -1; \
+        glEnableVertexAttribArray(m_attr_##NAME##);
+#define SHADER_UNIFORM(NAME) \
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/utils.cpp

@@ -1,0 +1,171 @@
+//=============================================================================================================
+// Utility functions
+//=============================================================================================================
+
+#include "utils.h"
+#include <stdio.h>
+#include <vector>
+#include <algorithm>
+
+//=============================================================================================================
+GLuint LoadShader(const char *name, const char *vertexShader, const char *fragmentShader) {
+    GLuint vertShader = glCreateShader(GL_VERTEX_SHADER);
+    GLuint fragShader = glCreateShader(GL_FRAGMENT_SHADER);
+
+    GLint result = GL_FALSE;
+    int logLength;
+
+    // Compile vertex shader
+    glShaderSource(vertShader, 1, &vertexShader, NULL);
+    glCompileShader(vertShader);
+
+    // Check vertex shader
+    glGetShaderiv(vertShader, GL_COMPILE_STATUS, &result);
+    glGetShaderiv(vertShader, GL_INFO_LOG_LENGTH, &logLength);
+    std::vector<GLchar> vertShaderError((logLength > 1) ? logLength : 1);
+    glGetShaderInfoLog(vertShader, logLength, NULL, &vertShaderError[0]);
+
+    // Compile fragment shader
+    glShaderSource(fragShader, 1, &fragmentShader, NULL);
+    glCompileShader(fragShader);
+
+    // Check fragment shader
+    glGetShaderiv(fragShader, GL_COMPILE_STATUS, &result);
+    glGetShaderiv(fragShader, GL_INFO_LOG_LENGTH, &logLength);
+    std::vector<GLchar> fragShaderError((logLength > 1) ? logLength : 1);
+    glGetShaderInfoLog(fragShader, logLength, NULL, &fragShaderError[0]);
+
+    GLuint program = glCreateProgram();
+    glAttachShader(program, vertShader);
+    glAttachShader(program, fragShader);
+    glLinkProgram(program);
+
+    glGetProgramiv(program, GL_LINK_STATUS, &result);
+    glGetProgramiv(program, GL_INFO_LOG_LENGTH, &logLength);
+    std::vector<char> programError((logLength > 1) ? logLength : 1);
[…]

### 2015-08-27 Submission/SupplementalMaterials/OpenGL/utils.h

@@ -1,0 +1,46 @@
+//=============================================================================================================
+// Utility functions
+//=============================================================================================================
+
+#include "GL/glew.h"
+#include <GLFW/glfw3.h>
+#include <vector>
+
+GLuint LoadShader(const char *name, const char *vertexShader, const char *fragmentShader);
+
+template<typename T>
+GLuint MakeBuffer(const std::vector<T>& data);
+
+template<typename T>
+GLuint MakeTexture1D(GLsizei width, bool lerpSample, const std::vector<T>& data);
+
+template<typename T>
+GLuint MakeTexture2D(GLsizei width, GLsizei height, bool lerpSample, const std::vector<T>& data);
+
+template<typename T>
+GLuint MakeTexture3D(GLsizei width, GLsizei height, GLsizei depth, bool lerpSample, const std::vector<T>& data);
+
+//=============================================================================================================
+// Template Specializations
+//=============================================================================================================
+
+template<>
+GLuint MakeBuffer<double>(const std::vector<double>& data);
+template<>
+GLuint MakeBuffer<float>(const std::vector<float>& data);
+
+template<>
+GLuint MakeTexture1D<unsigned char>(GLsizei width, bool lerpSample, const std::vector<unsigned char>& data);
+template<>
+GLuint MakeTexture1D<float>(GLsizei width, bool lerpSample, const std::vector<float>& data);
+
+template<>
+GLuint MakeTexture2D<unsigned char>(GLsizei width, GLsizei height, bool lerpSample, const std::vector<unsigned char>& data);
+template<>
+GLuint MakeTexture2D<float>(GLsizei width, GLsizei height, bool lerpSample, const std::vector<float>& data);
+
+template<>
+GLuint MakeTexture3D<unsigned char>(GLsizei width, GLsizei height, GLsizei depth, bool lerpSample, const std::vector<unsigned char>& data);
+template<>
+GLuint MakeTexture3D<float>(GLsizei width, GLsizei height, GLsizei depth, bool lerpSample, const std::vector<float>& data);
+

### 2015-08-27 Submission/SupplementalMaterials/WebGL/webgl-utils.js

@@ -1,0 +1,175 @@
+/*
+ * Copyright 2010, Google Inc.
+ * All rights reserved.
+ *
+ * Redistribution and use in source and binary forms, with or without
+ * modification, are permitted provided that the following conditions are
+ * met:
+ *
+ *     * Redistributions of source code must retain the above copyright
+ * notice, this list of conditions and the following disclaimer.
+ *     * Redistributions in binary form must reproduce the above
+ * copyright notice, this list of conditions and the following disclaimer
+ * in the documentation and/or other materials provided with the
+ * distribution.
+ *     * Neither the name of Google Inc. nor the names of its
+ * contributors may be used to endorse or promote products derived from
+ * this software without specific prior written permission.
+ *
+ * THIS SOFTWARE IS PROVIDED BY THE COPYRIGHT HOLDERS AND CONTRIBUTORS
+ * "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING, BUT NOT
+ * LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND FITNESS FOR
+ * A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE COPYRIGHT
+ * OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT, INCIDENTAL,
+ * SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING, BUT NOT
+ * LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS OF USE,
+ * DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND ON ANY
+ * THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR TORT
+ * (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE USE
+ * OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH DAMAGE.
+ */
+
+
+/**
+ * @fileoverview This file contains functions every webgl program will need
+ * a version of one way or another.
+ *
+ * Instead of setting up a context manually it is recommended to
+ * use. This will check for success or failure. On failure it
+ * will attempt to present an approriate message to the user.
+ *
[…]

### 2016-04-28 Paper/paper.tex
Taking out jcgt for self publishing

@@
 \setciteauthor{Alan Wolfe}
-\setcitetitle{GPU Efficient Texture Based Bezier Curve Evaluation}
+\setcitetitle{GPU Texture Sampler Bezier Curve Evaluation}
 
@@
 \accepted{2014-02-07}{2014-02-07}{2014-02-07}{Editor Name}{3}{1}{1}{1}{2014}
-\seturl{http://jcgt.org/published/0003/01/01/}
+\seturl{http://blog.demofox.org/}
 
@@
 
-\title{GPU Efficient Texture Based Bezier Curve Evaluation}
+\title{GPU Texture Sampler Bezier Curve Evaluation}
 
 \author
-       {Alan Wolfe\\Blizzard Entertainment}
+       {Alan Wolfe\\http://blog.demofox.org}
 
@@
 
-The core of this technique is that the $N$-dimensional linear texture interpolation capabilities on the GPU can be mathematically equivalent to De Casteljeau's algorithm for evaluating Bezier curves.
+The core of this technique is that the $N$-dimensional linear texture interpolation capabilities on the GPU can be mathematically equivalent to De Casteljau's algorithm for evaluating Bezier curves.
 We can use linear texture sampling on textures of increasing dimensionalities to have the texture sampler calculate points on curves of increasing degree.
@@
 One dimensional linear texture sampling is just the linear interpolation between two data points.
-This is equivalent to the De Casteljeau algorithm when evaluating a linear curve of degree 1.
+This is equivalent to the De Casteljau algorithm when evaluating a linear curve of degree 1.
 In both cases, it is just linear interpolation between two values.
@@
 
-The De Casteljeau algorithm for evaluating a quadratic curve (degree 2) is also just a linear interpolation between two linear interpolations.
+The De Casteljau algorithm for evaluating a quadratic curve (degree 2) is also just a linear interpolation between two linear interpolations.
 If the control points of the quadratic curve are $P_0,P_1,P_2$, let's call the first interpolated point $Q_{0,1}$ which is the interpolation between $P_0$ and $P_1$ at $t$.
@@
 
-To further see how bilinear interpolation can be equivalent to evaluating a quadratic Bezier curve with the De Casteljeau algorithm, \autoref{fig:decasteljeauBilinear} shows it visually, and you can also compare the GLSL source code in \autoref{lst:GLSLCurves}.
-
-\begin{lstlisting}[caption={GLSL implementation of bilinear interpolation and the De Casteljeau algorithm for a quadratic Bezier curve.}, label={lst:GLSLCurves}]
+To further see how bilinear interpolation can be equivalent to evaluating a quadratic Bezier curve with the De Casteljau algorithm, \autoref{fig:decasteljeauBilinear} shows it visually, and you can also compare the GLSL source code in \autoref{lst:GLSLCurves}.
+
+\begin{lstlisting}[caption={GLSL implementation of bilinear interpolation and the De Casteljau algorithm for a quadratic Bezier curve.}, label={lst:GLSLCurves}]
 float QuadraticBezier (
@@
     \end{tikzpicture} 
-    \caption{\textit{Left:} A quadratic Bezier curve evaluated at {\bf{t}}=0.6 using the De Casteljeau algorithm.  \textit{Right:} The De Casteljeau algorithm using bilinear interpolation.}
+    \caption{\textit{Left:} A quadratic Bezier curve evaluated at {\bf{t}}=0.6 using the De Casteljau algorithm.  \textit{Right:} The De Casteljau algorithm using bilinear interpolation.}
     \label{fig:decasteljeauBilinear}
@@
 Linear texture sampling of textures of dimension $N$ is just the linear interpolation between two linear texture samples of dimension $N-1$.
-Using the De Casteljeau algorithm to evaluate a curve of degree $N$ just means that you take a linear interpolation between curves of degree $N-1$.
-
-Compared to a quadratic curve evaluated with De Casteljeau's algorithm, bilinear texture sampling has two blend weights instead of one, and has four values to interpolate between instead of three, but you can set a texture up such that when you sample it a specific way, you get as output a quadratic Bezier curve.
-Because of this, the De Casteljeau algorithm is a subset of the $N$-dimensional linear texture sampling available on the GPU.
+Using the De Casteljau algorithm to evaluate a curve of degree $N$ just means that you take a linear interpolation between curves of degree $N-1$.
+
+Compared to a quadratic curve evaluated with De Casteljau's algorithm, bilinear texture sampling has two blend weights instead of one, and has four values to interpolate between instead of three, but you can set a texture up such that when you sample it a specific way, you get as output a quadratic Bezier curve.
+Because of this, the De Casteljau algorithm is a subset of the $N$-dimensional linear texture sampling available on the GPU.
 
@@
 
-It is also possible to get points on curves of higher degree by taking multiple texture reads and combining them either using the De Casteljeau algorithm, or by using the Bernstein form equation of Bezier curves.
+It is also possible to get points on curves of higher degree by taking multiple texture reads and combining them either using the De Casteljau algorithm, or by using the Bernstein form equation of Bezier curves.
 
@@
 
-The De Casteljeau algorithm is equivalent to the Bernstein form of Bezier curves (\autoref{eqn:bernsteinform}).
+The De Casteljau algorithm is equivalent to the Bernstein form of Bezier curves (\autoref{eqn:bernsteinform}).
 
@@
   \end{tikzpicture}
-  \caption{A tree showing the De Casteljeau algorithm for a cubic curve.
+  \caption{A tree showing the De Casteljau algorithm for a cubic curve.
 The labels on the right show what type of curves are evaluated at that level, as well as the $N$ dimensional sampling that is required to evaluate nodes at that level with a single texture read.}
@@
 
-Since the De Casteljeau algorithm just interpolates between linear interpolations, we can take more texture samples and combine them in the shader program to get higher degree curves.
-For a degree $N$ Bezier curve, the De Casteljeau algorithm requires $2^{N-1}$ linear interpolations for the linear level of the tree.
+Since the De Casteljau algorithm just interpolates between linear interpolations, we can take more texture samples and combine them in the shader program to get higher degree curves.
+For a degree $N$ Bezier curve, the De Casteljau algorithm requires $2^{N-1}$ linear interpolations for the linear level of the tree.
 You need two pixels to perform a linear interpolation, so it seems that we would need $2^N$ pixels to store a curve of degree $N$ in a 1 dimensional textures.
@@
 
-Taking $N$ linearly interpolated texture samples from a one dimensional texture of size $N+1$ gives us the linear interpolated values we would need to continue to perform the De Casteljeau algorithm.
+Taking $N$ linearly interpolated texture samples from a one dimensional texture of size $N+1$ gives us the linear interpolated values we would need to continue to perform the De Casteljau algorithm.
 We can compute the final curve point either by doing that, or by plugging the values into the Bernstein form equation of Bezier curves.
@@
 In the case of a cubic curve with four control points, the one dimensional texture will be 4 pixels in size, and three texture reads will need to be done to get the interpolations along the line segments for $\overline{P_0P_1},\overline{P_1P_2},\overline{P_2P_3}$.
-Those will then need to be combined using either the De Casteljeau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = P_0*s^2 + P_1*2st + P_2*t^2$) to elevate those three points from degree 1 to degree 3, to get the final point on the curve.
+Those will then need to be combined using either the De Casteljau algorithm, or by using the Bernstein form of a quadratic Bezier curve ($P = P_0*s^2 + P_1*2st + P_2*t^2$) to elevate those three points from degree 1 to degree 3, to get the final point on the curve.
 Sample code of this example is provided in \autoref{lst:GLSLCubicTexture1D}.
@@
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a 4 pixel 1d texture.
-Linear texture sampling is used to evaluate the linear level of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
+Linear texture sampling is used to evaluate the linear level of the De Casteljau algorithm, then the process is continued both with the De Casteljau algorithm, as well as the Bernstein form of a quadratic Bezier curve.}, label={lst:GLSLCubicTexture1D}]
 uniform sampler1D uSampler;  
@@
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,4)$ pixel 2d texture.
-Bilinear texture sampling used to evaluate the first two levels of the De Casteljeau algorithm, then the process is continued both with the De Casteljeau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture2D}]
+Bilinear texture sampling used to evaluate the first two levels of the De Casteljau algorithm, then the process is continued both with the De Casteljau algorithm, as well as the Bernstein form of a linear Bezier curve (lerp).}, label={lst:GLSLCubicTexture2D}]
 uniform sampler2D uSampler; 
@@
 \begin{lstlisting}[caption={GLSL for evaluating a cubic curve encoded in a $(2,2,2)$ pixel 3d texture.
-Trilinear texture sampling used to evaluate all three levels of the De Casteljeau algorithm.}, label={lst:GLSLCubicTexture3D}]
+Trilinear texture sampling used to evaluate all three levels of the De Casteljau algorithm.}, label={lst:GLSLCubicTexture3D}]
 // 2x2x2 3d texture.
@@
 You'd only get a single curve value per texture read, but it would be 3 degrees higher.
-You could combine the color channels either with De Casteljeau's algorithm, or with the cubic Bernstein Bezier form.
+You could combine the color channels either with De Casteljau's algorithm, or with the cubic Bernstein Bezier form.
 
@@
 
-A better approach that gives the same results would be to only do one nearest neighbor texture sample per control point in the texture, and then in the shader program, either use De Casteljeau's algorithm to combine them, or use the Bernstein form equation of Bezier curves.
+A better approach that gives the same results would be to only do one nearest neighbor texture sample per control point in the texture, and then in the shader program, either use De Casteljau's algorithm to combine them, or use the Bernstein form equation of Bezier curves.
 At this point, you are best off just using a 1D texture to store your control points in, since you don't need any of the built in interpolation.
@@
 Alan Wolfe \newline
-Blizzard Entertainment \newline
-16215 Alton Parkway \newline
-Irvine, CA 92618 \newline
-\href{mailto:awolfe@blizzard.com}{awolfe@blizzard.com}
+\href{mailto:alan.wolfe@gmail.com}{alan.wolfe@gmail.com}
 \href{http://blog.demofox.org}{http://blog.demofox.org}
